---
title: "04_exploratory_test"
format: 
  html:
      self-contained: true
      
execute:
  eval: true
  echo: true
  warning: false
---

## Load Packages
These are the packages that have been used throughout the following document: `here`, `tidyverse`, `lubridate`, `knitr`
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(kableExtra)
```

## Reading data and combining
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )


# Factorising the data

cov <- cov |>
  mutate(covid_coverage_dosage = factor(covid_coverage_dosage, levels = c(0, 1, 2, 3)))

inf <- inf |>
  mutate(influenza_coverage_dosage = factor(influenza_coverage_dosage, levels = c(0, 1, 2)))


# Creating data frames for bivariate and multivariate analysis
# influenza and independent variable data
inf_ivd <- bind_cols(inf, ivd)

# covid and independent variable data
cov_ivd <- bind_cols(cov, ivd)
```

## parent's age
Examining how the upatke of the influenza and covid vaccines by the COI varies with the responding parent's age

```{r}
cov_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  summarise(count = n(), .by = c(parent_1_age, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = parent_1_age) |>
  
  ggplot(aes(x = parent_1_age, y = proportion)) +
  geom_point(aes(colour = covid_coverage_age)) +
  xlim(NA, 60) +
  geom_smooth(aes(colour = covid_coverage_age), method = "loess")

inf_ivd |>
  filter(!is.na(influenza_coverage_age)) |>
  summarise(count = n(), .by = c(parent_1_age, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = parent_1_age) |>
  
  ggplot(aes(x = parent_1_age, y = proportion)) +
  geom_point(aes(colour = influenza_coverage_age)) +
  xlim(NA, 60) +
  geom_smooth(aes(colour = influenza_coverage_age), method = "loess")
```

## chronic illnesses
Looking at chronic illness status by the age of the parent
```{r}
# chronic illness status as a proportion for parents of each age
cov_ivd |>
  filter(!is.na(parent_chronic_illness) & child_of_interest == 1) |>
  
  # group variables for <18y/o and > 60y/o
  mutate(parent_1_age = case_when(
    parent_1_age <= 18 ~ 18,
    parent_1_age > 18 & parent_1_age < 60 ~ parent_1_age,
    parent_1_age >= 60 ~ 60
  )) |>
  summarise(count = n(), .by = c(parent_chronic_illness, parent_1_age)) |>
  mutate(proportion = count/sum(count), .by = (parent_1_age)) |>
  

  
  ggplot() +
  geom_point(aes(x = parent_1_age, y = proportion, colour = parent_chronic_illness))
  #facet_wrap(vars(parent_chronic_illness))

cov_ivd |>
filter(!is.na(covid_coverage_age) & child_of_interest == 1) |>
  mutate(count = n(), .by = c(parent_1_age, parent_chronic_illness)) |>
  ggplot() +
  geom_histogram(aes(x = parent_1_age, fill = covid_coverage_age), position = "fill", binwidth = 3) +
  facet_wrap(vars(parent_chronic_illness))

inf_ivd |>
filter(!is.na(influenza_coverage_age) & child_of_interest == 1) |>
  mutate(count = n(), .by = c(parent_1_age, parent_chronic_illness)) |>
  ggplot() +
  geom_histogram(aes(x = parent_1_age, fill = influenza_coverage_age), position = "fill", binwidth = 3) +
  facet_wrap(vars(parent_chronic_illness))
```
How chronic illness status varies in the responding parent based on the number of paretns in the same household
```{r}
cov_ivd |>
  filter(child_of_interest == 1) |>
  summarise(count = n(), .by = c(child_parents, parent_chronic_illness)) |>
  mutate(child_parents = factor(child_parents)) |>
  mutate(proportion = count/sum(count), .by = child_parents) |>
  ggplot(aes(x = parent_chronic_illness, y = proportion)) +
  geom_col(aes(fill = child_parents), position = "dodge")
```

Looknig at how vaccine uptake varies with every single chronic illnesss
```{r}
# dosage
cov_ivd |>
  filter(!is.na(covid_coverage_dosage)) |>
  select(c(starts_with("respondent_"), covid_coverage_dosage)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work, respondent_sex, respondent_age)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -covid_coverage_dosage, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, covid_coverage_dosage)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    .by = c(illness, illness_experience)
  ) |>
  
  ggplot(aes(x = covid_coverage_dosage, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  facet_wrap(vars(illness))
```
```{r}
# coverage
cov_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  select(c(starts_with("respondent_"), covid_coverage_age)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work, respondent_sex, respondent_age)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -covid_coverage_age, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, covid_coverage_age)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    .by = c(illness, illness_experience)
  ) |>
  
  ggplot(aes(x = covid_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  facet_wrap(vars(illness))
```

_**Categories for the Covid vaccine**_
1. Expereince with a chronic illnes detracts from the likelihood of being vaccinated. The more recent the experience with the chronic illness, the less likely that the COI is going to get vaccinated with the influena vaccine, Never > Prev > Current
  
    
2. No experience with X chronic illness results in higher vaccine uptake than any sort of experience with the chronic illness irregardless of previous or current
    -   allergic rhinitis
    -   Cancer

3. Experience with a chronic illness results in a higher vaccine uptake but previous illness is a stronger predictor than current illness 
    -   Depression
    -   Cataract
    -   Hypertension
  
4. Current experience results in lower uptake as compareed to never having experienced a chronic illness or previous experience
    -   Asthmaa
    
5. Prev Experience is a predictor of increased uptake (relative to no experience) whilst current experience is a negative predictor of increased uptake
    -   Angina
    -   Atopic Derma
    -   COPD
    -   Abnormalities
    -   Kidney Disease
    -   Pneumonia
    -   Psychiatric other
    -   Stroke
    
    
6. Any experience with a chronic illness results in a higher vaccine uptake with no difference between the prev and current
    -   Hepatitis cirrhosis
    -   Periodontitis
    
7. Experience with chronic illness results in a higher vaccine uptake with the more current experience resulting in a higher uptake
    -   Chronic Pain
    -   Caries
    -   Diabetes
    -   Dyslipdemia
    
Looking at how uptake of the influenza vaccine varies with each illness
```{r}
# dosage
inf_ivd |>
  filter(!is.na(influenza_coverage_dosage)) |>
  select(c(starts_with("respondent_"), influenza_coverage_dosage)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work, respondent_sex, respondent_age)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -influenza_coverage_dosage, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, influenza_coverage_dosage)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    .by = c(illness, illness_experience)
  ) |>
  
  ggplot(aes(x = influenza_coverage_dosage, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  facet_wrap(vars(illness))
```

```{r}
# age
inf_ivd |>
  filter(!is.na(influenza_coverage_age)) |>
  select(c(starts_with("respondent_"), influenza_coverage_age)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work, respondent_sex, respondent_age)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -influenza_coverage_age, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, influenza_coverage_age)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    .by = c(illness, illness_experience)
  ) |>
  
  ggplot(aes(x = influenza_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  facet_wrap(vars(illness))
```

_**Categories for the influenza vaccine**_
1. Expereince with a chronic illnes detracts from the likelihood of being vaccinated. The more recent the experience with the chronic illness, the less likely that the COI is going to get vaccinated with the influena vaccine, Never > Prev > Current
    -   Angina
    -   Asthma
    -   Atopic dermatitis
    -   Cancer
    -   Cataract
    -   Chronic Pain
    -   COPD
    -   Dyslipidemia
    -   Immune abnormalities
    -   Kidney Disease
    -   Stroke

*Characteristics*
    Current < Never
    Prev < Never
    Current < Prev
    
    

2. No experience with X chronic illness results in higher vaccine uptake than any sort of experience with the chronic illness irregardless of previous or current
    -   Allergic Rhinitis

*Characteristics*
    Current < Never
    Prev< Never
    Current == Prev
    
3. Experience with a chronic illness results in a higher vaccine uptake but previous illness is a stronger predictor than current illness
    -   Diabetes
    -   Hypertension
    -   Periodontitis
    -   Pneumonia
    
*Characteristics*
    Current > Never
    Prev > Never
    Current < Prev
    
4. Current experience results in lower uptake as compareed to never having experienced a chronic illness or previous experience

*Characteristics*
    Current < Never
    Prev == Never
    Current < Prev

5. Prev Experience is a predictor of increased uptake (relative to no experience) whilst current experience is a negative predictor of increased uptake
    -   Caries
    -   Hepatitis cirrhosis
    -   Other Psychiatric disorders
    
*Characteristics*
    Current < Never
    Prev > Never
    Current < Prev
    
6. Any experience with a chronic illness results in a higher vaccine uptake with no difference between the prev and current

*Characteristics*
    Current > Never
    Prev > Never
    Current == Prev
    
7. Experience with chronic illness results in a higher vaccine uptake with the more current experience resulting in a higher uptake
    -   Depression
    
    Current > Never 
    Prev > Never
    Current > Prev
**Comparison of trends**
```{r}
# select only columns that correspond to chronic illness names
respondent_chronic_illnesses <- cov_ivd |>
  select(starts_with("respondent_")) |>
  select(- c(respondent_age, respondent_sex, respondent_employment_status, respondent_industry_of_work)) |>
  colnames() 

chronic_illnesses <- c()

# extract names for chronic illnesses
for(i in seq_along(respondent_chronic_illnesses)) {
  str_split_1(respondent_chronic_illnesses[i], pattern = "_") -> x
  chronic_illnesses [i] <- x [[2]] 
}

# manually input categories for influenza and covid vaccine uptake wrt to chronic illnesses
cov_chronic_illness_response <-
  c(3, 7, 7, 5, 4, 5, 2, 6, 7, 3, 5, 5, 5, 5, 6, 5, 2, 7, 3, 5)

inf_chronic_illness_response <-
  c(3, 3, 1, 3, 4, 1, 2, 3, 5, 1, 1, 1, 1, 1, 5 , 1, 1, 1, 7, 5)

chronic_illness_comparison <- data.frame(
  chronic_illnesses, cov_chronic_illness_response, inf_chronic_illness_response
)

chronic_illness_comparison <- chronic_illness_comparison |>
  mutate(
    same_effect = case_when(
    cov_chronic_illness_response == inf_chronic_illness_response ~ "Yes",
    cov_chronic_illness_response != inf_chronic_illness_response ~ "No"
    ),
    
    # covid    
    # how currently having each chronic illness impacts the COI's covid
    # vax uptake compared to those who've never had the specific illness
    cov_current_v_never = case_when(
      cov_chronic_illness_response %in% c(1, 2, 4 ,5) ~ "C<N",
      cov_chronic_illness_response %in% c(3, 6 ,7) ~ "C>N"
    ),
    
    # how previously having each chronic illness impacts the COI's covid
    # vax uptake compared to those who've never had the specific illness
    cov_previous_v_never = case_when(
      cov_chronic_illness_response %in% c(1, 2) ~ "P<N",
      cov_chronic_illness_response %in% c(3, 5, 6, 7) ~ "P>N",
      cov_chronic_illness_response == 4 ~ "P=N"
    ),
    
    # how currently having each chronic illness impacts the COI's covid vax
    # uptake compared to those who previously had the chronic illness
    cov_current_v_prev = case_when(
      cov_chronic_illness_response %in% c(1, 3, 4, 5) ~ "C<P",
      cov_chronic_illness_response == 7 ~ "C>P",
      cov_chronic_illness_response %in% c(2, 6) ~ "C=P"
    ),
    
    # Influenza
    # how currently having each chronic illness impacts the COI's influenza
    # vax uptake compared to those who've never had the specific illness 
    inf_current_v_never = case_when(
      inf_chronic_illness_response %in% c(1, 2, 4 ,5) ~ "C<N",
      inf_chronic_illness_response %in% c(3, 6 ,7) ~ "C>N"
    ),
    
    # how previously having each chronic illness impacts the COI's influneza
    # vax uptake compared to those who've never had the specific illness
    inf_previous_v_never = case_when(
      inf_chronic_illness_response %in% c(1, 2) ~ "P<N",
      inf_chronic_illness_response %in% c(3, 5, 6, 7) ~ "P>N",
      inf_chronic_illness_response == 4 ~ "P=N"
    ),
    
    # how currently having each chronic illness impacts the COI's influenza vax
    # uptake compared to those who previously had the chronic illness
    cov_current_v_prev = case_when(
      cov_chronic_illness_response %in% c(1, 3, 4, 5) ~ "C<P",
      cov_chronic_illness_response == 7 ~ "C>P",
      cov_chronic_illness_response %in% c(2, 6) ~ "C=P"
    )
  )

kable(chronic_illness_comparison, "html")
```


-   **influenza**: A chronic illness is a predictor of lower vaccine uptake in their children, with the usual order of vaccine uptake being Never > Prev > Curr
    -     Given that influenza is a endemic disease, it would make sense that individuals who are more health cautious are less likely to get the disease and thus, will be more willing to vaccinate
    -     This is applicable to the following (catgory 1): dyslipedemia, atopic dermatitis, cataract, angina, stroke, copd, kidney disease, immune abnormalities, cnacer, chronic pain, depression

-   **cov**: Previously having a chronic illness is a predictor of higher vaccine uptake in the coi,
the most common order is Prev > Never > Curr sometimes followed by Prev > Curr > Nev
    -   Perhaps previous uptake has taugth them to be more wary? whilst those currently affected are more cautious of serious impacts 


# education
Exploring the breakdown of education categories between moms and dads
```{r}
ivd |> 
  filter(child_of_interest == 1 & !is.na(mother_highest_education)) |>
  summarise(count = n(), .by = mother_highest_education) |>
  arrange(mother_highest_education)

ivd |>
  filter(child_of_interest == 1 & !is.na(father_highest_education)) |>
  summarise(count = n(), .by = father_highest_education) |>
  arrange(father_highest_education)
```

Examining how the mother and father's highest educational attainments affect the uptake of vaccines indepdendently
```{r}
# educational attainment function
test_function_stratify_data <- function(dataset, variable, coverage) {
  
  dataset |>
    filter(!is.na(coverage) & !is.na(variable)) |>
    summarise(count = n(), .by = c(variable, coverage)) |>
    mutate(proportion = count/sum(count), .by = variable) ->
    stratified_data
  
  return(stratified_data)
}


test_function_stratify_data(cov_ivd, mother_highest_education, covid_coverage_age) |>
  ggplot(aes(x = covid_coverage_age, y = proportion)) +
  geom_col(aes(fill = mother_highest_education), position = "dodge")

#-----------------------------------------------------------------------------
# covid vaccine
# covid vax coverage with mothers' educational attainments
cov_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_highest_education)) |>
  summarise(count = n(), .by = c(mother_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = mother_highest_education) |>

  ggplot(aes(x = covid_coverage_age, y = proportion)) +
  geom_col(aes(fill = mother_highest_education), position = "dodge")

# covid vax coverage with fathers' highest educational attainments
cov_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(father_highest_education)) |>
  summarise(count = n(), .by = c(father_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = father_highest_education) |>

  ggplot(aes(x = covid_coverage_age, y = proportion)) +
  geom_col(aes(fill = father_highest_education), position = "dodge")

# influenza vaccine
# covid vax coverage with mothers' educational attainments
inf_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_highest_education)) |>
  summarise(count = n(), .by = c(mother_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = mother_highest_education) |>

  ggplot(aes(x = influenza_coverage_age, y = proportion)) +
  geom_col(aes(fill = mother_highest_education), position = "dodge")

# influenza vax coverage with father's highest educatioinal attainment
inf_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(father_highest_education)) |>
  summarise(count = n(), .by = c(father_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = father_highest_education) |>

  ggplot(aes(x = influenza_coverage_age, y = proportion)) +
  geom_col(aes(fill = father_highest_education), position = "dodge")
```

Now Examining how different combinations of highest educational attainments in mothers and fathers affects the uptake of vaccines in the COI
```{r}
# examine how covid vaccine coverage in the COI varies with different combinations of educational attainment
cov_ivd |> 
  filter(
    child_of_interest == 1 & !is.na(covid_coverage_age)
  ) |>
  summarise(count = n(), .by = c(mother_highest_education, father_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(mother_highest_education, father_highest_education)) -> cov_age_father_mother_ed

# Covid vax uptake, varying mother's highest educational attainment for each educational attainment of the father
cov_age_father_mother_ed |>
  ggplot() +
  geom_col(aes(x = father_highest_education , y = proportion, fill = covid_coverage_age)) +
  facet_grid(cols = vars(mother_highest_education)) +
  labs(title = "COI's Covid vaccine coverage with age depending on their mother (each column) \n and father's (x) maximum education")

# Covid vax uptake, varying father's highest educational attainment for each educational attainment of the mother
cov_age_father_mother_ed |>
  ggplot() +
  geom_col(aes(x = mother_highest_education , y = proportion, fill = covid_coverage_age)) +
  facet_grid(cols = vars(father_highest_education)) +
  labs(title = "COI's Covid vaccine coverage with age depending on their father (each column) \n and mother's (x) maximum education")

# examine how influenza vaccine coverage in the COI varies with different combinations of educational attainment
inf_ivd |> 
  filter(
    child_of_interest == 1 & !is.na(influenza_coverage_age)) |>
  mutate(
    mother_highest_education = factor(mother_highest_education),
    father_highest_education = factor(father_highest_education)
  ) |>
  summarise(count = n(), .by = c(mother_highest_education, father_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(mother_highest_education, father_highest_education)) -> inf_age_father_mother_ed

# influenza vax uptake, varying mother's highest educational attainment for each educational attainment of the father
inf_age_father_mother_ed |>
  ggplot() +
  geom_col(aes(x = father_highest_education , y = proportion, fill = influenza_coverage_age)) +
  facet_grid(cols = vars(mother_highest_education), drop = TRUE) +
  labs(title = "COI's Influenza vaccine coverage with age depending on their \n mother (each column)  and father's (x) maximum education")

# influenza vax uptake, varying father's highest educational attainment for each educational attainment of the mother
inf_age_father_mother_ed |>
  ggplot() +
  geom_col(aes(x = mother_highest_education , y = proportion, fill = influenza_coverage_age)) +
  facet_grid(cols = vars(father_highest_education), drop = TRUE) +
  labs(title = "COI's Influenza vaccine coverage with age depending on their \n father's (each column) and mother's (x) maximum education")
```
Looking at the influenza data it seems as if the proportion of children vaccinated increases much more with respect to the mother's highest educational attainment as opposed to the father's highest educational attainment - as can be seen from the steeper increases in propritions within each father education band, or the uniform rise in influenza vaccination levles moving across columns of differing highest mother educations

Furthermore, education elvels do seem to have a greater impact on the uptake of influenza vaccines as opposed to the uptake of covid vaccines.

