---
title: "04_exploratory_test"
format: 
  html:
      self-contained: false
      
execute:
  eval: true
  echo: true
  warning: false
---

## Load Packages
These are the packages that have been used throughout the following document: `here`, `tidyverse`, `lubridate`, `knitr`
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(kableExtra)
library(binom)

# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

## Reading data and combining
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )


# Factorising the data

cov <- cov |>
  mutate(covid_coverage_dosage = factor(covid_coverage_dosage, levels = c(0, 1, 2, 3)))

inf <- inf |>
  mutate(influenza_coverage_dosage = factor(influenza_coverage_dosage, levels = c(0, 1, 2)))


# Creating data frames for bivariate and multivariate analysis
# influenza and independent variable data
inf_ivd <- bind_cols(inf, ivd)

# covid and independent variable data
cov_ivd <- bind_cols(cov, ivd)
```

## child's number of parents, stratified by single mother or single father
examinig how the number of parents a child has (2, single father or single mother) affects the child's uptake of the:

covid vaccine
```{r}


function_stratify_child_parents <- 
function(data) {
  mutate(
    data,
    child_parents_strat = case_when(
      child_parents == 2 ~ "both",
      child_parents == 1 & parent_1_sex == 0 ~ "father only",
      child_parents == 1 & parent_1_sex == 1 ~ "mother only"
    ) 
  )
}

cov_ivd |> 
  function_stratify_child_parents() -> cov_child_parents_strat

inf_ivd |>
  function_stratify_child_parents() -> inf_child_parents_strat

  
cov_child_parents_strat |>
  function_data_stratify(child_parents_strat, as.factor, covid_coverage_age) |>
  function_plot_proportion_cols(child_parents_strat, covid_coverage_age) +
  function_plot_label_count(child_parents_strat, covid_coverage_age)

cov_child_parents_strat |>
  function_data_stratify(child_parents_strat, as.factor, covid_coverage_dosage) |>
  function_plot_proportion_cols(child_parents_strat, covid_coverage_dosage) +
  function_plot_label_count(child_parents_strat, covid_coverage_dosage)

inf_child_parents_strat |>
  function_data_stratify(child_parents_strat, as.factor, influenza_coverage_age) |>
  function_plot_proportion_cols(child_parents_strat, influenza_coverage_age) +
  function_plot_label_count(child_parents_strat, influenza_coverage_age)

inf_child_parents_strat |>
  function_data_stratify(child_parents_strat, as.factor, influenza_coverage_dosage) |>
  function_plot_proportion_cols(child_parents_strat, influenza_coverage_dosage) +
  function_plot_label_count(child_parents_strat, influenza_coverage_dosage)
```
For the covid vaccine, children with single mothers and fathers both display an increased uptake of the covid vaccination as compare to children with both parents. However, for the influenza vaccine, children with single mothers display a lower uptake of the vaccine as compared to children with a single father and with both parents

## parent's age
Examining how the uptake of the influenza and covid vaccines by the COI varies with the responding parent's age

```{r}
cov_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  summarise(count = n(), .by = c(parent_1_age, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = parent_1_age) |>
  
  ggplot(aes(x = parent_1_age, y = proportion)) +
  geom_point(aes(colour = covid_coverage_age)) +
  xlim(NA, 60) +
  geom_smooth(aes(colour = covid_coverage_age), method = "loess")



inf_ivd |>
  filter(!is.na(influenza_coverage_age)) |>
  summarise(count = n(), .by = c(parent_1_age, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = parent_1_age) |>
  
  ggplot(aes(x = parent_1_age, y = proportion)) +
  geom_point(aes(colour = influenza_coverage_age)) +
  xlim(NA, 60) +
  geom_smooth(aes(colour = influenza_coverage_age), method = "loess")
```

## chronic illnesses
Looking at chronic illness status by the age of the parent
```{r}
# chronic illness status as a proportion for parents of each age
cov_ivd |>
  filter(!is.na(parent_chronic_illness) & child_of_interest == 1) |>
  
  # group variables for <18y/o and > 60y/o
  mutate(parent_1_age = case_when(
    parent_1_age <= 18 ~ 18,
    parent_1_age > 18 & parent_1_age < 60 ~ parent_1_age,
    parent_1_age >= 60 ~ 60
  )) |>
  summarise(count = n(), .by = c(parent_chronic_illness, parent_1_age)) |>
  mutate(proportion = count/sum(count), .by = (parent_1_age)) |>

  
  ggplot() +
  geom_point(aes(x = parent_1_age, y = proportion, colour = parent_chronic_illness))
  #facet_wrap(vars(parent_chronic_illness))

cov_ivd |>
filter(!is.na(covid_coverage_age) & child_of_interest == 1) |>
  mutate(count = n(), .by = c(parent_1_age, parent_chronic_illness)) |>
  ggplot() +
  geom_histogram(aes(x = parent_1_age, fill = covid_coverage_age), position = "fill", binwidth = 3) +
  facet_wrap(vars(parent_chronic_illness))

inf_ivd |>
filter(!is.na(influenza_coverage_age) & child_of_interest == 1) |>
  mutate(count = n(), .by = c(parent_1_age, parent_chronic_illness)) |>
  ggplot() +
  geom_histogram(aes(x = parent_1_age, fill = influenza_coverage_age), position = "fill", binwidth = 3) +
  facet_wrap(vars(parent_chronic_illness))
```
How chronic illness status varies in the responding parent based on the number of paretns in the same household
```{r}
cov_ivd |>
  filter(child_of_interest == 1) |>
  summarise(count = n(), .by = c(child_parents, parent_chronic_illness)) |>
  mutate(child_parents = factor(child_parents)) |>
  mutate(proportion = count/sum(count), .by = child_parents) |>
  ggplot(aes(x = parent_chronic_illness, y = proportion)) +
  geom_col(aes(fill = child_parents), position = "dodge")
```

Looknig at how vaccine uptake varies with every single chronic illnesss
```{r}
# dosage
inf_ivd |>
  filter(!is.na(influenza_coverage_age)) |>
  select(c(starts_with("respondent_"), influenza_coverage_age)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -influenza_coverage_age, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, influenza_coverage_age)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    .by = c(illness, illness_experience)
  ) |>
  
   # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    
    # variables for confidence intervals of proportions, x = successful cases, n = total cases
    x = count, 
    n = sum(count),
    .by = c(illness, illness_experience)
  ) |>
  
  # rename the illness variables
  mutate(illness = str_remove(illness, "respondent_")) |>
  mutate(
    illness = ifelse(
      illness == "angina",
      "angina pectoris & MI",
      illness)
  ) -> influenza_age_stratified_chronic_illnesses
  
# agresti coulli confidence intervals
influenza_age_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_agresti = binom.agresti.coull(x, n)$lower,
    upper_CI_agresti = binom.agresti.coull(x, n)$upper
  ) |>
 
  ggplot(aes(x = influenza_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_agresti, ymax = upper_CI_agresti, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, influenza_coverage_age) +
  facet_wrap(vars(illness)) +
  labs(title = "with agresti coulli intervals")

# wilson confidence intervals
influenza_age_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_wilson = binom.wilson(x, n)$lower,
    upper_CI_wilson = binom.wilson(x, n)$upper
  ) |>
 
  ggplot(aes(x = influenza_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_wilson, ymax = upper_CI_wilson, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, influenza_coverage_age) +
  facet_wrap(vars(illness)) +
  xlab("Degree of coverage COI has obtained from the influenza vaccine \n
    based on their parent's experience with different chronic illnesses") + 
  theme(
    axis.title.x = element_text(size = 10),
    legend.title = element_text(size = 9),
    aspect.ratio = 6.5/11
  )
  #ggsave(
  #  "Child's influenza uptake by parent's chronic illness",
   # path = "C:\Users\kevin\Documents\obsidian vaccine uptake\Attachments",
  #  )
```

```{r}
# coverage
cov_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  select(c(starts_with("respondent_"), covid_coverage_age)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -covid_coverage_age, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, covid_coverage_age)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    
    # variables for confidence intervals of proportions, x = successful cases, n = total cases
    x = count, 
    n = sum(count),
    .by = c(illness, illness_experience)
  ) |>
  
  # rename the illness variables
  mutate(illness = str_remove(illness, "respondent_")) |>
  mutate(
    illness = ifelse(
      illness == "angina",
      "angina pectoris & MI",
      illness)
  )-> covid_age_stratified_chronic_illnesses
 
# agresti coulli confidence intervals
covid_age_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_agresti = binom.agresti.coull(x, n)$lower,
    upper_CI_agresti = binom.agresti.coull(x, n)$upper
  ) |>
 
  ggplot(aes(x = covid_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_agresti, ymax = upper_CI_agresti, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, covid_coverage_age) +
  facet_wrap(vars(illness)) +
  labs(title = "with agresti coulli intervals")

# wilson confidence intervals
covid_age_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_wilson = binom.wilson(x, n)$lower,
    upper_CI_wilson = binom.wilson(x, n)$upper
  ) |>
 
  ggplot(aes(x = covid_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_wilson, ymax = upper_CI_wilson, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, covid_coverage_age) +
  facet_wrap(vars(illness)) +
  labs(
    fill = "experience with illness", size = 4
  ) +
  xlab("Degree of coverage COI has obtained from the covid vaccine \n
    based on their parent's experience with different chronic illnesses") + 
  theme(
    axis.title.x = element_text(size = 10),
    legend.title = element_text(size = 9),
    aspect.ratio = 6.5/11
  )
```

_**Categories for the Covid vaccine**_
1. Expereince with a chronic illnes detracts from the likelihood of being vaccinated. The more recent the experience with the chronic illness, the less likely that the COI is going to get vaccinated with the influena vaccine, Never > Prev > Current
  
    
2. No experience with X chronic illness results in higher vaccine uptake than any sort of experience with the chronic illness irregardless of previous or current
    -   allergic rhinitis
    -   Cancer

3. Experience with a chronic illness results in a higher vaccine uptake but previous illness is a stronger predictor than current illness 
    -   Depression
    -   Cataract
    -   Hypertension
  
4. Current experience results in lower uptake as compareed to never having experienced a chronic illness or previous experience
    -   Asthmaa
    
5. Prev Experience is a predictor of increased uptake (relative to no experience) whilst current experience is a negative predictor of increased uptake
    -   Angina
    -   Atopic Derma
    -   COPD
    -   Abnormalities
    -   Kidney Disease
    -   Pneumonia
    -   Psychiatric other
    -   Stroke
    
    
6. Any experience with a chronic illness results in a higher vaccine uptake with no difference between the prev and current
    -   Hepatitis cirrhosis
    -   Periodontitis
    
7. Experience with chronic illness results in a higher vaccine uptake with the more current experience resulting in a higher uptake
    -   Chronic Pain
    -   Caries
    -   Diabetes
    -   Dyslipdemia
    
Looking at how uptake of the influenza vaccine varies with each illness
```{r}
# dosage
inf_ivd |>
  filter(!is.na(influenza_coverage_dosage)) |>
  select(c(starts_with("respondent_"), influenza_coverage_dosage)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -influenza_coverage_dosage, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, influenza_coverage_dosage)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    
    # variables for confidence intervals of proportions, x = successful cases, n = total cases
    x = count, 
    n = sum(count),
    .by = c(illness, illness_experience)
  ) -> influenza_dosage_stratified_chronic_illnesses
 
# agresti coulli confidence intervals
influenza_dosage_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_agresti = binom.agresti.coull(x, n)$lower,
    upper_CI_agresti = binom.agresti.coull(x, n)$upper
  ) |>
 
  ggplot(aes(x = influenza_coverage_dosage, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_agresti, ymax = upper_CI_agresti, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, influenza_coverage_dosage) +
  facet_wrap(vars(illness)) +
  labs(title = "with agresti coulli intervals")

# wilson confidence intervals
influenza_dosage_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_wilson = binom.wilson(x, n)$lower,
    upper_CI_wilson = binom.wilson(x, n)$upper
  ) |>
 
  ggplot(aes(x = influenza_coverage_dosage, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_wilson, ymax = upper_CI_wilson, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, influenza_coverage_dosage) +
  facet_wrap(vars(illness)) +
  labs(title = "with wilson intervals")
  
```

```{r}
# age
inf_ivd |>
  filter(!is.na(influenza_coverage_age)) |>
  select(c(starts_with("respondent_"), influenza_coverage_age)) |>
  select(- c(respondent_employment_status, respondent_industry_of_work)) |>
#  select(
#    all_of(c("covid_coverage_dosage", chronic_illnesses))
#  ) |>
  pivot_longer(
    cols = -influenza_coverage_age, 
    names_to = "illness", 
    values_to = "status",
    values_ptypes = list(status = integer())
  ) |>
  mutate(
    illness_experience = case_when(
      status == 1 ~ "Never", # never had a chronic illness
      status == 2 ~ "Previously" ,# previous illness
      status %in% 3:5 ~ "Currently"# current chronic illness
    ) |>
    factor(
      levels = c("Never", "Previously", "Currently")
    )
  ) |>
  # number of children of each dosage for each status of their parent's chronic illness for each illness
  summarise(
    count = n(), .by = c(illness, illness_experience, influenza_coverage_age)
  ) |>
  
  # calculate proportions of each disease and each dosage by status
  mutate(
    proportions = count/sum(count),
    
    # variables for confidence intervals of proportions, x = successful cases, n = total cases
    x = count, 
    n = sum(count),
    .by = c(illness, illness_experience)
  ) -> influenza_age_stratified_chronic_illnesses
 
# agresti coulli confidence intervals
influenza_age_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_agresti = binom.agresti.coull(x, n)$lower,
    upper_CI_agresti = binom.agresti.coull(x, n)$upper
  ) |>
 
  ggplot(aes(x = influenza_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_agresti, ymax = upper_CI_agresti, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, influenza_coverage_age) +
  facet_wrap(vars(illness)) +
  labs(title = "with agresti coulli intervals")

# wilson confidence intervals
influenza_age_stratified_chronic_illnesses |>
  
  #caluclate the confidence intervals
  mutate(
    lower_CI_wilson = binom.wilson(x, n)$lower,
    upper_CI_wilson = binom.wilson(x, n)$upper
  ) |>
 
  ggplot(aes(x = influenza_coverage_age, y = proportions)) +
  geom_col(aes(fill = illness_experience), position = "dodge") +
  geom_errorbar(
    aes(ymin = lower_CI_wilson, ymax = upper_CI_wilson, group = illness_experience),
    position = "dodge"
  ) +
  function_plot_label_count(illness_experience, influenza_coverage_age) +
  facet_wrap(vars(illness)) +
  labs(title = "with wilson intervals")
```

_**Categories for the influenza vaccine**_
1. Expereince with a chronic illnes detracts from the likelihood of being vaccinated. The more recent the experience with the chronic illness, the less likely that the COI is going to get vaccinated with the influena vaccine, Never > Prev > Current
    -   Angina
    -   Asthma
    -   Atopic dermatitis
    -   Cancer
    -   Cataract
    -   Chronic Pain
    -   COPD
    -   Dyslipidemia
    -   Immune abnormalities
    -   Kidney Disease
    -   Stroke

*Characteristics*
    Current < Never
    Prev < Never
    Current < Prev
    
    

2. No experience with X chronic illness results in higher vaccine uptake than any sort of experience with the chronic illness irregardless of previous or current
    -   Allergic Rhinitis

*Characteristics*
    Current < Never
    Prev< Never
    Current == Prev
    
3. Experience with a chronic illness results in a higher vaccine uptake but previous illness is a stronger predictor than current illness
    -   Diabetes
    -   Hypertension
    -   Periodontitis
    -   Pneumonia
    
*Characteristics*
    Current > Never
    Prev > Never
    Current < Prev
    
4. Current experience results in lower uptake as compareed to never having experienced a chronic illness or previous experience

*Characteristics*
    Current < Never
    Prev == Never
    Current < Prev

5. Prev Experience is a predictor of increased uptake (relative to no experience) whilst current experience is a negative predictor of increased uptake
    -   Caries
    -   Hepatitis cirrhosis
    -   Other Psychiatric disorders
    
*Characteristics*
    Current < Never
    Prev > Never
    Current < Prev
    
6. Any experience with a chronic illness results in a higher vaccine uptake with no difference between the prev and current

*Characteristics*
    Current > Never
    Prev > Never
    Current == Prev
    
7. Experience with chronic illness results in a higher vaccine uptake with the more current experience resulting in a higher uptake
    -   Depression
    
    Current > Never 
    Prev > Never
    Current > Prev
**Comparison of trends**
```{r}
# select only columns that correspond to chronic illness names
respondent_chronic_illnesses <- cov_ivd |>
  select(starts_with("respondent_")) |>
  select(- c(respondent_employment_status, respondent_industry_of_work)) |>
  colnames() 

chronic_illnesses <- c()

# extract names for chronic illnesses
for(i in seq_along(respondent_chronic_illnesses)) {
  str_split_1(respondent_chronic_illnesses[i], pattern = "_") -> x
  chronic_illnesses [i] <- x [[2]] 
}

# manually input categories for influenza and covid vaccine uptake wrt to chronic illnesses
cov_chronic_illness_response <-
  c(3, 7, 7, 5, 4, 5, 2, 6, 7, 3, 5, 5, 5, 5, 6, 5, 2, 7, 3, 5)

inf_chronic_illness_response <-
  c(3, 3, 1, 3, 4, 1, 2, 3, 5, 1, 1, 1, 1, 1, 5 , 1, 1, 1, 7, 5)

chronic_illness_comparison <- data.frame(
  chronic_illnesses, cov_chronic_illness_response, inf_chronic_illness_response
)

chronic_illness_comparison <- chronic_illness_comparison |>
  mutate(
    same_effect = case_when(
    cov_chronic_illness_response == inf_chronic_illness_response ~ "Yes",
    cov_chronic_illness_response != inf_chronic_illness_response ~ "No"
    ),
    
    # covid    
    # how currently having each chronic illness impacts the COI's covid
    # vax uptake compared to those who've never had the specific illness
    cov_current_v_never = case_when(
      cov_chronic_illness_response %in% c(1, 2, 4 ,5) ~ "C<N",
      cov_chronic_illness_response %in% c(3, 6 ,7) ~ "C>N"
    ),
    
    # how previously having each chronic illness impacts the COI's covid
    # vax uptake compared to those who've never had the specific illness
    cov_previous_v_never = case_when(
      cov_chronic_illness_response %in% c(1, 2) ~ "P<N",
      cov_chronic_illness_response %in% c(3, 5, 6, 7) ~ "P>N",
      cov_chronic_illness_response == 4 ~ "P=N"
    ),
    
    # how currently having each chronic illness impacts the COI's covid vax
    # uptake compared to those who previously had the chronic illness
    cov_current_v_prev = case_when(
      cov_chronic_illness_response %in% c(1, 3, 4, 5) ~ "C<P",
      cov_chronic_illness_response == 7 ~ "C>P",
      cov_chronic_illness_response %in% c(2, 6) ~ "C=P"
    ),
    
    # Influenza
    # how currently having each chronic illness impacts the COI's influenza
    # vax uptake compared to those who've never had the specific illness 
    inf_current_v_never = case_when(
      inf_chronic_illness_response %in% c(1, 2, 4 ,5) ~ "C<N",
      inf_chronic_illness_response %in% c(3, 6 ,7) ~ "C>N"
    ),
    
    # how previously having each chronic illness impacts the COI's influneza
    # vax uptake compared to those who've never had the specific illness
    inf_previous_v_never = case_when(
      inf_chronic_illness_response %in% c(1, 2) ~ "P<N",
      inf_chronic_illness_response %in% c(3, 5, 6, 7) ~ "P>N",
      inf_chronic_illness_response == 4 ~ "P=N"
    ),
    
    # how currently having each chronic illness impacts the COI's influenza vax
    # uptake compared to those who previously had the chronic illness
    cov_current_v_prev = case_when(
      cov_chronic_illness_response %in% c(1, 3, 4, 5) ~ "C<P",
      cov_chronic_illness_response == 7 ~ "C>P",
      cov_chronic_illness_response %in% c(2, 6) ~ "C=P"
    )
  )

kable(chronic_illness_comparison, "html")
```


-   **influenza**: A chronic illness is a predictor of lower vaccine uptake in their children, with the usual order of vaccine uptake being Never > Prev > Curr
    -     Given that influenza is a endemic disease, it would make sense that individuals who are more health cautious are less likely to get the disease and thus, will be more willing to vaccinate
    -     This is applicable to the following (catgory 1): dyslipedemia, atopic dermatitis, cataract, angina, stroke, copd, kidney disease, immune abnormalities, cnacer, chronic pain, depression

-   **cov**: Previously having a chronic illness is a predictor of higher vaccine uptake in the coi,
the most common order is Prev > Never > Curr sometimes followed by Prev > Curr > Nev
    -   Perhaps previous uptake has taugth them to be more wary? whilst those currently affected are more cautious of serious impacts 

## Marital status combining all unmarried categories vs marital status by all categories
```{r}
# covid vaccine
# un-combined marital statuses
function_data_stratify(cov_ivd, parents_marital_status, as.factor, covid_coverage_age) |>
  function_calculate_confidence_intervals(parents_marital_status, "wilson") |>
  function_plot_proportion_cols(parents_marital_status, covid_coverage_age) +
  function_plot_confidence_intervals(parents_marital_status) +
  function_plot_label_count(parents_marital_status, covid_coverage_age) +
  scale_fill_discrete(labels = c("married", "bereaved", "divorced", "unmarried"))

# combined marital statuses
function_data_stratify(cov_ivd, test_parents_marital_status, as.factor, covid_coverage_age) |>
  function_calculate_confidence_intervals(test_parents_marital_status, "wilson") |>
  function_plot_proportion_cols(test_parents_marital_status, covid_coverage_age) +
  function_plot_label_count(test_parents_marital_status, covid_coverage_age) +
  function_plot_confidence_intervals(test_parents_marital_status) +
  scale_fill_discrete(labels = c("married", "not married"))

# influenza vaccine
# un-combined marital statuses
function_data_stratify(inf_ivd, parents_marital_status, as.factor, influenza_coverage_age) |>
  function_calculate_confidence_intervals(parents_marital_status, "wilson") |>
  function_plot_proportion_cols(parents_marital_status, influenza_coverage_age) +
  function_plot_label_count(parents_marital_status, influenza_coverage_age) +
  function_plot_confidence_intervals(parents_marital_status) +
  scale_fill_discrete(labels = c("married", "bereaved", "divorced", "unmarried"))

# combined marital statuses
function_data_stratify(inf_ivd, test_parents_marital_status, as.factor, influenza_coverage_age) |>
  function_calculate_confidence_intervals(test_parents_marital_status, "wilson") |>  
  function_plot_proportion_cols(test_parents_marital_status, influenza_coverage_age) +
  function_plot_label_count(test_parents_marital_status, influenza_coverage_age) +
  function_plot_confidence_intervals(test_parents_marital_status) +
  scale_fill_discrete(labels = c("married", "not married"))
```
As is consistent when using either combined or uncombined marital statuses, being divorced or unmarried (uncombined) or not married (combined) are both positively assocaited with higher uptake of full covid vacination as compareid to being married. This trend is either reversed for the covid vaccination or negilgible .(we have excluded COI associated with bereavement due to the small sample size)

## Parent's education
Exploring the breakdown of education categories between moms and dads
```{r}
ivd |> 
  filter(child_of_interest == 1 & !is.na(mother_highest_education)) |>
  summarise(count = n(), .by = mother_highest_education) |>
  arrange(mother_highest_education)

ivd |>
  filter(child_of_interest == 1 & !is.na(father_highest_education)) |>
  summarise(count = n(), .by = father_highest_education) |>
  arrange(father_highest_education)
```

Examining how the mother and father's highest educational attainments affect the uptake of vaccines indepdendently
```{r}
# covid vaccine
# covid vax coverage with mothers' educational attainments
cov_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_highest_education)) |>
  summarise(count = n(), .by = c(mother_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = mother_highest_education) |>

  ggplot(aes(x = covid_coverage_age, y = proportion)) +
  geom_col(aes(fill = mother_highest_education), position = "dodge") +
  function_plot_label_count(mother_highest_education, coverage = covid_coverage_age) +
  labs(title = "proportion of COI who have obtained no, partial and full coverage of the covid\nvaccination with respect to the highest educational attainment of their mother") +
  xlab("degree of coverage from the covid vaccine")


# covid vax coverage with fathers' highest educational attainments
cov_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(father_highest_education)) |>
  summarise(count = n(), .by = c(father_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = father_highest_education) |>

  ggplot(aes(x = covid_coverage_age, y = proportion)) +
  geom_col(aes(fill = father_highest_education), position = "dodge") +
  function_plot_label_count(father_highest_education, coverage = covid_coverage_age) +
  labs(title = "proportion of COI who have obtained no, partial and full coverage of the covid\nvaccination with respect to the highest educational attainment of their father") +
  xlab("degree of coverage from the covid vaccine")

# influenza vaccine
# covid vax coverage with mothers' educational attainments
inf_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_highest_education)) |>
  summarise(count = n(), .by = c(mother_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = mother_highest_education) |>

  ggplot(aes(x = influenza_coverage_age, y = proportion)) +
  geom_col(aes(fill = mother_highest_education), position = "dodge") +
  function_plot_label_count(mother_highest_education, influenza_coverage_age) +
  labs(title = "proportion of COI who have obtained no, partial and full coverage of the influenza\nvaccination with respect to the highest educational attainment of their mother") +
  xlab("degree of coverage from the influenza vaccine")

# influenza vax coverage with father's highest educatioinal attainment
inf_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(father_highest_education)) |>
  summarise(count = n(), .by = c(father_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = father_highest_education) |>

  ggplot(aes(x = influenza_coverage_age, y = proportion)) +
  geom_col(aes(fill = father_highest_education), position = "dodge") +
  function_plot_label_count(father_highest_education, coverage = influenza_coverage_age) +
  labs(title = "proportion of COI who have obtained no, partial and full coverage of the influenza\nvaccination with respect to the highest educational attainment of their fathers") +
  xlab("degree of coverage from the influenza vaccine")
```

Now Examining how different combinations of highest educational attainments in mothers and fathers affects the uptake of vaccines in the COI
```{r}
# examine how covid vaccine coverage in the COI varies with different combinations of educational attainment
cov_ivd |> 
  filter(
    child_of_interest == 1 & !is.na(covid_coverage_age) &
    !is.na(mother_highest_education) & !is.na(father_highest_education)
  ) |>
  summarise(count = n(), .by = c(mother_highest_education, father_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(mother_highest_education, father_highest_education)) -> cov_age_father_mother_ed

# Covid vax uptake, varying mother's highest educational attainment for each educational attainment of the father
cov_age_father_mother_ed |>
  ggplot(aes(x = father_highest_education , y = proportion)) +
  geom_col(aes(fill = covid_coverage_age)) +
  facet_grid(cols = vars(mother_highest_education)) +
  labs(title = "COI's Covid vaccine coverage with age depending on their mother (each column) \n and father's (x) maximum education") +
  geom_text(aes(group = covid_coverage_age, label = count), position = position_fill(vjust = 0.5), size = 3)

# Covid vax uptake, varying father's highest educational attainment for each educational attainment of the mother
cov_age_father_mother_ed |>
  ggplot(aes(x = mother_highest_education , y = proportion)) +
  geom_col(aes(fill = covid_coverage_age)) +
  facet_grid(cols = vars(father_highest_education)) +
  labs(title = "COI's Covid vaccine coverage with age depending on their father (each column) \n and mother's (x) maximum education") +
  geom_text(aes(group = covid_coverage_age, label = count), position = position_fill(vjust = 0.5), size = 3)

# examine how influenza vaccine coverage in the COI varies with different combinations of educational attainment
inf_ivd |> 
  filter(
    child_of_interest == 1 & !is.na(influenza_coverage_age) &
    !is.na(mother_highest_education) & !is.na(father_highest_education)) |>
  mutate(
    mother_highest_education = factor(mother_highest_education),
    father_highest_education = factor(father_highest_education)
  ) |>
  summarise(count = n(), .by = c(mother_highest_education, father_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(mother_highest_education, father_highest_education)) -> inf_age_father_mother_ed

# influenza vax uptake, varying mother's highest educational attainment for each educational attainment of the father
inf_age_father_mother_ed |>
  ggplot(aes(x = father_highest_education , y = proportion)) +
  geom_col(aes(fill = influenza_coverage_age)) +
  facet_grid(cols = vars(mother_highest_education), drop = TRUE) +
  labs(title = "COI's Influenza vaccine coverage with age depending on their \n mother (each column)  and father's (x) maximum education") +
  geom_text(aes(group = influenza_coverage_age, label = count), position = position_fill(vjust = 0.5), size = 3)

# influenza vax uptake, varying father's highest educational attainment for each educational attainment of the mother
inf_age_father_mother_ed |>
  ggplot(aes(x = mother_highest_education, y = proportion)) +
  geom_col(aes(x = mother_highest_education , y = proportion, fill = influenza_coverage_age)) +
  facet_grid(cols = vars(father_highest_education), drop = TRUE) +
  labs(title = "COI's Influenza vaccine coverage with age depending on their \n father's (each column) and mother's (x) maximum education") +
  geom_text(aes(group = influenza_coverage_age, label = count), position = position_fill(vjust = 0.5), size = 3)
```
Looking at the influenza data it seems as if the proportion of children vaccinated increases much more with respect to the mother's highest educational attainment as opposed to the father's highest educational attainment - as can be seen from the steeper increases in propritions within each father education band, or the uniform rise in influenza vaccination levles moving across columns of differing highest mother educations

Furthermore, education elvels do seem to have a greater impact on the uptake of influenza vaccines as opposed to the uptake of covid vaccines.

## Parents education, but with JC and VC seperated from tertiary with
A breakdown of parents by the test educations
```{r}
ivd |>
  filter(!is.na(child_of_interest) & !is.na(test_mother_highest_education)) |>
  summarise(n(), .by = test_mother_highest_education)
```

mothers' highest education
```{r}
# covid coverage by age by mothers' higest education
cov_ivd |>
  function_data_stratify(test_mother_highest_education, as.factor, covid_coverage_age) |>
  function_calculate_confidence_intervals(test_mother_highest_education, "wilson") |>
  function_plot_proportion_cols(test_mother_highest_education, covid_coverage_age) +
  function_plot_label_count(test_mother_highest_education, covid_coverage_age) +
  function_plot_confidence_intervals(test_mother_highest_education)

inf_ivd |>
  function_data_stratify(test_mother_highest_education, as.factor, influenza_coverage_age) |>
  function_calculate_confidence_intervals(test_mother_highest_education, "wilson") |>
  function_plot_proportion_cols(test_mother_highest_education, influenza_coverage_age) +
  function_plot_label_count(test_mother_highest_education, influenza_coverage_age) +
  function_plot_confidence_intervals(test_mother_highest_education)
```
father's highest education
```{r}
# covid coverage by age by mothers' higest education
cov_ivd |>
  function_data_stratify(test_father_highest_education, as.factor, covid_coverage_age) |>
  function_plot_proportion_cols(test_father_highest_education, covid_coverage_age) +
  function_plot_label_count(test_father_highest_education, covid_coverage_age)

inf_ivd |>
  function_data_stratify(test_father_highest_education, as.factor, influenza_coverage_age) |>
  function_plot_proportion_cols(test_father_highest_education, influenza_coverage_age) +
  function_plot_label_count(test_father_highest_education, influenza_coverage_age)
```

## Unstratified Household Income vs stratifiged household income
```{r}
# comparing gruoping and ungrouping of household income and how it differs for influenza vax uptake
# extended plot of how covid coverage varies with test household income (ungrouped)
function_data_stratify(cov_ivd, test_household_income, as.numeric, covid_coverage_age) |>

  # dot plot of proportion of COI with each coverage status for each income bracket
  function_plot_proportion_dots(test_household_income, covid_coverage_age) +
  geom_smooth(aes(colour = covid_coverage_age), method = "lm")

# unextended plot of grouped household income
function_data_stratify(cov_ivd, household_income, as.numeric, covid_coverage_age) |>

  # dot plot of proportion of COI with each coverage status for each income bracket
  function_plot_proportion_dots(household_income, covid_coverage_age) +
  geom_smooth(aes(colour = covid_coverage_age), method = "lm")




# comparing gruoping and ungrouping of household income and how it differs for influenza vax uptake
# extended plot of how influenza coverage varies with test household income (ungrouped)
function_data_stratify(inf_ivd, test_household_income, as.numeric, influenza_coverage_age) |>
  
  # dot plot of proportion of COI with each influenza vax coverage status by income bracket
  function_plot_proportion_dots(test_household_income, influenza_coverage_age) +
  geom_smooth(aes(colour = influenza_coverage_age), method = "lm")


# unextended plot of grouped household income
function_data_stratify(inf_ivd, household_income, as.numeric, influenza_coverage_age) |>

  # dot plot of proportion of COI with each coverage status for each income bracket
  function_plot_proportion_dots(household_income, influenza_coverage_age) +
  geom_smooth(aes(colour = influenza_coverage_age), method = "lm")


```
When we don't stratify and keep the top 10% of earners together, we see that there is a continuous increase in the uptake of both the covid and vaccinatiosn as we move to higher income brackets

