---
title: "04_Exploratory Data Analysis"
format: html
---
## Load Packages
These are the packages that have been used throughout the following document: `here`, `tidyverse`, `lubridate`, `knitr`
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(GGally)
```
*other packages will be loaded as needed*

## Reading data
```{r}
# transformed independent variable data
transformed_ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
transformed_cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
transformed_inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )
```

## Influenza data
### Distribution of coverage by number of doses and the degree of coverage (since october 2022)

**By degree of coverage**
```{r}
  transformed_inf |>
    filter(!is.na(influenza_coverage_age)) |>
    summarise(individuals = n(), .by = influenza_coverage_age) |>
    mutate(proportion = individuals / sum(individuals)) |>
    arrange(influenza_coverage_age) |>
    mutate(
      influenza_coverage_age = case_when(
        influenza_coverage_age == 0 ~ "Not vaxxed",
        influenza_coverage_age == 1 ~ "Partially vaxxed",
        influenza_coverage_age == 2 ~ "Fully vaxxed"
      )
    ) |>
    ggplot(aes(x = influenza_coverage_age, y = proportion)) + geom_col() +
    geom_text(aes(label = individuals), vjust = 1.0) +
    ggtitle(
      paste(
        "Vaccination status of eligible children, N =",
        sum(!is.na(transformed_inf$influenza_coverage_age))
        )
      )
```
**By number of doses**
```{r}
  transformed_inf |>
    filter(!is.na(influenza_coverage_dosage)) |>
    summarise(individuals = n(), .by = influenza_coverage_dosage) |>
    mutate(proportion = individuals / sum(individuals)) |>
    arrange(influenza_coverage_dosage)
```


A majority of the children (68%) who are eligible for the influenza vax have not receieved the vaccine at all (i.e. 0 doses or Not vaxxed). However, within the children who have receieved at least one dose of the vaccine (~32%), a much greater proportion of them are considered fully vaxxed than being partially vaxxed (a ratio of 10:1). 

This is supported by data on the number of doses received, the ratio of individuals who have received 2 doses as compared to 1 dose is roughly 3:1 (25:7.5). The discrepnacy in ratios can be explained by children below the age of 5 being considered fully vaxxed individuals upon receiving 1 or more doses of the influenza vax


## Covid data
### Distribution of coverage by number of doses and the degree of coverage (since october 2022)

**By degree of coverage**
```{r}
  transformed_cov |>
    filter(!is.na(covid_coverage_age)) |>
    summarise(individuals = n(), .by = covid_coverage_age) |>
    mutate(proportion = individuals / sum(individuals)) |>
    arrange(covid_coverage_age) |>
    mutate(
      covid_coverage_age = case_when(
        covid_coverage_age == 0 ~ "Not vaxxed",
        covid_coverage_age == 1 ~ "Partially vaxxed",
        covid_coverage_age == 2 ~ "Fully vaxxed"
      )
    )
```

**By number of doses**
```{r}
  transformed_cov |>
    filter(!is.na(covid_coverage_dosage)) |>
    summarise(individuals = n(), .by = covid_coverage_dosage) |>
    mutate(proportion = individuals / sum(individuals)) |>
    arrange(covid_coverage_dosage) 
```

The data on covid vaccinations tells a similar story to that of influenza vaccinations. Namely, the proportion of eligible children who are not vaxxed at all remains high at 80% of the children body. However, the proportion of individuals who are partially vaccinated -- less than 3 doses for individuals over the age of 5 -- is significantly higher (partial:full = 1:3) than that for those who received the influenza vaccine (partial:full = 1:10). 

Referencing the number of doses of the covid vaccine received by individuals, we note that 13.6% of the eligible children received 3 doses of the covid vaccine, 1.3% lower than the 14.9% of children who are fully vaxxed -- this is explained by children under 5y/o being classified as fully vaccinated as long as they have 1 or more doses of the covid vaccine due to variances in the vaccination schedule of covid vacccines for that age group. Note that majority (85%) of the 5.6% children who are partially vaccinated received 2 doses, 4.8% of all eligible children.

***Why are there more children who are partially vaccinated for covid as opposed to the influenza vaccination?***

## Multivariate analysis
### Independent variables 
Package used: `GGally` for pairs plots?


## Bivariate analysis
### Independent variables 

Questions to be asked





## Number of individuals

### Total number of individuals

-   Does the number of individuals in a household affect:

    -   the child's (covid) vaccination status

    -   the number of doses of the covid vaccine the child receives

    -   the child's (influenza) vaccination status

    -   the number of doses of the influenza vaccine the child receive

### Number of aunts and uncles

-   Does the number of aunts and uncles a child has affect:

    -   the child's (covid) vaccination status

    -   the number of doses of the covid vaccine the child receives

    -   the child's (influenza) vaccination status

    -   the number of doses of the influenza vaccine the child receive

### Number of vulnerable individuals

-   Does the number of vulnerable individuals living in the same household (this includes individuals who are bedriden, need ventilation and need feeding) affect:

### Number of grandparents

-   Does the number of grandparents living in the same household affect:

## Child and siblings

### Total number of siblings

-   Does the number of siblings living with the child in the same household affect:

### Number of brothers and/or siblings

-   Does the number of sisters and or brothers living in the same household as the child affect:

### Number of siblings at the time of vaccination

## Parents

### Number of parents

-   Does the number of parents a child has affect:

    -   the child's (covid) vaccination status

    -   the number of doses of the covid vaccine the child receives

    -   the child's (influenza) vaccination status

    -   the number of doses of the influenza vaccine the child receive

### Parent's marital status

-   Does the marital status of the parents affect:

## Finances

### Annual household income

-   Does the family's annual household income affect:

## Chronic illness

### Respondent's chronic illness

-   Does the presence of chronic illness in the responding parent affect:

## Industry of work

### Respondent parent working in healthcare

-   Does the respondent parent working in the healthcare sector affect:

## Parent's highest educational attianment

### Parent's highest education by qualification

-   Does the highest educational qualification of a child's parents affect:

## Child's parent's vaccination

### Parent's influenza vaccination

-   Does the influenza vaccination status of a child's parents in the past year affect:

### Parent's covid vaccination (dosage)

-   Does the covid vaccination status of a child's parents affect:

### Recency of parent's covid vaccination

-   Does the recency of a child's parent's covid vaccination affect:

### Child's parent's yearly vaccination intention

-   Does the child's parent's intention to get the covid vaccine every year affect:

