---
title: "04_exploring_perception_of_vaccines"
output: html_document
date: "`r Sys.Date()`"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load Packages
These are the packages that have been used throughout the following document: `here`, `tidyverse`, `lubridate`, `knitr`
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(GGally)
```
*other packages will be loaded as needed*

## Reading data
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )
```

## Creating data frames for bivariate and multivariate analysis
```{r}
#| echo: FALSE

# influenza and independent variable data
inf_ivd <- bind_cols(inf, ivd)

# covid and independent variable data
cov_ivd <- bind_cols(cov, ivd)

# all data
cov_inf_ivd <- bind_cols(cov, inf, ivd)
```


this is a scrap document to quickly investigate if the perception of vaccine safety and 
efficacy has any impact on vaccine uptake in children of interest from the families we are studying

## Questions
People were asked the following 8 questions and gave their responses on a scale
of 1 (strongly disagree) to 7 (strongly agree)

1.	We are confident that government agencies will only allow vaccines that are effective and safe for children
2.	It is very dangerous to be infected, so I have my children vaccinated
3.	Immunizations are very important to your child, so prioritize them over other things
4.	Only vaccinate your own children if the benefits clearly outweigh the risks
5.	I think immunization of children is a collective action to prevent the spread of disease
6.	Sanctions should be available for those who do not comply with vaccination recommendations from health authorities
7.	Vaccination causes more serious illnesses and allergies in children than the diseases it would otherwise prevent
8.	If a lot of people want their children to get vaccinated, I'm going to get them vaccinated


## Plots
 1.	We are confident that government agencies will only allow vaccines that are effective and safe for hildren
```{r}
cov_ivd |>
     
     # stratify by vaccine danger and doses received
     filter(household_total > 1 & !is.na(covid_coverage_age)) |>
     group_by(perception_safety, covid_coverage_age) |>
  
     # count the number of children per category
     summarise(cov_count = n()) -> cov_processed

barwidth = 0.10


     ggplot() + 
     geom_col(data = cov_processed,
         aes(x = perception_safety, y = cov_count, fill = covid_coverage_age), 
         position = "fill"
     ) +
     xlab("The government only allows safe and effective vaccines\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by views on safety and efficacy of vaccines") +
     geom_text(
       data = cov_processed, 
       aes(x = perception_safety,
           y = cov_count,
           label = cov_count,
           colour = covid_coverage_age
       ), 
       position = position_fill(vjust = 0.5),
       colour = "white"
     )


inf_ivd |>
    filter(household_total > 1 & !is.na(influenza_coverage_age)) |>
    group_by(perception_safety, influenza_coverage_age) |>
    
    # count the number of children by influenza doses and perceived vaccine safety
    summarise(inf_count = n()) -> inf_processed

ggplot() +
     geom_col(data = inf_processed,
         aes(x = perception_safety + barwidth + 0.01, y = inf_count, fill = influenza_coverage_age),
         position = "fill")
```

 2.	It is very dangerous to be infected, so I have my children vaccinated
```{r}
 
 cov_ivd |>
     
     # stratify by vaccine danger and doses received
     filter(household_total > 1 & !is.na(covid_coverage_dosage)) |>
     group_by(perception_infection_danger, covid_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_infection_danger, y = count, fill = covid_coverage_dosage), 
         position = "fill"
     ) + xlab("Infection is dangerous, so i get my children vaccinated\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by views on dangers of infection")

inf_ivd |>
     # stratify by vaccine danger and doses received
     filter(household_total > 1 & !is.na(influenza_coverage_dosage)) |>
     group_by(perception_infection_danger, influenza_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_infection_danger, y = count, fill = influenza_coverage_dosage), 
         position = "fill"
     ) + xlab("Infection is dangerous, so i get my children vaccinated\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in influenza dosage by views on dangers of infection")

```

 3.	Immunizations are very important to your child, so prioritize them over other things
```{r}
cov_ivd |>
     
     # stratify by vaccine danger and doses received
     filter(household_total > 1 & !is.na(covid_coverage_dosage)) |>
     group_by(perception_immunisation_importance, covid_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_importance, y = count, fill = covid_coverage_dosage), 
         position = "fill"
     ) + xlab("immunisations should be prioritised as they're important\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by views on importance of immunisation")


inf_ivd |>
     # stratify by vaccine danger and doses received
     filter(household_total > 1 & !is.na(influenza_coverage_dosage)) |>
     group_by(perception_immunisation_importance, influenza_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_importance, y = count, fill = influenza_coverage_dosage), 
         position = "fill"
     ) + xlab("Infection is dangerous, so i get my children vaccinated\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in influenza dosage by views on importance of immunisation")
```
 4.	Only vaccinate your own children if the benefits clearly outweigh the risks
```{r}
cov_ivd |>
     
     # stratify by vaccine danger and doses received
     filter(household_total > 1 & !is.na(covid_coverage_dosage)) |>
     group_by(perception_immunisation_benefits, covid_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_benefits, y = count, fill = as.factor(covid_coverage_dosage)), 
         position = "fill"
     ) + xlab("Only immunise if benefits outweigh the risks\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by views on risk & benefit of immunisation")

inf_ivd |>
     # stratify by vaccine danger and doses received
     filter(household_total > 1 & !is.na(influenza_coverage_dosage)) |>
     group_by(perception_immunisation_benefits, influenza_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_benefits, y = count, fill = as.factor(influenza_coverage_dosage)), 
         position = "fill"
     ) + xlab("vaccinate only if benefits outweigh the risks\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in influenza dosage by views on benefits and risks of vaccination")
```


 5.	I think immunization of children is a collective action to prevent the spread of disease
```{r}
cov_ivd |>
     
     # stratify by perception of collective immunisation and doses received
     filter(household_total > 1 & !is.na(covid_coverage_dosage)) |>
     group_by(perception_collective_immunisation, covid_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_collective_immunisation, y = count, fill = as.factor(covid_coverage_dosage)), 
         position = "fill"
     ) + xlab("The immunisation of children is a collective action\
     to prevent the spread of disease\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by views on collective protection")

inf_ivd |>
     # stratify by perception of collective immunisation and doses received
     filter(household_total > 1 & !is.na(influenza_coverage_dosage)) |>
     group_by(perception_collective_immunisation, influenza_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |>
     ggplot() + 
     geom_col(
         aes(x = perception_collective_immunisation, y = count, fill = as.factor(influenza_coverage_dosage)), 
         position = "fill"
     ) + xlab("The immunisation of children is a collective action\
     to prevent the spread of disease\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in influenza dosage by views on benefits and risks of vaccination")
```



 6.	Sanctions should be available for those who do not comply with vaccination recommendations from health authorities
```{r}
cov_ivd |>
     
     # stratify by opinion on sanctions for unvaccinated and doses received
     filter(household_total > 1 & !is.na(covid_coverage_dosage)) |>
     group_by(perception_immunisation_sanctions, covid_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) -> cov_sanctions_dosage

cov_sanctions_dosage |>
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_sanctions, y = count, fill = as.factor(covid_coverage_dosage)), 
         position = "fill"
     ) + xlab("Those who refuse to vaccinate should be sanctioned\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by views on sanctioning unvaxxed")

inf_ivd |>
     
     # stratify by opinion on sanctioning the unvaccinated and doses received
     filter(household_total > 1 & !is.na(influenza_coverage_dosage)) |>
     group_by(perception_immunisation_sanctions, influenza_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) -> inf_sanctions_dosage

inf_sanctions_dosage |>
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_sanctions, y = count, fill = as.factor(influenza_coverage_dosage)),
         position = "fill"
     ) + xlab("Those who refuse to vaccinate should be sanctioned\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in influenza dosage by views on sanctioning unvaxxed")

```

 7.	Vaccination causes more serious illnesses and allergies in children than the diseases it would otherwise prevent
```{r}
cov_ivd |>
     
     # stratify by perception of the adverse effects of vaccines and doses received
     filter(household_total > 1 & !is.na(covid_coverage_dosage)) |>
     group_by(perception_immunisation_adverse, covid_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |> 
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_adverse, y = count, fill = as.factor(covid_coverage_dosage)), 
         position = "fill"
     ) + xlab("vaccination causes more adverse effects than it presents,\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by perception of the adverse effects of vaccines")

inf_ivd |>
     
     # stratify by perception of the adverse effects of vaccines and doses received
     filter(household_total > 1 & !is.na(influenza_coverage_dosage)) |>
     group_by(perception_immunisation_adverse, influenza_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |> 
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_adverse, y = count, fill = as.factor(influenza_coverage_dosage)), 
         position = "fill"
     ) + xlab("vaccination causes more adverse effects than it presents,\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in influenza dosage by perception of the adverse effects of vaccines")
```

8.	If a lot of people want their children to get vaccinated, I'm going to get them vaccinated
```{r}
cov_ivd |>
     
     # stratify by opinion on herd vaccinating and doses received
     filter(household_total > 1 & !is.na(covid_coverage_dosage)) |>
     group_by(perception_immunisation_herd, covid_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |> 
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_herd, y = count, fill = as.factor(covid_coverage_dosage)), 
         position = "fill"
     ) + xlab("vaccination causes more adverse effects than it presents,\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in covid dosage by willingness to vaccinate with the herd")

inf_ivd |>
     
     # stratify by opinion on herd vaccinating and doses received
     filter(household_total > 1 & !is.na(influenza_coverage_dosage)) |>
     group_by(perception_immunisation_herd, influenza_coverage_dosage) |>
     
     # count the number of children in each category
     summarise(count = n()) |> 
     ggplot() + 
     geom_col(
         aes(x = perception_immunisation_herd, y = count, fill = as.factor(influenza_coverage_dosage)), 
         position = "fill"
     ) + xlab("vaccination causes more adverse effects than it presents,\
     strongly disagree to strongly agree") +
     ylab("proportion of households by dosage") +
     labs(title = "variation in influenza dosage by willingness to vaccinate with the herd")
```

# heatmap

# pairs plot
```{r}
cov_perception <- select(cov_ivd, starts_with("perception_") | starts_with("covid_coverage"))

ggpairs(cov_perception)
```
"***"
if the p-value is < 0.001

"**"
if the p-value is < 0.01

"*"
if the p-value is < 0.05

"."
if the p-value is < 0.10

""
otherwise
