---
title: "05_investigating interdependence"
format: 
  html:
    fig-asp: 0.8
execute: 
  eval: true
  echo: false
  warning: false
---

Libraries
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)
library(patchwork)
library(car)

# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

Data
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )

# transformed age data
age <- 
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_age_data.RDS"
    )
  )

# Creating data frames for bivariate and multivariate analysis
# limit indep data to only those households with a COI
prepped_ivd <- ivd |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1)

# influenza and independent variable data
inf_prepped_ivd <- bind_cols(inf, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1 & !is.na(influenza_coverage_age)) 

# covid and independent variable data
cov_prepped_ivd <- bind_cols(cov, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1 & !is.na(covid_coverage_age))

# create dummy variables for both influenza and covid uptake response variables
inf_prepped_ivd |>
  model.matrix(~ influenza_coverage_age + 0, data = _) |>
  as.data.frame() -> inf_ivd_dummy_vars

cov_prepped_ivd |>
  model.matrix(~ covid_coverage_age + 0, data = _) |>
  as.data.frame() -> cov_ivd_dummy_vars


# create sets of data with dummy response variables for multinomial regresion fitting
# influenza
dummy_inf_prepped_ivd <-
  cbind(inf_ivd_dummy_vars, inf_prepped_ivd) |>
  select(-influenza_coverage_age)

# covid
dummy_cov_prepped_ivd <-
  cbind(cov_ivd_dummy_vars, cov_prepped_ivd) |>
  select(-covid_coverage_age)

```
This document will be used to analyse the interdependencies between variables we have processed thusfar,
to help us determine the sort of relationships that exist between them, and aid us in choosing a model to use.

## Section 1 - collinearity between independent (explanatory) variables
### Breakdown of coverage statuses
```{r}
# stratified counts of covid coverages
xtabs(~ covid_coverage_age + covid_coverage_dosage, data = cov_prepped_ivd)

# stratified counts of influenza coverages
xtabs(~ influenza_coverage_age + influenza_coverage_dosage, data = inf_prepped_ivd)
```

### Numerical variables
Check if any of the continuous numerical variables are collinear

```{r}
# extract all numerical variables (including test_household income)
ivd |>
  filter(child_of_interest == 1) |>
  
  # make test_household_income numeric
  mutate(test_household_income = as.numeric(test_household_income)) |>
  
  # transform test_household_income such that each value represents the number of JPY in millions
  mutate(
    test_household_income = case_when(
      test_household_income == 1 ~ 0,
      test_household_income %in% 2:3 ~ 1,
      test_household_income >= 4 ~ test_household_income - 2
    )
  ) |>
  
  select(!where(is.factor) & !where(is.character) & !starts_with("respondent_") & !starts_with("perception")) |>
  filter(!is.na(test_household_income)) |>
  
  # calculate correlation matrix for cases with a COI
  cor() |>
  
  # plot the correlation plot
  ggcorrplot(method = "square", lab = TRUE, lab_size = 3)
```
The variables that display the most collinearity are:
household total
1. child siblings
2. child_borthers
3. child_sisters
4. child_grand

Furthermore, child_siblngs is associated withthe number of brothers and the number of sisters

### Categorical variables
Check if there's **covariance** between categorical variables

**you cAN look at this type of graph for variables you suspect may be highly correlated**
```{r}
# prepare data frame to be passed into recursive function
ivd$age_of_interest <- age$age_of_interest
prepped_ivd <- ivd |>
  filter(child_of_interest != 0)

# read dependencies
causal_relationship_combinations <-
  readRDS(here("Output", "causal_relationship_combinations.RDS")) |>
  rename(variable1 = name, variable2 = to) |>

  # dropping rows with COI's_familial_factors and "vaccine_uptake" for now
  filter(!if_any(everything(), ~ .x %in% c("vaccine uptake", "COI's familial factors")))
  
# plot every pair 
# input the list of factor_pairs, the function, and pass the dataframe ivd to the df argument of our custom fn
list_of_plots <- pmap(causal_relationship_combinations, function_plot_corr_pairs, df = prepped_ivd)
```

save the categorical plots

```{r}
saveRDS(list_of_plots, here("Output", "causal_relationship_plots.RDS"))
```


## Multivariate plots (correlation)

In the following section the variable of interest which corresponds to the variable in the "TO" row of the codebook will be associated with `###` whilst every other sub variable, which corresponds to the variable(s) in the "From" row for each variable of itnerest, will be associated with `####` 

### education
#### marital status 
Invesigating the distribution of educational attainments between mothers who are married and who are single
```{r}
# educational distribution of all mothers
ivd |>
  filter(child_of_interest == 1) |>
  summarise(n(), mean(test_household_income, na.rm = TRUE), .by = mother_highest_education) |>
  arrange(mother_highest_education)


# educational distribution of single mothers
ivd |>
  filter(child_of_interest == 1 & child_parents == 1 & parent_1_sex == 1) |>
  summarise(n(), mean(test_household_income, na.rm = TRUE), .by = mother_highest_education) |>
  arrange(mother_highest_education)
```
It is evident that single mothers are disproportionately from lower educational backgrounds, with a
much greater proportion of them having only graduated HS/MS and JC/TC as compared to the general mother populus

### test_household_income
#### marital_status and sex
Against marital status and, the sex of the parent
```{r}
ivd |>
     filter(child_of_interest == 1) |>
     ggplot() +
     geom_boxplot(aes(x = test_parents_marital_status, y = test_household_income, fill = parent_1_sex))
```

Against marital status and, sex for single parent children
```{r}
ivd |>
   filter(child_of_interest == 1 & child_parents == 1) |>
   summarise(n(), mean(test_household_income, na.rm = TRUE), .by = c(parent_1_sex, test_parents_marital_status)) |>
  arrange(parent_1_sex, test_parents_marital_status)
```
- When it is a single parent family, we observe that unmarried fathers earn more on average than married fathers (with only 1 child) but married mothers earn more than unmarried mothers. This contradicts the idea that on average, unmarried households earn less than married households

#### education and marital status 
Testing how the test_household_income varaies with the mother and father's highest education
```{r}
ivd |>
  filter(child_of_interest == 1) |>
  ggplot() +
  geom_boxplot(aes(x = father_highest_education, y = test_household_income))

ivd |>
  filter(child_of_interest == 1) |>
  ggplot() +
  geom_boxplot(aes(x = mother_highest_education, y = test_household_income))

ivd |>
  filter(child_of_interest == 1) |>
  ggplot() +
  geom_boxplot(aes(x = parents_highest_education, y = test_household_income))
```
Mothers who graduated from technical colleges and postgraduate institutions are associated wtih a higher household income than fathers of the same educational attainments

**But, could this be due to marrying partners of the same or higher educational attainment on the mothers part? Or is this due solely to educatioanl attainment itself**

Testing for different permutations of the father's and mother's highest education
```{r}
ivd |>
    filter(child_of_interest == 1) |>
    summarise(count = n(), mean = mean(test_household_income, na.rm = TRUE), .by = c(mother_highest_education, father_highest_education)) |>
    mutate(proportion = count / sum(count), .by = father_highest_education) |>
    ggplot(aes(x = father_highest_education, y = mean, colour = mother_highest_education)) +
    geom_point(aes(size = proportion))


ivd |>
    filter(child_of_interest == 1) |>
    summarise(count = n(), mean = mean(test_household_income, na.rm = TRUE), .by = c(mother_highest_education, father_highest_education)) |>
    mutate(proportion = count / sum(count), .by = mother_highest_education) |>
    ggplot(aes(x = mother_highest_education, y = mean, colour = father_highest_education)) +
    geom_point(aes(size = proportion)) 
```

Comparing the graphs of parents, we observe that, at each level of educational attainment, a greater proportion of mothers tend to be married to fathers who are of the same or higher educational attainment. (this is particularly prominent at the postgraduate and JC/TC level). 

Furthermore, if we stratify mothers earnings by their educational level for single mothers only:
```{r}
ivd |>
   filter(child_of_interest == 1 & parent_1_sex == 1) |> 
   summarise(n(), mean = mean(test_household_income, na.rm = TRUE), .by = c(test_parents_marital_status, mother_highest_education)) -> mother_marital_status_education_income

mother_marital_status_education_income |>
  arrange(mother_highest_education, test_parents_marital_status)

mother_marital_status_education_income |>
  ggplot() +
  geom_col(aes(x = mother_highest_education, y = mean, fill = test_parents_marital_status), position = "dodge")
```

Mothers who are married have ~ 2x the annual household income of their unmarried counterparts. With soem caveats for those from HS/JC. (this contradicts our assumption that mothers of each educational attainment tend to marry to fathers of a higehr attainment. If this is the case, why aren't married mothers from HS/MS earning > x2 the income of single mothers from HS/MS?) 

HS/MS: In the case of single mothers, all mothers would be working as they're likely the only source of income for their family. Whereas, if they're married, mothers of lower income households are more likely to stay home to take care of their children?

### mother stay home
#### marital status, education 
```{r}
prepped_ivd |>
  summarise(count = n(), .by = c(mother_highest_education, mother_stay_home, test_parents_marital_status)) |>
  mutate(proportion = count/sum(count), .by = c(mother_highest_education, test_parents_marital_status)) |>
  filter(mother_stay_home == 1, !is.na(mother_highest_education)) |>
  ggplot() +
  geom_col(aes(x = mother_highest_education, y = proportion, fill = test_parents_marital_status), position = "dodge") +
  labs(title = "the proportion of mothers who stay home based on thier marital \n status and educational attainment")
```
The proportion of married mothers who stay home decreases as their educational attainments increase for whilst the proportion of unmarried mothers who stay home remains low throughout given they are likely the sole breadwinner of the family in such scenarios


### Household debt
distribution of debt
```{r}
prepped_ivd |>
  filter(!is.na(household_debt) & child_of_interest == 1) |>
  # filter(household_debt > 0) 
  ggplot(aes(x = household_debt)) +
  geom_histogram()
``` 
debt and education
```{r}
prepped_ivd |>
  filter(!is.na(household_debt) & child_of_interest == 1) |>
  filter(household_debt > 0) |>
  summarise(count = n(), .by = c(parents_highest_education, household_debt)) |>
  mutate(proportion = count/sum(count), .by = parents_highest_education) |>
  ggplot(aes(x = household_debt, y = proportion, colour = parents_highest_education)) +
  geom_point() +
  facet_wrap(vars(parents_highest_education))
```
debt and test_household_income
```{r} 
prepped_ivd |>
  filter(!is.na(household_debt) & !is.na(test_household_income) & !is.na(parents_highest_education)) |>
  summarise(avg_debt = sum(household_debt/n()), .by = c(parents_highest_education, test_household_income)) |>
  ggplot(aes(x = test_household_income, y = avg_debt, colour = parents_highest_education)) +
  geom_point() +
  geom_smooth(method = "lm") +
  facet_wrap(vars(parents_highest_education))

# running a regression

  # homoscedasticity??
  prepped_ivd |>
  filter(!is.na(household_debt) & !is.na(test_household_income) & !is.na(parents_highest_education)) |>
  summarise(avg_debt = sum(household_debt/n()), .by = c(parents_highest_education, test_household_income)) |>
  ggplot(aes(x = test_household_income, y = avg_debt, colour = parents_highest_education)) +
  geom_point() 
  
  # collinearity??

  
prepped_ivd |>
  lm(household_debt ~ test_household_income + parents_highest_education + parents_highest_education*test_household_income, data = _)
```

### Household_mortgage
distribution of mortgages
```{r}
prepped_ivd |>
  filter(!is.na(household_mortgage) & child_of_interest == 1) |>
  # filter(household_debt > 0) 
  ggplot(aes(x = household_mortgage)) +
  geom_histogram()
``` 
mortgage and education
```{r}
prepped_ivd |>
  filter(!is.na(household_mortgage) & child_of_interest == 1 & !is.na(parents_highest_education)) |>
  # filter(household_debt > 0) |>
  summarise(count = n(), .by = c(parents_highest_education, household_mortgage)) |>
  mutate(proportion = count/sum(count), .by = parents_highest_education) |>
  ggplot(aes(x = household_mortgage, y = proportion, colour = parents_highest_education)) +
  geom_point() +
  facet_wrap(vars(parents_highest_education))
```

mortgage and debt
```{r}
prepped_ivd |>
  filter(!is.na(household_mortgage) & !is.na(household_debt) & !is.na(parents_highest_education)) |>
  summarise(avg_debt = sum(household_debt) / n(), count = n(), .by = c(household_mortgage, parents_highest_education)) |>
  mutate(proportion = count / sum(count), .by = parents_highest_education) |>
  ggplot(aes(x = household_mortgage, y = avg_debt, colour = parents_highest_education)) +
  geom_point(aes(size = proportion)) +
  facet_wrap(vars(parents_highest_education))
```

Mortgage, debt and income
```{r}
prepped_ivd |>
  filter(!is.na(household_income) & !is.na(household_mortgage) & !is.na(household_debt)) |>
  mutate(avg_debt = household_debt / n(), .by = c(household_income, household_mortgage, parents_highest_education)) |>
  mutate(avg_mortgage = household_mortgage / n(), .by = c(household_income, household_debt)) |>
  ggplot(aes(x = household_income, y = avg_mortgage, colour = parents_highest_education, alpha = avg_debt)) +
  geom_point() +
  facet_wrap(vars(parents_highest_education))
  
```

### Birth order
#### age_of_interest, child_siblings
```{r}
# how birth order varies with child_siblings
prepped_ivd |>
  summarise(mean_BO = mean(birth_order, na.rm = TRUE), .by = child_siblings) |>
  ggplot(aes(x = child_siblings, y = mean_BO)) +
  geom_point()
```
We note that the mean birth order generally increases as the number of siblings and age of interest increases

```{r}
# birth order with age
prepped_ivd |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  summarise(mean_BO = mean(birth_order, na.rm = TRUE), .by = age_of_interest) |>
  ggplot(aes(x = age_of_interest, y = mean_BO)) +
  geom_point()
```

```{r}
prepped_ivd |>
  
  # categorise age by integer values (so you don't have impossibly many ages) and mash sibligns together
  mutate(
    age_of_interest  = ceiling(age_of_interest)
  ) |>
  summarise(count = n(), .by = c(child_siblings, age_of_interest, birth_order)) |>
  ggplot() + 
  geom_density(aes(x = age_of_interest, colour = child_siblings)) +
  facet_wrap(vars(birth_order))
```

## Multivariate (interactions)
### (M) test_household_income
coverage by mothers and fathers education
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age)) |>
  
  # calculate proportions by mother and fathers education for each degree of coverage
  summarise(count = n(), .by = c(father_highest_education, mother_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(father_highest_education, mother_highest_education)) |>
  
  # plot the distribution of vaccine uptakes for each combination of mothers' and fathers' educations
  ggplot(aes(x = father_highest_education, y = proportion, colour = mother_highest_education)) +
  geom_point() + 
  geom_line(aes(group = mother_highest_education)) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "a plot of how each degree of uptake changes with the father's highest education, \n
    for each highest educational level of the mother"
  ) 

function_plot_save(last_plot(), "cov_age_mother_father_highest_education", "png", "Output/05_multivariate_uptake_plots")



# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age)) |>
  
  # calculate proportions by mother and fathers education for each degree of inferage
  summarise(count = n(), .by = c(father_highest_education, mother_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(father_highest_education, mother_highest_education)) |>
  
  # plot the distribution of vaccine uptakes for each combination of mothers' and fathers' educations
  ggplot(aes(x = father_highest_education, y = proportion, colour = mother_highest_education)) +
  geom_point() + 
  geom_line(aes(group = mother_highest_education)) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "a plot of how each degree of uptake changes with the father's highest education, \n
    for each highest educational level of the mother"
  ) 

function_plot_save(last_plot(), "inf_age_mother_father_highest_education", "png", "Output/05_multivariate_uptake_plots")
  
```

#### father/mother_education income
coverage by mothers and fathers education with income
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  
  pivot_longer(cols = c(father_highest_education, mother_highest_education), values_to = "education", names_to = "parents") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(parents, education, income, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(parents, education, income)) |>

  
  # plot
  ggplot(aes(x = income, y = proportion, colour = parents)) +
  geom_point() +
  geom_smooth(aes(group = parents, fill = parents), alpha = 0.2, method = "lm") +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(education)) -> father_mother_highest_education_income_cov_age

father_mother_highest_education_income_cov_age


# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
  
  pivot_longer(cols = c(father_highest_education, mother_highest_education), values_to = "education", names_to = "parents") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(parents, education, income, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(parents, education, income)) |>

  
  # plot
  ggplot(aes(x = income, y = proportion, colour = parents)) +
  geom_point() +
  geom_smooth(aes(group = parents, fill = parents), alpha = 0.2, method = "lm") +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(education)) -> father_mother_highest_education_income_inf_age

father_mother_highest_education_income_inf_age
```
coverage by number of parents and income
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(test_household_income) & !is.na(covid_coverage_age)) |>
           
  # stratify income levels to compress the levels
  mutate(income = ceiling(test_household_income / 5)) |>  
  
  # summarise proportions for each level of income by the number of parents the child has
  summarise(count = n(), .by = c(test_household_income, child_parents, covid_coverage_age)) |>
  mutate(proportions = count / sum(count), .by = c(test_household_income, child_parents)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportions, colour = covid_coverage_age)) +
  geom_point() +
  #geom_smooth(method = "lm") +
  facet_wrap(vars(child_parents)) +
  labs(
    title = "covid coverage with household income, stratified by household with 1 or 2 parents"
  )
  
  # save the plot
  function_plot_save(last_plot(), "income_child_parents_covid_age", "png", "Output/05_multivariate_uptake_plots")

#influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(test_household_income) & !is.na(influenza_coverage_age)) |>
           
  # stratify income levels to compress the levels
  mutate(income = ceiling(test_household_income / 5)) |>  
  
  # summarise proportions for each level of income by the number of parents the child has
  summarise(count = n(), .by = c(test_household_income, child_parents, influenza_coverage_age)) |>
  mutate(proportions = count / sum(count), .by = c(test_household_income, child_parents)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportions, colour = influenza_coverage_age)) +
  geom_point() +
  #geom_smooth(method = "lm") +
  facet_wrap(vars(child_parents)) +
  labs(
    title = "influenza coverage with household income, stratified by household with 1 or 2 parents"
  )
  
  # save the plot
  function_plot_save(last_plot(), "income_child_parents_influenza_age", "png", "Output/05_multivariate_uptake_plots")
            
```

#### father/mother/parents_highest_education  
coverage by father, mother and parents highest education and income
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  pivot_longer(cols = c(father_highest_education, mother_highest_education, parents_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parent))
    
  function_plot_save(plot = last_plot(), "income_father_mother_education_covid_age", "png", "Output/05_multivariate_uptake_plots")

    
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  pivot_longer(cols = c(father_highest_education, parents_highest_education, mother_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(parent))

  function_plot_save(plot = last_plot(), "income_father_mother_education_influenza_age", "png", "Output/05_multivariate_uptake_plots")

```


Stratifying by both the mother and father's highest education levels, we realise that as income is held constant, the difference in uptake of both the covid and influenza vaccines is constnat. __EXCEPT__ for postgraduate mothers who seem to have more of an effect on influenza uptake

looking at each cimbinatiins of parents education


#### father mother education stratified by each other
Now let's look at income for each combination of mother's and fathers
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  #pivot_longer(cols = c(father_highest_education, mother_highest_education, parents_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(mother_highest_education, father_highest_education, income, covid_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(mother_highest_education, father_highest_education, income)
  ) -> mother_highest_father_highest_education_covid_age
  #filter(mother_highest_education == "Junior High or High school", father_highest_education == "Junior High or High school")
 
# plot
mother_highest_father_highest_education_covid_age |>
  
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = covid_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(mother_highest_education), rows = vars(father_highest_education))

# lay out the data
mother_highest_father_highest_education_covid_age |>
  arrange(mother_highest_education, father_highest_education, covid_coverage_age, income)

# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(mother_highest_education, father_highest_education, income, influenza_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(mother_highest_education, father_highest_education, income)
  ) -> mother_highest_father_highest_education_influenza_age
  #filter(mother_highest_education == "Junior High or High school", father_highest_education == "Junior High or High school")
 
# plot
mother_highest_father_highest_education_influenza_age |>
  
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = influenza_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(mother_highest_education), rows = vars(father_highest_education))

# lay out the data
mother_highest_father_highest_education_influenza_age |>
  arrange(mother_highest_education, father_highest_education, influenza_coverage_age, income)
```

#### (R) test_father and test_mother's education stratified by each other
Now let's try stratifying by test_father and test_mother's highest education 
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(test_mother_highest_education) & !is.na(test_father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  #pivot_longer(cols = c(test_father_highest_education, test_mother_highest_education, parents_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(test_mother_highest_education, test_father_highest_education, income, covid_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(test_mother_highest_education, test_father_highest_education, income)
  ) -> test_mother_highest_test_father_highest_education_covid_age
  #filter(test_mother_highest_education == "Junior High or High school", test_father_highest_education == "Junior High or High school")
 
# plot
test_mother_highest_test_father_highest_education_covid_age |>
  
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = covid_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(test_mother_highest_education), rows = vars(test_father_highest_education)) +
  labs(
    title = "uptake of the covid vaccine in the COI according to their mother and father's highest educational attainments",
    subtitle = "columns represent mother's highest_education and rows represent father's highest education"
  )

# lay out the data
test_mother_highest_test_father_highest_education_covid_age |>
  arrange(test_mother_highest_education, test_father_highest_education, covid_coverage_age, income)

# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(test_mother_highest_education) & !is.na(test_father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(test_mother_highest_education, test_father_highest_education, income, influenza_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(test_mother_highest_education, test_father_highest_education, income)
  ) -> test_mother_highest_test_father_highest_education_influenza_age
  #filter(test_mother_highest_education == "Junior High or High school", test_father_highest_education == "Junior High or High school")
 
# plot
test_mother_highest_test_father_highest_education_influenza_age |>
  
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = influenza_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(test_mother_highest_education), rows = vars(test_father_highest_education)) +
  labs(
    title = "uptake of the influenza vaccine in the COI according to their mother and father's highest educational attainments",
    subtitle = "columns represent mother's highest_education and rows represent father's highest education"
  )

# lay out the data
test_mother_highest_test_father_highest_education_influenza_age |>
  arrange(test_mother_highest_education, test_father_highest_education, influenza_coverage_age, income)
```
#### (R) test_father_highest_education and mother_highest_education
Let's look at the highest possible
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(test_father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  #pivot_longer(cols = c(test_father_highest_education, mother_highest_education, parents_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(mother_highest_education, test_father_highest_education, income, covid_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(mother_highest_education, test_father_highest_education, income)
  ) -> highest_mother_test_father_highest_education_covid_age
  
# plot
highest_mother_test_father_highest_education_covid_age |>
  
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = covid_coverage_age), method = "lm") +
  ylim(0, 1) +
  facet_grid(cols = vars(mother_highest_education), rows = vars(test_father_highest_education)) +
  labs(
    title = "uptake of the covid vaccine in the COI according to their mother and (test) father's highest educational attainments",
    subtitle = "columns represent mother_highest_education and rows represent test_father_highest education"
  )

# lay out the data
highest_mother_test_father_highest_education_covid_age |>
  arrange(mother_highest_education, test_father_highest_education, covid_coverage_age, income)

# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(test_father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(mother_highest_education, test_father_highest_education, income, influenza_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(mother_highest_education, test_father_highest_education, income)
  ) -> highest_mother_test_father_highest_education_influenza_age
  #filter(mother_highest_education == "Junior High or High school", test_father_highest_education == "Junior High or High school")
 
# plot
highest_mother_test_father_highest_education_influenza_age |>
  
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = influenza_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(mother_highest_education), rows = vars(test_father_highest_education)) +
  labs(
    title = "uptake of the influenza vaccine in the COI according to their mother and father's highest educational attainments",
    subtitle = "columns represent mother_highest_education and rows represent test_father_highest education"
  )

# lay out the data
highest_mother_test_father_highest_education_influenza_age |>
  arrange(mother_highest_education, test_father_highest_education, influenza_coverage_age, income)
```

#### (R) father_highest_education and test_mother_highest_education
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(test_mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(test_mother_highest_education, father_highest_education, income, covid_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(test_mother_highest_education, father_highest_education, income)
  ) -> test_mother_highest_father_highest_education_covid_age

# plot
test_mother_highest_father_highest_education_covid_age |>
  
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = covid_coverage_age), method = "lm") +
  ylim(0, 1) +
  facet_grid(cols = vars(test_mother_highest_education), rows = vars(father_highest_education)) +
  labs(
    title = "uptake of the covid vaccine in the COI according to their mother and father's highest educational attainments",
    subtitle = "columns represent test_mother_highest_education and rows represent father_highest_education"
  )

# lay out the data
test_mother_highest_father_highest_education_covid_age |>
  arrange(test_mother_highest_education, father_highest_education, covid_coverage_age, income)

# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(test_mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(test_mother_highest_education, father_highest_education, income, influenza_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(test_mother_highest_education, father_highest_education, income)
  ) -> test_mother_highest_father_highest_education_influenza_age
  #filter(test_mother_highest_education == "Junior High or High school", father_highest_education == "Junior High or High school")
 
# plot
test_mother_highest_father_highest_education_influenza_age |>
  
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = influenza_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(test_mother_highest_education), rows = vars(father_highest_education)) +
  labs(
    title = "uptake of the influenza vaccine in the COI according to their mother and father's highest educational attainments",
    subtitle = "columns represent test_mother_highest_education and rows represent test_father_highest education"
  )

# lay out the data
test_mother_highest_father_highest_education_influenza_age |>
  arrange(test_mother_highest_education, father_highest_education, influenza_coverage_age, income)
```



```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(test_mother_highest_education) & !is.na(test_father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  

  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(test_mother_highest_education, test_father_highest_education, income, covid_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(test_mother_highest_education, test_father_highest_education, income)
  ) -> test_mother_highest_father_highest_education_covid_age
  #filter(test_mother_highest_education == "Junior High or High school", test_father_highest_education == "Junior High or High school")
 
# plot
test_mother_highest_father_highest_education_covid_age |>
  
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = covid_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(test_mother_highest_education), rows = vars(test_father_highest_education)) +
  labs(
    title = "uptake of the covid vaccine in the COI according to their mother and father's highest educational attainments",
    subtitle = "columns represent mother's highest_education and rows represent father's highest education"
  )

# lay out the data
test_mother_highest_father_highest_education_covid_age |>
  arrange(test_mother_highest_education, test_father_highest_education, covid_coverage_age, income)

# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(test_mother_highest_education) & !is.na(test_father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(test_mother_highest_education, test_father_highest_education, income, influenza_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(test_mother_highest_education, test_father_highest_education, income)
  ) -> test_mother_highest_father_highest_education_influenza_age
  #filter(test_mother_highest_education == "Junior High or High school", test_father_highest_education == "Junior High or High school")
 
# plot
test_mother_highest_father_highest_education_influenza_age |>
  
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = influenza_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(test_mother_highest_education), rows = vars(test_father_highest_education)) +
  labs(
    title = "uptake of the influenza vaccine in the COI according to their mother and father's highest educational attainments",
    subtitle = "columns represent mother's highest_education and rows represent father's highest education"
  )

# lay out the data
test_mother_highest_father_highest_education_influenza_age |>
  arrange(test_mother_highest_education, test_father_highest_education, influenza_coverage_age, income)
```

Now let's try seperating married fathers & mothers and single parents
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(test_household_income)) |>

# trying all unmarried parents
mutate(
  single_parent_highest_education = case_when(
    test_parents_marital_status == 1 & parent_1_sex == 1 ~ mother_highest_education,
    test_parents_marital_status == 1 & parent_1_sex == 0 ~father_highest_education,
    .default =  NA
  )
) |>

  # pivot to include values for both mother's and father's education
  pivot_longer(
    cols = c(father_highest_education, mother_highest_education, single_parent_highest_education),
    values_to = "education",
    names_to = "parent"
  ) |>
  
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # remove NA values for education
  filter(!is.na(education)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  ylim(0,1) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parent))
```

Now let's try married parents vs single mothers only
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  
  # seperate out single mothers from mother's highest education 
  mutate(
    single_mother_highest_education = case_when(
      
    # for any response that indicates unmarried and where the responding parent is female
    test_parents_marital_status == 1 & parent_1_sex == 1 ~ mother_highest_education,
    .default = NA
    )
 ) |>

  # pivot to include values for both mother's and father's education
  pivot_longer(
    cols = c(father_highest_education, mother_highest_education, single_mother_highest_education),
    values_to = "education",
    names_to = "parent"
  ) |>
  
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # remove NA values for education
  filter(!is.na(education)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  ylim(0,1) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parent))

  # save the plot
  function_plot_save(plot = last_plot(), "income_marital_father_mother_education_covid_age", "png", "Output/05_multivariate_uptake_plots")


# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
  
  # seperate out single mothers from mother's highest education 
  mutate(
    single_mother_highest_education = case_when(
      
    # for any response that indicates unmarried and where the responding parent is female
    test_parents_marital_status == 1 & parent_1_sex == 1 ~ mother_highest_education,
    .default = NA
    )
 ) |>

  # pivot to include values for both mother's and father's education
  pivot_longer(
    cols = c(father_highest_education, mother_highest_education, single_mother_highest_education),
    values_to = "education",
    names_to = "parent"
  ) |>
  
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # remove NA values for education
  filter(!is.na(education)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  ylim(0,1) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(parent)) 

  # save the plot
  function_plot_save(plot = last_plot(), "income_marital_father_mother_education_influenza_age", "png", "Output/05_multivariate_uptake_plots")
```
I'm pretty sure there's some sort of interaction between education and household income in affecting the uptake of influenza because the slopes change

#### mother's employment
We will test to see if a mother's employment status i.e. if the household is a one or 2 income household, affects the rate of vaccination for families of the same income. We are not testing the same for father's employment due to the low no. of responses of mother income only families

Here mother's employment is **fully stratified**
```{r}
# Covid vax
income_mother_employment_cov_age <- cov_prepped_ivd |> 
  # filter out NA response
  filter(!if_any(c(mother_employment_status, covid_coverage_age), is.na)) |>

  summarise(count = n(), .by = c(mother_employment_status, test_household_income, covid_coverage_age)) |>

  # make mother's employment binary, working or not working (but really i think that it should be on a scale beacuse the amount of time ???)

  # make each data point depending on coverage, income, etc.
  mutate(proportion = count/sum(count), .by = c(mother_employment_status, test_household_income))

income_mother_employment_cov_age |>
  ggplot(aes(x = test_household_income, y = proportion, colour = mother_employment_status)) + 
  geom_smooth(aes(linetype = covid_coverage_age), method = "lm") +
  geom_point(aes(shape = covid_coverage_age)) +
  #geom_line(aes(linetype = covid_coverage_age)) + 
  labs(title = "The vaccination uptake with increasing income, depending on if the mother works")

income_mother_employment_cov_age

```

```{r}
# influenza vax
income_mother_employment_cov_age <- cov_prepped_ivd |> 
  # filter out NA response
  filter(!if_any(c(mother_employment_status, covid_coverage_age), is.na)) |>

  summarise(count = n(), .by = c(mother_employment_status, test_household_income, covid_coverage_age)) |>

  # make mother's employment binary, working or not working (but really i think that it should be on a scale beacuse the amount of time ???)

  # make each data point depending on coverage, income, etc.
  mutate(proportion = count/sum(count), .by = c(mother_employment_status, test_household_income))

income_mother_employment_cov_age |>
  ggplot(aes(x = test_household_income, y = proportion, colour = mother_employment_status)) + 
  geom_smooth(aes(linetype = covid_coverage_age), method = "lm")
  #geom_line(aes(linetype = covid_coverage_age)) + 
  labs(title = "The vaccination uptake with increasing income, depending on if the mother works")

income_mother_employment_cov_age
```

#### Mother's weekly working hours
Seeing how the income varies with the parent's working hours. Logically, for 2 children whose amilies have the same finanical ability to vaccinate them, the child whose parents work less hours a week would be more likely to be fully vaccinated as their parents have the time to bring them to be vaccinated

Covid
```{r}
cov_prepped_ivd |>
  filter(!is.na(mother_work_weekly)) |>
  # let's try seperating ages into 5 hour bins, with 60+ hours per weeek being 1 bin
  mutate(
    mother_work_weekly_bin = factor(
      case_when(
      mother_work_weekly < 60 ~ mother_work_weekly %/% 5 * 5, 
      mother_work_weekly >= 60 ~ 60
      )
    )
   ) |>

  summarise(count = n(), .by = c(covid_coverage_age, mother_work_weekly_bin, test_household_income)) |>
  
  # calculate proportion of each income group and mother_work_hours/week which the child's coverage is at
  mutate(proportion = count/sum(count), .by = c(covid_coverage_age, mother_work_weekly_bin)) |>

  # make a heatmap, for each coverage status
  # we are now just testing for full coverage
  filter(covid_coverage_age == 2) |>

  # Complete the table, fill in empty data
  complete(test_household_income, mother_work_weekly_bin, fill = list(proportion = 0)) |>

  ggplot(aes(x = test_household_income, y = mother_work_weekly_bin)) + 
   geom_tile(aes(fill = proportion)) +
    scale_fill_gradient(low = "white", high = "red") 
```

If we look solely at the 5-10 million yen/year household income range, there is some semblance of less workjing hours equating to a higher uptake of vaccines but i'm not too sure??

Now we look at influenza data instead

```{r}
inf_prepped_ivd |>
  filter(!is.na(mother_work_weekly)) |>
  # let's try seperating ages into 5 hour bins, with 60+ hours per weeek being 1 bin
  mutate(
    mother_work_weekly_bin = factor(
      case_when(
      mother_work_weekly < 60 ~ mother_work_weekly %/% 5 * 5, 
      mother_work_weekly >= 60 ~ 60
      )
    )
   ) |>

  summarise(count = n(), .by = c(influenza_coverage_age, mother_work_weekly_bin, test_household_income)) |>
  
  # calculate proportion of each income group and mother_work_hours/week which the child's coverage is at
  mutate(proportion = count/sum(count), .by = c(influenza_coverage_age, mother_work_weekly_bin)) |>

  # make a heatmap, for each coverage status
  # we are now just testing for full coverage
  filter(influenza_coverage_age == 2) |>

  ggplot(aes(x = test_household_income, y = mother_work_weekly_bin)) + 
    geom_tile(aes(fill = proportion)) +
    scale_fill_gradient(low = "white", high = "red") 
```

##### Running regressions to see if working hours is truly significant
So the heatmap plots don't really reveal anything about if there is a sort of interaction between the mother's working hours and household income. 

Hypothesis: that as the number of working hours increases, we would see a decrease in proportion of vaccination even given the same vax status

We'll investigate how the proportion of children with full covid coverage varies vs no full coverage (binary variable)

```{r}
data <- cov_prepped_ivd |>

  # filter out households without a vaccine status
  filter(!is.na(covid_coverage_age) & !is.na(test_household_income)) |>

  # recode coverage as binary
  mutate(
    cov_vaxxed_full = factor(case_when(
      covid_coverage_age != 2 ~ 0,
      covid_coverage_age == 2 ~ 1
      
    )
  )) |>  

  select(cov_vaxxed_full, test_household_income, mother_work_weekly)

  # run one with income_only
  income_only <- glm(cov_vaxxed_full ~ test_household_income, data = data, family = binomial(link = "logit"))

  # run regression with coverage as binary variable, income and mother's hours as predictor, 
  # and no interaction term
  no_interaction <- glm(cov_vaxxed_full ~ test_household_income + mother_work_weekly, data = data, family = binomial(link = "logit"))

  # run logistic regression with interaction term
  interaction <- glm(cov_vaxxed_full ~ test_household_income + mother_work_weekly + mother_work_weekly*test_household_income, data = data, family = binomial(link = "logit"))

  summary(income_only)
  summary(no_interaction)
  summary(interaction)
```

- additionally, the number of hours that a mother works a week (at the 5% significance level) isn't a significant predictor of uptake

- this is directly against https://www.sciencedirect.com/science/article/abs/pii/S0091743514001844?via%3Dihub

- but we will include working hours as previous literature states that it might be important


Now let me do the same for influenza, which I hazard might have a greater possibility of verifying our hyptohesis given that it's not mandatory like covid. Thus, parental free-time is a big factor, which is inversely correlated with parental working hours, in deciding if the child will be brought to be vaccinated
```{r}
data <- inf_prepped_ivd |>

  # filter out households without a vaccine status
  filter(!is.na(influenza_coverage_age) & !is.na(test_household_income)) |>

  # recode coverage as binary
  mutate(
    inf_vaxxed_full = factor(case_when(
      influenza_coverage_age == 2 ~ 1,
      influenza_coverage_age != 2 ~ 0
    )
  )) |>  

  select(inf_vaxxed_full, test_household_income, mother_work_weekly)

  # only household_income
  income_only <- glm(inf_vaxxed_full ~ test_household_income, data = data, family = "binomial")

  # run regression with coverage as binary variable, income and mother's hours as predictor, 
  # and no interaction term
  no_interaction <- glm(inf_vaxxed_full ~ test_household_income + mother_work_weekly, data = data, family = "binomial")

  # run logistic regression with interaction term
  interaction <- glm(inf_vaxxed_full ~ test_household_income + mother_work_weekly + mother_work_weekly*test_household_income, data = data, family = "binomial")

  summary(income_only)
  summary(no_interaction)
  summary(interaction)
```


- forall 3 models it seems that mothers work hours are slightly negatively correlated with full coverage. 

- Income is still a positive predictor of full uptake which corroborates what we've found in our EDA

As income and mother's work hours increase, it seeems that there is a negligible effect on uptake. (P value is 0.311 )
- the interaction doesn't seems significant

#### Father's weekly working hours




#### mother_stay_home (we need mother employment status)
Now, let's examine how uptake differs between families where mothers stay home and don't, holding income level constant
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  # pivot_longer(cols = c(father_highest_education, mother_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, test_household_income, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by families with a stay-home mom"#,
    #caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home))
    
  function_plot_save(plot = last_plot(), "test_household_income_mother_stay_home_covid_age", "png", "Output/05_multivariate_uptake_plots")

  
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, test_household_income, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by families with a stay-home mom"#,
   # caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home))
    
  function_plot_save(plot = last_plot(), "test_household_income_mother_stay_home_influenza_age", "png", "Output/05_multivariate_uptake_plots")

```
Now let's investigate the uptake and how it varies with test_household_income, marital_status and mother's employment
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
    
  # pivot to include values for mom's employment
  # pivot_longer(cols = c(father_highest_education, mother_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, mother_employment_status, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, mother_employment_status, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by mother employment status against stay-home"#,
    #caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(mother_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_employment_covid_age", "png", "Output/05_multivariate_uptake_plots")

  
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, mother_employment_status, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, mother_stay_home, mother_employment_status)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by mother employment status against stay-home"#,
   # caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(mother_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_employment_influenza_age", "png", "Output/05_multivariate_uptake_plots")

```

#### mother_stay_home, father_employment
Let's investigate how vaccine uptake varies with test_household_income, mother_stay_home and father's employment ab
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, father_employment_status, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, father_employment_status, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by mother stay-home against father_stay_home",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(father_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_father_employment_covid_age", "png", "Output/05_multivariate_uptake_plots")

  
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, father_employment_status, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, mother_stay_home, father_employment_status)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by mother stay-home against father_employment",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(father_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_father_employment_influenza_age", "png", "Output/05_multivariate_uptake_plots")

```

### (M) age_of_interest

#### birth_order
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    birth_order = ifelse(
      birth_order <= 3,
      as.character(birth_order),
      "4+"
    ),
    
    # round age
    age_of_interest = ceiling(age_of_interest)
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, birth_order, covid_coverage_age) |>
  arrange(birth_order, age_of_interest, covid_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = case_when(
      age_of_interest %in% 1:5 ~ "pre",
      age_of_interest %in% 6:12 ~ "pri",
      age_of_interest > 12 ~ "high"
    )
  ) |>
  #arrange(birth_order, age_of_interest, covid_coverage_age)
  
  #filter(age_cat == "pre", covid_coverage_age == 2) |>
  #mutate(weight = count / sum(count), .by = c(birth_order))
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, birth_order, covid_coverage_age)
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(birth_order)) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \ncoverage by the covid vaccine, stratified by different age groups",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and birth order",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_birth_order_covid_age

age_birth_order_covid_age

# save plots
function_plot_save(plot = last_plot(), "age_birth_order_covid_age", "png", "Output/05_multivariate_uptake_plots")

  

# influenza coverage
inf_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    birth_order = ifelse(
      birth_order <= 3,
      as.character(birth_order),
      "4+"
    ),
    
    # round age
    age_of_interest = ceiling(age_of_interest)
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, birth_order, influenza_coverage_age) |>
  arrange(birth_order, age_of_interest, influenza_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = case_when(
      age_of_interest %in% 1:5 ~ "pre",
      age_of_interest %in% 6:12 ~ "pri",
      age_of_interest > 12 ~ "high"
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, birth_order, influenza_coverage_age)
  ) -> data_age_birth_order_influenza_age

data_age_birth_order_influenza_age |>
  # plot graphs of influenza coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(birth_order)) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \ncoverage by the influenza vaccine, stratified by different age groups",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and birth order",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_birth_order_influenza_age

age_birth_order_influenza_age

# save plots
function_plot_save(age_birth_order_influenza_age, "age_birth_order_influenza_age", "png", "Output/05_multivariate_uptake_plots")


```

#### child_siblings
The following examines child_siblings only
```{r}
# covid uptake
cov_prepped_ivd |>
  
  mutate(
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2,
    
    # compress individuals with >= 3 siblings
    child_siblings = ifelse(child_siblings >= 2, "2+", child_siblings)
  ) |>
  
  
  # stratify proportions of vaccine uptake by age and the number of siblings
  function_data_triple_stratify(age_of_interest, as.numeric, child_siblings, covid_coverage_age) |>
  
  # plot 
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point() +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the covid vaccine changes with age, stratified by the number of siblings they have",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))

# influenza uptake
inf_prepped_ivd |>
  
  mutate(
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2,
    
    # compress individuals with >= 3 siblings
    child_siblings = ifelse(child_siblings >= 2, "2+", child_siblings)
  ) |>
  
  
  
  # stratify proportions of vaccine uptake by age and the number of siblings
  function_data_triple_stratify(age_of_interest, as.numeric, child_siblings, influenza_coverage_age) |>
  
  # plot 
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_smooth(method = "lm", se = FALSE) +
  geom_point() +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the influenza vaccine changes with age, stratified by the number of siblings they have",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))
```



The following examines child_siblings and age_cat
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    child_siblings = ifelse(
      child_siblings <= 1,
      as.character(child_siblings),
      "2+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, child_siblings, covid_coverage_age) |>
  arrange(child_siblings, age_of_interest, covid_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) -> cov_prepped_ivd_transformed_age_siblings_age_cat
  
cov_prepped_ivd_transformed_age_siblings_age_cat |>

  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, child_siblings, covid_coverage_age)
  ) -> data_age_child_siblings_covid_age_cat2

data_age_child_siblings_covid_age_cat2 |>
  
  # plot graphs of covid coverage by age across differing number of siblings
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the covid vaccine changes with age, stratified by the number of siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_child_siblings_covid_age_cat2

age_child_siblings_covid_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_child_siblings_covid_age_cat2", "png", "Output/05_multivariate_uptake_plots")

# running an ancova to determine if they're any differences between uptakes for different ages across age groups and the number of siblings
cov_prepped_ivd_transformed_age_siblings_age_cat |>

  # filter the data to only include cases of full vaccination
  filter(covid_coverage_age == 2) -> cov_prepped_ivd_transformed_age_siblings_age_cat_full_uptake

  # testing for independence of covariates
  aov(age_of_interest ~ age_cat + child_siblings, data = cov_prepped_ivd_transformed_age_siblings_age_cat_full_uptake) |>
  summary()

  # testing for homogeneity in variance
  leveneTest(age_of_interest ~ age_cat * child_siblings, data = cov_prepped_ivd_transformed_age_siblings_age_cat_full_uptake)
  # age_cat and age of interest aren't independent which makes sense but child_sibligns is independent of age_of_interest
  
# fitting the ancova
data_age_child_siblings_covid_age_cat2 |>
  
  # filter the data to only contain cases with full uptake
  filter(covid_coverage_age == 2) |>
  

  (\(.x) {
    
  # to store ancovas
  ancovas_age_cat <- list()
      
  # plot the ancova for each age 
  for(i in c("pre", "primary", "highsch")) {
    filter(.x, age_cat == i) |>
        
      aov(
        proportion ~ age_of_interest + child_siblings + child_siblings * age_of_interest,
        data = _
      ) |>
      
      Anova(type = "III") -> ancova_result
      
      ancovas_age_cat[[i]] <- ancova_result
  }
    
  return(ancovas_age_cat)
  }) ()

  
  
# influenza coverage
inf_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    child_siblings = ifelse(
      child_siblings <= 1,
      as.character(child_siblings),
      "2+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, child_siblings, influenza_coverage_age) |>
  arrange(child_siblings, age_of_interest, influenza_coverage_age) |>
  
   mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, child_siblings, influenza_coverage_age)
  ) |>

  # plot graphs of influenza coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the influenza vaccine, changes with age, stratified by the number of siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_child_siblings_influenza_age_cat2

age_child_siblings_influenza_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_child_siblings_influenza_age_cat2", "png", "Output/05_multivariate_uptake_plots")
```

#### test_child_siblings
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    test_child_siblings = ifelse(
      test_child_siblings <= 1,
      as.character(test_child_siblings),
      "2+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, test_child_siblings, covid_coverage_age) |>
  arrange(test_child_siblings, age_of_interest, covid_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, test_child_siblings, covid_coverage_age)
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(test_child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the covid vaccine changes with age, stratified by the number of test_siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and test_siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_test_child_siblings_covid_age_cat2

age_test_child_siblings_covid_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_test_child_siblings_covid_age_cat2", "png", "Output/05_multivariate_uptake_plots")

  

# influenza coverage
inf_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    test_child_siblings = ifelse(
      test_child_siblings <= 1,
      as.character(test_child_siblings),
      "2+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, test_child_siblings, influenza_coverage_age) |>
  arrange(test_child_siblings, age_of_interest, influenza_coverage_age) |>
  
   mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, test_child_siblings, influenza_coverage_age)
  ) |>

  # plot graphs of influenza coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(test_child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the influenza vaccine, changes with age, stratified by the number of test_siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and test_siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_test_child_siblings_influenza_age_cat2

age_test_child_siblings_influenza_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_test_child_siblings_influenza_age_cat2", "png", "Output/05_multivariate_uptake_plots")
```
Let's stratify by child sibling and test_child_siblings
```{r}
# covid_uptake
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      test_child_siblings <= 2,
     as.character(test_child_siblings),
      "3+"
    ),
    
    child_siblings = ifelse(
     child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, test_child_siblings, child_siblings, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, test_child_siblings, child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(fill = covid_coverage_age), method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(child_siblings), rows = vars(test_child_siblings)) +
  labs(
    title = "Plot of how the uptake of different coverages of the covid vaccine changes with age",
    subtitle = "stratified by child_siblings with columns and test_child_siblings by rows" 
  ) 

# influenza uptake
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      test_child_siblings <= 2,
     as.character(test_child_siblings),
      "3+"
    ),
    
    child_siblings = ifelse(
     child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, test_child_siblings, child_siblings, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, test_child_siblings, child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(fill = influenza_coverage_age), method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(child_siblings), rows = vars(test_child_siblings)) +
  labs(
    title = "Plot of how the uptake of different coverages of the influenza vaccine changes with age",
    subtitle = "stratified by child_siblings with columns and test_child_siblings by rows" 
  ) 
```



#### age_cat

Testng age categories and how they interact with ages
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  filter(!is.na(covid_coverage_age)) |>
    
  # segment age into increments of 0.5 years
  mutate(
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>
  
  summarise(count = n(), .by = c(age_of_interest, covid_coverage_age, age_cat)) |>
  mutate(proportion = count / sum (count), .by = c(age_of_interest, age_cat)) |>
  arrange(age_of_interest, covid_coverage_age) |>
  
  mutate(
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, covid_coverage_age)
    
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \n coverage by the covid vaccine, stratified by different age groups",
    subtitle = "trend lines weighted by the sample size",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))

# influenza
inf_prepped_ivd |>
  
  filter(!is.na(influenza_coverage_age)) |>
  
  mutate(
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>
  
  summarise(count = n(), .by = c(age_of_interest, influenza_coverage_age, age_cat)) |>
  mutate(proportion = count / sum (count), .by = c(age_of_interest, age_cat)) |>
  arrange(age_of_interest, influenza_coverage_age) |>
  
  mutate(
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, influenza_coverage_age)
    
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \n coverage by the influenza vaccine, stratified by different age groups",
    subtitle = "lines weighted by the sample size within each age category, coverage status and birth order",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))
```



Looking at uptake by age of interest stratified by birth order and child_siblings
where child siblings refers only to children < 18
```{r}
# covid_uptake
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      birth_order <= 2,
     as.character(birth_order),
      "3+"
    ),
    
    child_siblings = ifelse(
     child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, birth_order, child_siblings, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, birth_order, child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(child_siblings), rows = vars(birth_order)) +
  labs(
    title = "Plot of how the uptake of different coverages of the covid vaccine changes with age",
    subtitle = "stratified by child_siblings with columns and birth_order by rows" 
  ) 
```

Looking at uptkae by age of interest stratified by birth order and test_child_siblings
```{r}
# covid_uptake
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      birth_order <= 2,
     as.character(birth_order),
      "3+"
    ),
    
    test_child_siblings = ifelse(
     test_child_siblings <= 2,
      as.character(test_child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, birth_order, test_child_siblings, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, birth_order, test_child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(test_child_siblings), rows = vars(birth_order)) +
  labs(
    title = "Plot of how the uptake of different coverages of the covid vaccine changes with age",
    subtitle = "stratified by test_child_siblings with columns and birth_order by rows" 
  ) 
```


### (M) test_parents_marital_status
#### child_parents
Testing how test_parents_marital_status interacts with a child's parents

general breakdown:
```{r}
cov_prepped_ivd |>
  summarise(n(), .by = c(test_parents_marital_status, child_parents))
```

stratified plots
```{r}
# covid plot
cov_prepped_ivd |>
  
  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(covid_coverage_age)) |>
  summarise(count = n(), .by = c(test_parents_marital_status, child_parents, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_parents_marital_status, child_parents)) |>
  
  # plot
  ggplot(aes(x = child_parents, y = proportion)) +
  geom_point(aes(colour = test_parents_marital_status)) +
  geom_smooth(method = "lm", aes(colour = test_parents_marital_status)) +
  function_plot_label_count(child_parents, test_parents_marital_status) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine \n 
    according to their parents marital status and the number of parents they have"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> child_parents_marital_status_covid_age

  child_parents_marital_status_covid_age

  # save the plot for reference
  function_plot_save(last_plot(), "child_parents_marital_status_covid_age", ".png", "Output/05_multivariate_uptake_plots")

# influenza plot
inf_prepped_ivd |>
  
  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(influenza_coverage_age)) |>
  summarise(count = n(), .by = c(test_parents_marital_status, child_parents, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_parents_marital_status, child_parents)) |>
  
  # plot
  ggplot(aes(x = child_parents, y = proportion)) +
  geom_point(aes(colour = test_parents_marital_status)) +
  geom_smooth(method = "lm", aes(colour = test_parents_marital_status)) +
  function_plot_label_count(child_parents, test_parents_marital_status) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine \n 
    according to their parents marital status and the number of parents they have"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> child_parents_marital_status_influenza_age

  child_parents_marital_status_influenza_age

  # save the plot for reference
  function_plot_save(last_plot(), "child_parents_marital_status_influenza_age", ".png", "Output/05_multivariate_uptake_plots")
```

### (M) Vulnerable individuals
#### child_grand
examining how the number of vulnerable individuals and the number of grandparents in the COI's household
affects their uptake of the influenza and covid vaccines
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # reduce dimensions of vulnerable individuals and child_grand to ensure adequate sample size
  mutate(
    across(
      c(vulnerable_individuals, child_grand),
      ~ifelse(.x > 0, 1, 0) |> as.factor()
    )
  ) |>
  
  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(covid_coverage_age)) |>
  summarise(count = n(), .by = c(vulnerable_individuals, child_grand, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(vulnerable_individuals, child_grand)) |>
  
  # plot
  ggplot(aes(x = child_grand, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(method = "lm", aes(colour = vulnerable_individuals)) +
  function_plot_label_count(child_grand, vulnerable_individuals) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine \n 
    according to the presence of vulnerable individuals and grandparents at home"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> vulnerable_indivs_child_grand_covid_age

  vulnerable_indivs_child_grand_covid_age

  # save the plot for reference
  function_plot_save(last_plot(), "vulnerable_indivs_child_grand_covid_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # reduce dimensions of vulnerable individual data and grandparent data to ensure sufficient sample size for analysis
  mutate(
    across(
      c(vulnerable_individuals, child_grand), 
      ~ ifelse(.x > 0, 1, 0) |> as.factor()
    )
  ) |> 

  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(influenza_coverage_age)) |>
  summarise(count = n(), .by = c(vulnerable_individuals, child_grand, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(vulnerable_individuals, child_grand)) |>
  
  # plot
  ggplot(aes(x = child_grand, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(method = "lm", aes(colour = vulnerable_individuals)) +
  function_plot_label_count(child_grand, vulnerable_individuals) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine \n 
    according to the presence of vulnerable individuals and grandparents at home"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> vulnerable_indivs_child_grand_influenza_age

  vulnerable_indivs_child_grand_influenza_age

  # save the plot for reference
  function_plot_save(last_plot(), "vulnerable_indivs_child_grand_influenza_age", ".png", "Output/05_multivariate_uptake_plots")
```

We can run a 2 factor ANOVA, to determine if there is any sort of interaction between these 2? Controlling for other confounding factors

#### household_income
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # reduce dimensions of vulnerable individuals and hosuehold_income to ensure adequate sample size for analysis
  mutate(
    vulnerable_individuals = ifelse(vulnerable_individuals > 0, 1, 0) |> as.factor(),
    income = ceiling(test_household_income/4)
  ) |>
  
  # ensure no missing covid vax data and stratify by vulnerable individuals and income
  filter(!is.na(covid_coverage_age)) |>
  summarise(count = n(), .by = c(vulnerable_individuals, income, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(vulnerable_individuals, income)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(method = "lm", aes(colour = vulnerable_individuals)) +
  function_plot_label_count(income, vulnerable_individuals) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine \n 
    according to their parents marital status and the number of parents they have"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> vulnerable_indivs_income_covid_age

  vulnerable_indivs_income_covid_age

  # save the plot for reference
 # function_plot_save(last_plot(), "vulnerable_indivs_child_grand_covid_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
   # reduce dimensions of vulnerable individuals and hosuehold_income to ensure adequate sample size for analysis
  mutate(
    vulnerable_individuals = ifelse(vulnerable_individuals > 0, 1, 0) |> as.factor(),
    income = ceiling(test_household_income/4)
  ) |>
  
  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(influenza_coverage_age)) |>
  summarise(count = n(), .by = c(vulnerable_individuals, income, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(vulnerable_individuals, income)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(method = "lm", aes(colour = vulnerable_individuals)) +
  function_plot_label_count(income, vulnerable_individuals) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine \n 
    according to their parents marital status and the number of parents they have"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> vulnerable_indivs_income_influenza_age

  vulnerable_indivs_income_influenza_age

  # save the plot for reference
 # function_plot_save(last_plot(), "vulnerable_indivs_child_grand_influenza_age", ".png", "Output/05_multivariate_uptake_plots")
```

#### parent_chronic_illness

```{r}
# covid uptake
cov_prepped_ivd |>
  
  # reduce dimensions of vulnerable individuals to ensure adequate sample size for analysis
  mutate(
    vulnerable_individuals = ifelse(vulnerable_individuals > 0, 1, 0) |> as.factor()
  ) |>
  
  # ensure no missing covid vax data and stratify by vulnerable individuals and parent_chronic_illness
  filter(!is.na(covid_coverage_age)) |>
  summarise(count = n(), .by = c(vulnerable_individuals, parent_chronic_illness, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(vulnerable_individuals, parent_chronic_illness)) |>
  
  # plot
  ggplot(aes(x = parent_chronic_illness, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(method = "lm", aes(colour = vulnerable_individuals)) +
  function_plot_label_count(parent_chronic_illness, vulnerable_individuals) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine \n 
    according to their parents' chronic illness status and the presence of vulnerable individuals at home"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> vulnerable_indivs_parent_chronic_illness_covid_age

  vulnerable_indivs_parent_chronic_illness_covid_age

  # save the plot for reference
  function_plot_save(last_plot(), "vulnerable_indivs_parent_chronic_illness_covid_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
   # reduce dimensions of vulnerable individuals and hosuehold_parent_chronic_illness to ensure adequate sample size for analysis
  mutate(
    vulnerable_individuals = ifelse(vulnerable_individuals > 0, 1, 0) |> as.factor()
  ) |>
  
  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(influenza_coverage_age)) |>
  summarise(count = n(), .by = c(vulnerable_individuals, parent_chronic_illness, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(vulnerable_individuals, parent_chronic_illness)) |>
  
  # plot
  ggplot(aes(x = parent_chronic_illness, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(method = "lm", aes(colour = vulnerable_individuals)) +
  function_plot_label_count(parent_chronic_illness, vulnerable_individuals) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine \n 
    according to their parents marital status and the number of parents they have"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> vulnerable_indivs_parent_chronic_illness_influenza_age

  vulnerable_indivs_parent_chronic_illness_influenza_age

  # save the plot for reference
  function_plot_save(last_plot(), "vulnerable_indivs_parent_chronic_illness_influenza_age", ".png", "Output/05_multivariate_uptake_plots")
```


#### child_grand, household_income, vulnerable_individuals
Given such small sample sizes, is it even feasible to perform multivariate stratification
```{r}
# covid coverage
cov_prepped_ivd |>
  
  # ensure no missing covid data
  filter(!is.na(covid_coverage_age)) |>
  
  # reduce dimensions of income and vulnerable individuals
  mutate(
    income = ceiling(test_household_income/5),
    vulnerable_individuals = ifelse(vulnerable_individuals > 0, 1, 0) |> as.factor(),
    child_grand = ifelse(child_grand > 0, 1, 0) |> as.factor()
  ) |>
  
  summarise(count = n(), .by = c(income, vulnerable_individuals, covid_coverage_age, child_grand)) |>
  mutate(proportion = count / sum(count), .by = c(child_grand, vulnerable_individuals, income)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(aes(colour = vulnerable_individuals), method = "lm") +
  geom_text(
    aes(x = income, label = count, colour = vulnerable_individuals),
    position = "jitter"
  ) +
  ylim(c(0,1.1)) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(child_grand)) +
  labs(
    title = "how the proportion of children with each level of coverage of the covid vaccine varies \n with income and the presence of a vulnearble individual & grandparent in the same household",
    subtitle = "column facets represent covid vaccination status and row facets the presence of grandaprents"
  ) +
  theme(plot.title = element_text(size = 10)) -> vulnerable_indivs_child_grand_income_parent_chronic_covid_age

vulnerable_indivs_child_grand_income_parent_chronic_covid_age

# influenza coverage
inf_prepped_ivd |>
  
  # ensure no missing covid data
  filter(!is.na(influenza_coverage_age)) |>
  
  # reduce dimensions of income and vulnerable individuals
  mutate(
    income = ceiling(test_household_income/5),
    vulnerable_individuals = ifelse(vulnerable_individuals > 0, 1, 0) |> as.factor(),
    child_grand = ifelse(child_grand > 0, 1, 0) |> as.factor()
  ) |>
  
  summarise(count = n(), .by = c(income, vulnerable_individuals, influenza_coverage_age, child_grand)) |>
  mutate(proportion = count / sum(count), .by = c(child_grand, vulnerable_individuals, income)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion)) +
  geom_point(aes(colour = vulnerable_individuals)) +
  geom_smooth(aes(colour = vulnerable_individuals), method = "lm") +
  geom_text(
    aes(x = income, label = count, colour = vulnerable_individuals),
    position = "jitter"
  ) +
  ylim(c(0,1.1)) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(child_grand)) +
  labs(
    title = "how the proportion of children with each level of coverage of the influenza vaccine varies \n with income and the presence of a vulnearble individual & grandparent in the same household",
    subtitle = "column facets represent influenza vaccination status and row facets the presence of grandaprents"
  ) +
  theme(plot.title = element_text(size = 10)) -> vulnerable_indivs_child_grand_income_parent_chronic_influenza_age

vulnerable_indivs_child_grand_income_parent_chronic_influenza_age
  # save
```
### (M) household_total
#### child_grand, test_parents_marital_status
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # reduce the dimensions of child_grand
  mutate(child_grand = ifelse(child_grand <1, 0, 1) |> as.factor()) |>
  
  # ensure no missing covid vax data and stratify by grandparents
  filter(!is.na(covid_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, child_grand, test_parents_marital_status, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, test_parents_marital_status, child_grand)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(method = "lm", aes(colour = child_grand)) +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(test_parents_marital_status)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine according to \n the total number of individuals,  presence of grandaprents in their household \n and parents' marital status",
    subtitle = "row facets represent if the child's parents are married (0) or unmarried (1) \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_child_grand_parent_marital_cov_age

  household_total_child_grand_parent_marital_cov_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_grand_parent_marital_cov_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # reduce the dimensions of child_grand
  mutate(child_grand = ifelse(child_grand <1, 0, 1) |> as.factor()) |>
  
  # ensure no missing influenza vax data and stratify by grandparents
  filter(!is.na(influenza_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, child_grand, test_parents_marital_status, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, test_parents_marital_status, child_grand)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(method = "lm", aes(colour = child_grand)) +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(test_parents_marital_status)) +
  ylim(c(0,1)) +
  labs(
      title = "proportion of children with each uptake of the covid vaccine according to \n the total number of individuals,  presence of grandaprents in their household \n and parents' marital status",
    subtitle = "row facets represent if the child's parents are married (0) or unmarried (1) \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.7))  -> household_total_child_grand_parent_marital_inf_age

  household_total_child_grand_parent_marital_inf_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_grand_parent_marital_inf_age", ".png", "Output/05_multivariate_uptake_plots")
```

#### child_grand, parents_highest_education
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # reduce the dimensions of child_grand
  mutate(child_grand = ifelse(child_grand <1, 0, 1) |> as.factor()) |>
  
  # ensure no missing covid vax data and stratify by grandparents
  filter(!is.na(covid_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, child_grand, parents_highest_education, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, parents_highest_education, child_grand)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(method = "lm", aes(colour = child_grand)) +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parents_highest_education)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine according to \n the total number of individuals,  presence of grandaprents in their household \n and parents' highest eduacation",
    subtitle = "row facets represent the parents' highest education \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_child_grand_parent_education_cov_age

  household_total_child_grand_parent_education_cov_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_grand_parent_education_cov_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # reduce the dimensions of child_grand
  mutate(child_grand = ifelse(child_grand <1, 0, 1) |> as.factor()) |>
  
  # ensure no missing influenza vax data and stratify by grandparents
  filter(!is.na(influenza_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, child_grand, parents_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, parents_highest_education, child_grand)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(method = "lm", aes(colour = child_grand)) +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(parents_highest_education)) +
  ylim(c(0,1)) +
  labs(
      title = "proportion of children with each uptake of the influenza vaccine according to \n the total number of individuals,  presence of grandaprents in their household \n and parents' highest eduacation",
    subtitle = "row facets represent the parents' highest education \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.7))  -> household_total_child_grand_parent_education_inf_age

  household_total_child_grand_parent_education_inf_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_grand_parent_education_inf_age", ".png", "Output/05_multivariate_uptake_plots")
```

#### child_grand
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # reduce the dimensions of child_grand
  mutate(child_grand = ifelse(child_grand <1, 0, 1) |> as.factor()) |>
  
  # ensure no missing covid vax data and stratify by grandparents
  filter(!is.na(covid_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, child_grand, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, child_grand)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(method = "lm", aes(colour = child_grand)) +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(child_grand)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine according to \n the total number of individuals, and presence of grandaprents in their household ",
    subtitle = "row facets represent the lack of (0) and presence of (1) grandparents \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_child_grand_cov_age

  household_total_child_grand_cov_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_grand_cov_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # reduce the dimensions of child_grand
  mutate(child_grand = ifelse(child_grand <1, 0, 1) |> as.factor()) |>
  
  # ensure no missing influenza vax data and stratify by grandparents
  filter(!is.na(influenza_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, child_grand, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, child_grand)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(method = "lm", aes(colour = child_grand)) +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(child_grand)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine according to \n the total number of individuals, and presence of grandaprents in their household ",
    subtitle = "row facets represent the lack of (0) and presence of (1) grandparents \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.7))  -> household_total_child_grand_inf_age

  household_total_child_grand_inf_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_grand_inf_age", ".png", "Output/05_multivariate_uptake_plots")
```


#### test_parents_marital_status
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing covid vax data and stratify by respondign parent's marital status
  filter(!is.na(covid_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, test_parents_marital_status, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, test_parents_marital_status)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point() +
  geom_smooth(method = "lm") +
  function_plot_label_count(test_parents_marital_status, covid_coverage_age) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(test_parents_marital_status)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine according to \n the total number of individuals, and presence of grandaprents in their household ",
    subtitle = "row facets represent responding parent's marital status: (0) married, (1) unmarried \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_child_parents_marital_cov_age

  household_total_child_parents_marital_cov_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_parents_marital_cov_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing influenza vax data and stratify by marital status
  filter(!is.na(influenza_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, test_parents_marital_status, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, test_parents_marital_status)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point() +
  geom_smooth(method = "lm") +
  function_plot_label_count(test_parents_marital_status, influenza_coverage_age) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(test_parents_marital_status)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine according to \n the total number of individuals, and the responding parent's marital status ",
    subtitle = "row facets represent the responding parent's marital status: (0) married, (1) unmarried\n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.7)) -> household_total_child_parents_marital_inf_age

  household_total_child_parents_marital_inf_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_child_parents_marital_inf_age", ".png", "Output/05_multivariate_uptake_plots")
```

#### test_parents_marital_status, household_income
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # reduce the dimensions of household income
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # ensure no missing covid vax data and stratify by grandparents
  filter(!is.na(covid_coverage_age) & household_total < 8 & !is.na(income)) |>
  summarise(count = n(), .by = c(household_total, income, test_parents_marital_status, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, test_parents_marital_status, income)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = test_parents_marital_status)) +
  geom_smooth(method = "lm", aes(colour = test_parents_marital_status)) +
  function_plot_label_count(test_parents_marital_status, covid_coverage_age) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(income)) +
  ylim(c(0,1.05)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine according to the total number of individuals,  household income and parents' marital status",
    subtitle = "row facets represent the total annual household income as multiples of 4million JPY \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_parent_marital_income_cov_age

  household_total_parent_marital_income_cov_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_parent_marital_income_cov_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # reduce the dimensions of household income
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # ensure no missing influenza vax data and stratify by grandparents
  filter(!is.na(influenza_coverage_age) & household_total < 8 & !is.na(income)) |>
  summarise(count = n(), .by = c(household_total, income, test_parents_marital_status, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, test_parents_marital_status, income)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point(aes(colour = test_parents_marital_status)) +
  geom_smooth(method = "lm", aes(colour = test_parents_marital_status)) +
  function_plot_label_count(test_parents_marital_status, influenza_coverage_age) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(income)) +
  ylim(c(0,1.05)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine according to the total number of individuals, household income and parents' marital status",
    subtitle = "row facets represent the total annual household income as multiples of 4million JPY \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_parent_marital_income_inf_age

  household_total_parent_marital_income_inf_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_parent_marital_income_inf_age", ".png", "Output/05_multivariate_uptake_plots")  
```
#### parents_highest_education
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing covid vax data and stratify by parent's highest education
  filter(!is.na(covid_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, parents_highest_education, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, parents_highest_education)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point() +
  geom_smooth(method = "lm") +
  function_plot_label_count(parents_highest_education, covid_coverage_age) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parents_highest_education)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine according to \n the total number of individuals, and the parents' highest educations",
    subtitle = "row facets represent responding parent's highest educations \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_highest_education_cov_age

  household_total_highest_education_cov_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_highest_education_cov_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing infid vax data and stratify by parent's highest education
  filter(!is.na(influenza_coverage_age) & household_total < 8) |>
  summarise(count = n(), .by = c(household_total, parents_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, parents_highest_education)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion)) +
  geom_point() +
  geom_smooth(method = "lm") +
  function_plot_label_count(parents_highest_education, influenza_coverage_age) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(parents_highest_education)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine according to \n the total number of individuals, and the parents' highest educations",
    subtitle = "row facets represent responding parent's highest educations \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_highest_education_inf_age

  household_total_highest_education_inf_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_highest_education_inf_age", ".png", "Output/05_multivariate_uptake_plots")
```
#### child_siblings and test_child_siblings
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # account for both test_child_siblings and child_siblings
  pivot_longer(cols = c(test_child_siblings, child_siblings), values_to = "siblings", names_to = "type") |>
  
  # ensure no missing covid vax data and reduce the dimensions of the number of siblings to ensure we have an adequate sample size for analysis
  filter(!is.na(covid_coverage_age) & household_total < 8) |>
  mutate(siblings = ifelse(siblings < 3, siblings, "3+") |> as.factor()) |>
  
  # stratify by household totals, silbings and test siblings
  summarise(count = n(), .by = c(household_total, siblings, type, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, siblings, type)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion, group = type)) +
  geom_point(aes(colour = type), position = position_dodge(width = 0.3)) +
  geom_smooth(method = "lm", aes(colour = type), position = position_dodge(width = 1.0)) +
  function_plot_label_count(household_total, covid_coverage_age) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(siblings)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine according to \n the total number of individuals, and siblings or test siblings they have at home",
    subtitle = "row facets represent the number of sibligns (test or non test) at home \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_siblings_test_siblings_cov_age

 household_total_siblings_test_siblings_cov_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_siblings_test_siblings_cov_age", ".png", "Output/05_multivariate_uptake_plots")
  
# influenza uptake
inf_prepped_ivd |>
  
  # account for both test_child_siblings and child_siblings
  pivot_longer(cols = c(test_child_siblings, child_siblings), values_to = "siblings", names_to = "type") |>
  
  # ensure no missing covid vax data and reduce the dimensions of the number of siblings to ensure we have an adequate sample size for analysis
  filter(!is.na(influenza_coverage_age) & household_total < 8) |>
  mutate(siblings = ifelse(siblings < 3, siblings, "3+") |> as.factor()) |>
  
  # stratify by household totals, silbings and test siblings
  summarise(count = n(), .by = c(household_total, siblings, type, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(household_total, siblings, type)) |>
  
  
  # plot
  ggplot(aes(x = household_total, y = proportion, group = type)) +
  geom_point(aes(colour = type), position = position_dodge(width = 0.3)) +
  geom_smooth(method = "lm", aes(colour = type), position = position_dodge(width = 1.0)) +
  function_plot_label_count(household_total, influenza_coverage_age) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(siblings)) +
  ylim(c(0,1)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine according to \n the total number of individuals, and siblings or test siblings they have at home",
    subtitle = "row facets represent the number of sibligns (test or non test) at home \n colum facets represent their vaccination status"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> household_total_siblings_test_siblings_inf_age

 household_total_siblings_test_siblings_inf_age

  # save the plot for reference
  function_plot_save(last_plot(), "household_total_siblings_test_siblings_inf_age", ".png", "Output/05_multivariate_uptake_plots")
```

### (M) child_grand
#### household_income
```{r}
# covid
cov_prepped_ivd |>
  
  # ensure no missing covid data
  filter(!is.na(covid_coverage_age)) |>
  
  # reduce dimensions of income and child_grand
  mutate(
    #test_household_income = ceiling(test_household_income/5),
    child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+")
  ) |>
  
  summarise(count = n(), .by = c(test_household_income, covid_coverage_age, child_grand)) |>
  mutate(proportion = count / sum(count), .by = c(child_grand, test_household_income)) -> child_grand_income_cov_age
  
child_grand_income_cov_age |>
  # plot
  ggplot(aes(x = test_household_income, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(aes(colour = child_grand), method = "lm") +
  geom_text(
    aes(x = test_household_income, label = count, colour = child_grand),
    position = "jitter"
  ) +
  ylim(c(0,1.1)) +
  facet_grid(cols = vars(covid_coverage_age)) 

# influenza
inf_prepped_ivd |>
  
  # ensure no missing covid data
  filter(!is.na(influenza_coverage_age)) |>
  
  # reduce dimensions of income and child_grand
  mutate(
    #test_household_income = ceiling(test_household_income / 5),
    child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+")
  ) |>
  
  summarise(count = n(), .by = c(test_household_income, influenza_coverage_age, child_grand)) |>
  mutate(proportion = count / sum(count), .by = c(child_grand, test_household_income)) -> child_grand_income_inf_age

child_grand_income_inf_age |>
  # plot
  ggplot(aes(x = test_household_income, y = proportion)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(aes(colour = child_grand), method = "lm") +
  geom_text(
    aes(x = test_household_income, label = count, colour = child_grand),
    position = "jitter"
  ) +
  ylim(c(0,1.1)) +
  facet_grid(cols = vars(influenza_coverage_age)) 
```

#### child_parents
let's examine how the number of parents a child has, together with the presence of a grandaprent affects the uptake of the vaccine
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(covid_coverage_age)) |>
  
  # switch between presence of grandparents and no. of grandparents
  # mutate(child_grand = ifelse(child_grand >= 1, 1, 0)) |>
  
  # stratify data by the child's coverage statuses, parent's marital statuses and the no. of grandparents
  function_data_triple_stratify(child_parents, as.factor, child_grand, covid_coverage_age) -> child_grand_parents_covid_age

# plot
child_grand_parents_covid_age |>
  ggplot(aes(x = child_grand, y = proportion, group = child_parents)) +
  geom_point(aes(colour = child_parents)) +
  geom_smooth(aes(colour = child_parents), method = "lm") +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "visualising how the uptake of the covid vaccine varies with an increasing number of grandparents, for children with 1 and 2 parents",
    subtitle = "the columns represent the degree of coverage with the coid vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )

# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(influenza_coverage_age)) |>
  
  # switch between presence of grandparents and no. of grandparents
   #mutate(child_grand = ifelse(child_grand >= 1, 1, 0)) |>
  
  # stratify data by the child's coverage statuses, parent's marital statuses and the no. of grandparents
  function_data_triple_stratify(child_parents, as.factor, child_grand, influenza_coverage_age) -> child_grand_parents_inf_age

# plot
child_grand_parents_inf_age |>
  ggplot(aes(x = child_grand, y = proportion, group = child_parents)) +
  geom_point(aes(colour = child_parents)) +
  geom_smooth(aes(colour = child_parents), method = "lm") +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "visualising how the uptake of the influenza vaccine varies with an increasing number of grandparents, for children with 1 and 2 parents",
    subtitle = "the columns represent the degree of coverage with the influenza vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )
```   

But maybe this is due to a decrease in income per capita? So let's try controlling for household income
#### household_income, child_parents
```{r}
# covid_uptake 
cov_prepped_ivd |>

  # filter out households that didn't provide an income response or vaccine data
  filter(!is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  
  # reduce dimensions of income and/or grandparents so we have a larger sample to work with
  #mutate(test_household_income = ceiling(test_household_income / 5)) |>
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>

  
  # stratify the data by the child's uptake status, number of parents, household_income and the number of grandparents
  summarise(count = n(), .by = c(test_household_income, child_parents, child_grand, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, child_parents, child_grand)) -> child_grand_parents_income_cov_age

# plot
child_grand_parents_income_cov_age |>
  ggplot(aes(x = test_household_income, y = proportion, group = child_parents)) +
  geom_point(aes(colour = child_parents)) +
  geom_smooth(aes(colour = child_parents), method = "lm") +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(child_grand)) +
  ylim(c(0,1)) +
  labs(
    title = "visualising how covid vaccine uptake in COI varies with household_income for different number of parents and grandparents",
    subtitle = "columns represent the uptake status of the covid vaccine and rows represent the number of grandparents the child has"
  )

# influenza uptake 
inf_prepped_ivd |>

  # filter out households that didn't provide an income response or vaccine data
  filter(!is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
  
  # reduce dimensions of income and/or grandparents so we have a larger sample to work with
  #mutate(test_household_income = ceiling(test_household_income / 5)) |>
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>

  
  # stratify the data by the child's uptake status, number of parents, household_income and the number of grandparents
  summarise(count = n(), .by = c(test_household_income, child_parents, child_grand, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, child_parents, child_grand)) -> child_grand_parents_income_inf_age

# plot
child_grand_parents_income_inf_age |>
  ggplot(aes(x = test_household_income, y = proportion, group = child_parents)) +
  geom_point(aes(colour = child_parents)) +
  geom_smooth(aes(colour = child_parents), method = "lm") +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(child_grand)) +
  ylim(c(0,1)) +
  labs(
    title = "visualising how influenza vaccine uptake in COI varies with household_income for different number of parents and grandparents",
    subtitle = "columns represent the uptake status of the influenza vaccine and rows represent the number of grandparents the child has"
  )
```


#### siblings_over_18, household_income
```{r}
# covid_uptake 
cov_prepped_ivd |>

  # filter out households that didn't provide an income response or vaccine data
  filter(!is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  
  # reduce the dimensions of the number of siblings over 18 so we can work with a larger sample size
  mutate(siblings_over_18 = ifelse(siblings_over_18 < 2, as.character(siblings_over_18), "2+")) |>
  
  # reduce dimensions of income and/or grandparents so we have a larger sample to work with
  #mutate(test_household_income = ceiling(test_household_income / 5)) |>
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>
  
  # factorise siblings over 18
  mutate(siblings_over_18 = as.character(siblings_over_18)) |>
  
  # stratify the data by the child's uptake status, number of parents, household_income and the number of grandparents
  summarise(count = n(), .by = c(test_household_income, siblings_over_18, child_grand, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, siblings_over_18, child_grand)) -> child_grand_siblings_over_18_income_cov_age

# plot
child_grand_siblings_over_18_income_cov_age |>
  ggplot(aes(x = test_household_income, y = proportion, group = child_grand)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(aes(colour = child_grand), method = "lm") +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(siblings_over_18)) +
  ylim(c(0,1)) +
  labs(
    title = "visualising how covid vaccine uptake in COI varies with household_income for different number of parents and grandparents",
    subtitle = "columns represent the uptake status of the covid vaccine and rows represent the number of siblings over 18 the child has"
  )

# influenza uptake 
inf_prepped_ivd |>

  # filter out households that didn't provide an income response or vaccine data
  filter(!is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
  
  # factorise siblings over 18
  mutate(siblings_over_18 = as.character(siblings_over_18)) |>

  # reduce the dimensions of the number of siblings over 18 so we can work with a larger sample size
  mutate(siblings_over_18 = ifelse(siblings_over_18 < 2, as.character(siblings_over_18), "2+")) |>
  
  # reduce dimensions of income and/or grandparents so we have a larger sample to work with
  #mutate(test_household_income = ceiling(test_household_income / 5)) |>
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>

  
  # stratify the data by the child's uptake status, number of parents, household_income and the number of grandparents
  summarise(count = n(), .by = c(test_household_income, siblings_over_18, child_grand, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, siblings_over_18, child_grand)) -> child_grand_siblings_over_18_income_inf_age

# plot
child_grand_siblings_over_18_income_inf_age |>
  ggplot(aes(x = test_household_income, y = proportion, group = child_grand)) +
  geom_point(aes(colour = child_grand)) +
  geom_smooth(aes(colour = child_grand), method = "lm") +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(siblings_over_18)) +
  ylim(c(0,1)) +
  labs(
    title = "visualising how influenza vaccine uptake in COI varies with household_income for different number of siblings over 18 and grandparents",
    subtitle = "columns represent the uptake status of the influenza vaccine and rows represent the number of siblings over 18 the child has"
  )

```

#### siblings_over_18
breakdown of children according to the number of silbings over 18yo they have
```{r}
cov_prepped_ivd |>
  xtabs(~ siblings_over_18, data = _)
```

```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(covid_coverage_age)) |>
  
  # reduce the dimensions of the number of siblings over 18 so we can work with a larger sample size
  mutate(siblings_over_18 = ifelse(siblings_over_18 < 2, as.character(siblings_over_18), "2+")) |>
  
  # stratify data by the child's coverage statuses, parent's marital statuses and the no. of grandparents
  function_data_triple_stratify(siblings_over_18, as.factor, child_grand, covid_coverage_age) -> child_grand_siblings_over_18_covid_age

# plot
child_grand_siblings_over_18_covid_age |>
  ggplot(aes(x = child_grand, y = proportion, group = siblings_over_18)) +
  geom_point(aes(colour = siblings_over_18)) +
  geom_smooth(aes(colour = siblings_over_18), method = "lm") +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "visualising how the uptake of the covid vaccine varies with an increasing number of grandparents, for children with different numbers of siblings over 18",
    subtitle = "the columns represent the degree of coverage with the coid vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )

# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(influenza_coverage_age)) |>
  
  # reduce the dimensions of the number of siblings over 18 so we can work with a larger sample size
  mutate(siblings_over_18 = ifelse(siblings_over_18 < 2, as.character(siblings_over_18), "2+")) |>
  
  # stratify data by the child's coverage statuses, parent's marital statuses and the no. of grandparents
  function_data_triple_stratify(siblings_over_18, as.factor, child_grand, influenza_coverage_age) -> child_grand_siblings_over_18_inf_age

# plot
child_grand_siblings_over_18_inf_age |>
  ggplot(aes(x = child_grand, y = proportion, group = siblings_over_18)) +
  geom_point(aes(colour = siblings_over_18)) +
  geom_smooth(aes(colour = siblings_over_18), method = "lm") +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "visualising how the uptake of the influenza vaccine varies with an increasing number of grandparents, for children with different numbers of siblings over 18",
    subtitle = "the columns represent the degree of coverage with the influenza vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )
```   

#### father_employment status
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(covid_coverage_age)) |>
  
  # reduce the dimensions of the number of grandparents so we have larger samples for analysis
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>

 # stratify data by the child's coverage statuses, parent's marital statuses and the father's employment status
  function_data_triple_stratify(father_employment_status, as.factor, child_grand, covid_coverage_age) -> child_grand_father_employment_covid_age

# plot
child_grand_father_employment_covid_age |>
  ggplot(aes(x = child_grand, y = proportion, group = father_employment_status)) +
  geom_point(aes(colour = father_employment_status)) +
  geom_smooth(aes(colour = father_employment_status), method = "lm") +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "visualising how the uptake of the covid vaccine varies with an increasing number of grandparents, for children with father's of different employment statuses",
    subtitle = "the columns represent the degree of coverage with the coid vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )


# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(influenza_coverage_age)) |>
  
  # reduce the dimensions of the number of grandparents so we have larger samples for analysis
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>
  
 # stratify data by the child's coverage statuses, parent's marital statuses and the father's employment status
  function_data_triple_stratify(father_employment_status, as.factor, child_grand, influenza_coverage_age) -> child_grand_father_employment_influenza_age

# plot
child_grand_father_employment_influenza_age |>
  ggplot(aes(x = child_grand, y = proportion, group = father_employment_status)) +
  geom_point(aes(colour = father_employment_status)) +
  geom_smooth(aes(colour = father_employment_status), method = "lm") +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "visualising how the uptake of the influenza vaccine varies with an increasing number of grandparents, for children with father's of different employment statuses",
    subtitle = "the columns represent the degree of coverage with the influenza vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )
```

#### mother_employment_status
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(covid_coverage_age)) |>
  
  # reduce the dimensions of the number of grandparents so we have larger samples for analysis
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>

 # stratify data by the child's coverage statuses, parent's marital statuses and the mother's employment status
  function_data_triple_stratify(mother_employment_status, as.factor, child_grand, covid_coverage_age) -> child_grand_mother_employment_covid_age

# plot
child_grand_mother_employment_covid_age |>
  ggplot(aes(x = child_grand, y = proportion, group = mother_employment_status)) +
  geom_point(aes(colour = mother_employment_status)) +
  geom_smooth(aes(colour = mother_employment_status, fill = mother_employment_status), method = "lm", alpha = 0.1) +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "visualising how the uptake of the covid vaccine varies with an increasing number of grandparents, for children with mother's of different employment statuses",
    subtitle = "the columns represent the degree of coverage with the coid vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )
  
  # run an ANOVA to check if there's a different in no coverage of the covid vaccine, with grandparents
  dummy_cov_prepped_ivd |>
    
    # ensure no missing data 
    filter(!is.na(child_grand) & !is.na(covid_coverage_age0)) |>
  
    # reduce the dimensions of the number of grandparents so we have larger samples for analysis
    mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+")) |> 
    
      # run an anova that includes the interaction between the number of grandparents and the mother's employment status
      aov(covid_coverage_age0 ~ child_grand + mother_employment_status + child_grand * mother_employment_status, data = _) |>
      Anova(type = "III")
    
     

# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(influenza_coverage_age)) |>
  
  # reduce the dimensions of the number of grandparents so we have larger samples for analysis
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>
  
 # stratify data by the child's coverage statuses, parent's marital statuses and the mother's employment status
  function_data_triple_stratify(mother_employment_status, as.factor, child_grand, influenza_coverage_age) -> child_grand_mother_employment_influenza_age

# plot
child_grand_mother_employment_influenza_age |>
  ggplot(aes(x = child_grand, y = proportion, group = mother_employment_status)) +
  geom_point(aes(colour = mother_employment_status)) +
  geom_smooth(aes(colour = mother_employment_status, fill = mother_employment_status), method = "lm", alpha = 0.1) +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "visualising how the uptake of the influenza vaccine varies with an increasing number of grandparents, for children with mother's of different employment statuses",
    subtitle = "the columns represent the degree of coverage with the influenza vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )
```


#### mother_stay_home
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(covid_coverage_age)) |>
  
  # reduce the dimensions of the number of grandparents so we have larger samples for analysis
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>

 # stratify data by the child's coverage statuses, parent's marital statuses and the father's employment status
  function_data_triple_stratify(mother_stay_home, as.factor, child_grand, covid_coverage_age) -> child_grand_mother_stay_home_covid_age

# plot
child_grand_mother_stay_home_covid_age |>
  ggplot(aes(x = child_grand, y = proportion, group = mother_stay_home)) +
  geom_point(aes(colour = mother_stay_home)) +
  geom_smooth(aes(colour = mother_stay_home), method = "lm") +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "visualising how the uptake of the covid vaccine varies with an increasing number of grandparents, depending on if the child's mother stays home or not",
    subtitle = "the columns represent the degree of coverage with the coid vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )


# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(influenza_coverage_age)) |>
  
  # reduce the dimensions of the number of grandparents so we have larger samples for analysis
  mutate(child_grand = ifelse(child_grand < 2, as.character(child_grand), "2+") ) |>
  
 # stratify data by the child's coverage statuses, parent's marital statuses and the father's employment status
  function_data_triple_stratify(mother_stay_home, as.factor, child_grand, influenza_coverage_age) -> child_grand_mother_stay_home_influenza_age

# plot
child_grand_mother_stay_home_influenza_age |>
  ggplot(aes(x = child_grand, y = proportion, group = mother_stay_home)) +
  geom_point(aes(colour = mother_stay_home)) +
  geom_smooth(aes(colour = mother_stay_home), method = "lm") +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "visualising how the uptake of the influenza vaccine varies with an increasing number of grandparents, depending on if the child's mother stays home or not",
    subtitle = "the columns represent the degree of coverage with the influenza vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )
```

#### household_total
```{r}
# covid uptake
cov_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(covid_coverage_age)) |>
  
  # reduce the dimensions of the household so we can work with a larger sample size
  mutate(household_total = ifelse(household_total < 4, as.character(household_total), "4+")) |>
  
  # stratify data by the child's coverage statuses, parent's marital statuses and the no. of grandparents
  function_data_triple_stratify(household_total, as.factor, child_grand, covid_coverage_age) -> child_grand_household_total_covid_age

# plot
child_grand_household_total_covid_age |>
  ggplot(aes(x = child_grand, y = proportion, group = household_total)) +
  geom_point(aes(colour = household_total)) +
  geom_smooth(aes(colour = household_total), method = "lm") +
  function_plot_label_count(child_grand, covid_coverage_age) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "visualising how the uptake of the covid vaccine varies with an increasing number of grandparents, for children with the total household size",
    subtitle = "the columns represent the degree of coverage with the coid vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )

# influenza uptake
inf_prepped_ivd |>
  
  # ensure no missing data 
  filter(!is.na(child_grand) & !is.na(influenza_coverage_age)) |>
  
  # reduce the dimensions of the household so we can work with a larger sample size
  mutate(household_total = ifelse(household_total < 4, as.character(household_total), "4+")) |>
  
  # stratify data by the child's coverage statuses, parent's marital statuses and the no. of grandparents
  function_data_triple_stratify(household_total, as.factor, child_grand, influenza_coverage_age) -> child_grand_household_total_influenza_age

# plot
child_grand_household_total_influenza_age |>
  ggplot(aes(x = child_grand, y = proportion, group = household_total)) +
  geom_point(aes(colour = household_total)) +
  geom_smooth(aes(colour = household_total), method = "lm") +
  function_plot_label_count(child_grand, influenza_coverage_age) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "visualising how the uptake of the influenza vaccine varies with an increasing number of grandparents, for children with the total household size",
    subtitle = "the columns represent the degree of coverage with the inf vax we're looking at: unvaxxed (0), partial vax (1), full vax (2)"
  )
```   