---
title: "05_investigating interdependence"
format: 
  html:
    fig-asp: 0.8
execute: 
  eval: true
  echo: false
---

Libraries
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)
library(patchwork)

# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

Data
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )

# transformed age data
age <- 
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_age_data.RDS"
    )
  )

# Creating data frames for bivariate and multivariate analysis
# limit indep data to only those households with a COI
prepped_ivd <- ivd |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1)

# influenza and covid variable data
inf_prepped_ivd <- bind_cols(inf, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1) 

# covid and independent variable data
cov_prepped_ivd <- bind_cols(cov, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1)

```
This document will be used to analyse the interdependencies between variables we have processed thusfar,
to help us determine the sort of relationships that exist between them, and aid us in choosing a model to use.

## Section 1 - collinearity between independent (explanatory) variables
### Breakdown of coverage statuses
```{r}
# stratified counts of covid coverages
xtabs(~ covid_coverage_age + covid_coverage_dosage, data = cov_ivd)

# stratified counts of influenza coverages
xtabs(~ influenza_coverage_age + influenza_coverage_dosage, data = inf_ivd)
```

### Numerical variables
Check if any of the continuous numerical variables are collinear

```{r}
# extract all numerical variables (including test_household income)
ivd |>
  filter(child_of_interest == 1) |>
  
  # make test_household_income numeric
  mutate(test_household_income = as.numeric(test_household_income)) |>
  
  # transform test_household_income such that each value represents the number of JPY in millions
  mutate(
    test_household_income = case_when(
      test_household_income == 1 ~ 0,
      test_household_income %in% 2:3 ~ 1,
      test_household_income >= 4 ~ test_household_income - 2
    )
  ) |>
  
  select(!where(is.factor) & !starts_with("respondent_") & !starts_with("perception")) |>
  filter(!is.na(test_household_income)) |>

  # calculate correlation matrix for cases with a COI
  cor() |>
  
  # plot the correlation plot
  ggcorrplot(method = "square", lab = TRUE, lab_size = 3)
```
The variables that display the most collinearity are:
household total
1. child siblings
2. child_borthers
3. child_sisters
4. child_grand

Furthermore, child_siblngs is associated withthe number of brothers and the number of sisters

### Categorical variables
Check if there's **covariance** between categorical variables

**you cAN look at this type of graph for variables you suspect may be highly correlated**
```{r}
# prepare data frame to be passed into recursive function
ivd$age_of_interest <- age$age_of_interest
prepped_ivd <- ivd |>
  filter(child_of_interest != 0)

# read dependencies
causal_relationship_combinations <-
  readRDS(here("Output", "causal_relationship_combinations.RDS")) |>
  rename(variable1 = name, variable2 = to) |>

  # dropping rows with COI's_familial_factors and "vaccine_uptake" for now
  filter(!if_any(everything(), ~ .x %in% c("vaccine uptake", "COI's familial factors")))
  
# plot every pair 
# input the list of factor_pairs, the function, and pass the dataframe ivd to the df argument of our custom fn
list_of_plots <- pmap(causal_relationship_combinations, function_plot_corr_pairs, df = prepped_ivd)
```

save the categorical plots

```{r}
saveRDS(list_of_plots, here("Output", "causal_relationship_plots.RDS"))
```


## Multivariate plots (correlation)

In the following section the variable of interest which corresponds to the variable in the "TO" row of the codebook will be associated with `###` whilst every other sub variable, which corresponds to the variable(s) in the "From" row for each variable of itnerest, will be associated with `####` 

### education
#### marital status 
Invesigating the distribution of educational attainments between mothers who are married and who are single
```{r}
# educational distribution of all mothers
ivd |>
  filter(child_of_interest == 1) |>
  summarise(n(), mean(test_household_income, na.rm = TRUE), .by = mother_highest_education) |>
  arrange(mother_highest_education)


# educational distribution of single mothers
ivd |>
  filter(child_of_interest == 1 & child_parents == 1 & parent_1_sex == 1) |>
  summarise(n(), mean(test_household_income, na.rm = TRUE), .by = mother_highest_education) |>
  arrange(mother_highest_education)
```
It is evident that single mothers are disproportionately from lower educational backgrounds, with a
much greater proportion of them having only graduated HS/MS and JC/TC as compared to the general mother populus

### test_household_income
#### marital_status and sex
Against marital status and, the sex of the parent
```{r}
ivd |>
     filter(child_of_interest == 1) |>
     ggplot() +
     geom_boxplot(aes(x = test_parents_marital_status, y = test_household_income, fill = parent_1_sex))
```

Against marital status and, sex for single parent children
```{r}
ivd |>
   filter(child_of_interest == 1 & child_parents == 1) |>
   summarise(n(), mean(test_household_income, na.rm = TRUE), .by = c(parent_1_sex, test_parents_marital_status)) |>
  arrange(parent_1_sex, test_parents_marital_status)
```
- When it is a single parent family, we observe that unmarried fathers earn more on average than married fathers (with only 1 child) but married mothers earn more than unmarried mothers. This contradicts the idea that on average, unmarried households earn less than married households

#### education and marital status 
Testing how the test_household_income varaies with the mother and father's highest education
```{r}
ivd |>
  filter(child_of_interest == 1) |>
  ggplot() +
  geom_boxplot(aes(x = father_highest_education, y = test_household_income))

ivd |>
  filter(child_of_interest == 1) |>
  ggplot() +
  geom_boxplot(aes(x = mother_highest_education, y = test_household_income))

ivd |>
  filter(child_of_interest == 1) |>
  ggplot() +
  geom_boxplot(aes(x = parents_highest_education, y = test_household_income))
```
Mothers who graduated from technical colleges and postgraduate institutions are associated wtih a higher household income than fathers of the same educational attainments

**But, could this be due to marrying partners of the same or higher educational attainment on the mothers part? Or is this due solely to educatioanl attainment itself**

Testing for different permutations of the father's and mother's highest education
```{r}
ivd |>
    filter(child_of_interest == 1) |>
    summarise(count = n(), mean = mean(test_household_income, na.rm = TRUE), .by = c(mother_highest_education, father_highest_education)) |>
    mutate(proportion = count / sum(count), .by = father_highest_education) |>
    ggplot(aes(x = father_highest_education, y = mean, colour = mother_highest_education)) +
    geom_point(aes(size = proportion))


ivd |>
    filter(child_of_interest == 1) |>
    summarise(count = n(), mean = mean(test_household_income, na.rm = TRUE), .by = c(mother_highest_education, father_highest_education)) |>
    mutate(proportion = count / sum(count), .by = mother_highest_education) |>
    ggplot(aes(x = mother_highest_education, y = mean, colour = father_highest_education)) +
    geom_point(aes(size = proportion)) 
```

Comparing the graphs of parents, we observe that, at each level of educational attainment, a greater proportion of mothers tend to be married to fathers who are of the same or higher educational attainment. (this is particularly prominent at the postgraduate and JC/TC level). 

Furthermore, if we stratify mothers earnings by their educational level for single mothers only:
```{r}
ivd |>
   filter(child_of_interest == 1 & parent_1_sex == 1) |> 
   summarise(n(), mean = mean(test_household_income, na.rm = TRUE), .by = c(test_parents_marital_status, mother_highest_education)) -> mother_marital_status_education_income

mother_marital_status_education_income |>
  arrange(mother_highest_education, test_parents_marital_status)

mother_marital_status_education_income |>
  ggplot() +
  geom_col(aes(x = mother_highest_education, y = mean, fill = test_parents_marital_status), position = "dodge")
```

Mothers who are married have ~ 2x the annual household income of their unmarried counterparts. With soem caveats for those from HS/JC. (this contradicts our assumption that mothers of each educational attainment tend to marry to fathers of a higehr attainment. If this is the case, why aren't married mothers from HS/MS earning > x2 the income of single mothers from HS/MS?) 

HS/MS: In the case of single mothers, all mothers would be working as they're likely the only source of income for their family. Whereas, if they're married, mothers of lower income households are more likely to stay home to take care of their children?

### mother stay home
#### marital status, education 
```{r}
prepped_ivd |>
  summarise(count = n(), .by = c(mother_highest_education, mother_stay_home, test_parents_marital_status)) |>
  mutate(proportion = count/sum(count), .by = c(mother_highest_education, test_parents_marital_status)) |>
  filter(mother_stay_home == 1, !is.na(mother_highest_education)) |>
  ggplot() +
  geom_col(aes(x = mother_highest_education, y = proportion, fill = test_parents_marital_status), position = "dodge") +
  labs(title = "the proportion of mothers who stay home based on thier marital \n status and educational attainment")
```
The proportion of married mothers who stay home decreases as their educational attainments increase for whilst the proportion of unmarried mothers who stay home remains low throughout given they are likely the sole breadwinner of the family in such scenarios


### Birth order
#### age_of_interest, child_siblings
```{r}
# how birth order varies with child_siblings
prepped_ivd |>
  summarise(mean_BO = mean(birth_order, na.rm = TRUE), .by = child_siblings) |>
  ggplot(aes(x = child_siblings, y = mean_BO)) +
  geom_point()
```
We note that the mean birth order generally increases as the number of siblings and age of interest increases

```{r}
# birth order with age
prepped_ivd |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  summarise(mean_BO = mean(birth_order, na.rm = TRUE), .by = age_of_interest) |>
  ggplot(aes(x = age_of_interest, y = mean_BO)) +
  geom_point()
```

```{r}
prepped_ivd |>
  
  # categorise age by integer values (so you don't have impossibly many ages) and mash sibligns together
  mutate(
    age_of_interest  = ceiling(age_of_interest)
  ) |>
  summarise(count = n(), .by = c(child_siblings, age_of_interest, birth_order)) |>
  ggplot() + 
  geom_density(aes(x = age_of_interest, colour = child_siblings)) +
  facet_wrap(vars(birth_order))

```

## Multivariate (interactions)
### (M) test_household_income
coverage by mothers and fathers education
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age)) |>
  
  # calculate proportions by mother and fathers education for each degree of coverage
  summarise(count = n(), .by = c(father_highest_education, mother_highest_education, covid_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(father_highest_education, mother_highest_education)) |>
  
  # plot the distribution of vaccine uptakes for each combination of mothers' and fathers' educations
  ggplot(aes(x = father_highest_education, y = proportion, colour = mother_highest_education)) +
  geom_point() + 
  geom_line(aes(group = mother_highest_education)) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "a plot of how each degree of uptake changes with the father's highest education, \n
    for each highest educational level of the mother"
  ) 

function_plot_save(last_plot(), "cov_age_mother_father_highest_education", "svg", "Output/05_multivariate_uptake_plots")



# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age)) |>
  
  # calculate proportions by mother and fathers education for each degree of inferage
  summarise(count = n(), .by = c(father_highest_education, mother_highest_education, influenza_coverage_age)) |>
  mutate(proportion = count/sum(count), .by = c(father_highest_education, mother_highest_education)) |>
  
  # plot the distribution of vaccine uptakes for each combination of mothers' and fathers' educations
  ggplot(aes(x = father_highest_education, y = proportion, colour = mother_highest_education)) +
  geom_point() + 
  geom_line(aes(group = mother_highest_education)) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "a plot of how each degree of uptake changes with the father's highest education, \n
    for each highest educational level of the mother"
  ) 

function_plot_save(last_plot(), "inf_age_mother_father_highest_education", "svg", "Output/05_multivariate_uptake_plots")
  
```

coverage by mothers and fathers education with income
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(father_highest_education, income, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(father_highest_education, income)) |>

  
  # plot
  ggplot(aes(x = income, y = proportion, colour = father_highest_education)) +
  geom_point() +
  geom_smooth(aes(group = father_highest_education), method = "lm") +
  facet_wrap(vars(covid_coverage_age))

```
coverage by number of parents and income
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(test_household_income) & !is.na(covid_coverage_age)) |>
           
  # stratify income levels to compress the levels
  mutate(income = ceiling(test_household_income / 5)) |>  
  
  # summarise proportions for each level of income by the number of parents the child has
  summarise(count = n(), .by = c(test_household_income, child_parents, covid_coverage_age)) |>
  mutate(proportions = count / sum(count), .by = c(test_household_income, child_parents)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportions, colour = covid_coverage_age)) +
  geom_point() +
  #geom_smooth(method = "lm") +
  facet_wrap(vars(child_parents)) +
  labs(
    title = "covid coverage with household income, stratified by household with 1 or 2 parents"
  )
  
  # save the plot
  function_plot_save(last_plot(), "income_child_parents_covid_age", "svg", "Output/05_multivariate_uptake_plots")

#influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(test_household_income) & !is.na(influenza_coverage_age)) |>
           
  # stratify income levels to compress the levels
  mutate(income = ceiling(test_household_income / 5)) |>  
  
  # summarise proportions for each level of income by the number of parents the child has
  summarise(count = n(), .by = c(test_household_income, child_parents, influenza_coverage_age)) |>
  mutate(proportions = count / sum(count), .by = c(test_household_income, child_parents)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportions, colour = influenza_coverage_age)) +
  geom_point() +
  #geom_smooth(method = "lm") +
  facet_wrap(vars(child_parents)) +
  labs(
    title = "influenza coverage with household income, stratified by household with 1 or 2 parents"
  )
  
  # save the plot
  function_plot_save(last_plot(), "income_child_parents_influenza_age", "svg", "Output/05_multivariate_uptake_plots")
            
```

    
coverage by father, mother and parents highest education and income
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  pivot_longer(cols = c(father_highest_education, mother_highest_education, parents_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parent))
    
  function_plot_save(plot = last_plot(), "income_father_mother_education_covid_age", "svg", "Output/05_multivariate_uptake_plots")

    
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  pivot_longer(cols = c(father_highest_education, parents_highest_education, mother_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(parent))

  function_plot_save(plot = last_plot(), "income_father_mother_education_influenza_age", "svg", "Output/05_multivariate_uptake_plots")

```


Stratifying by both the mother and father's highest education levels, we realise that as income is held constant, the difference in uptake of both the covid and influenza vaccines is constnat. __EXCEPT__ for postgraduate mothers who seem to have more of an effect on influenza uptake

looking at each cimbinatiins of parents education


### Revisit (R) father mother education stratified by each other
Now let's look at income for each combination of mother's and fathers
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(covid_coverage_age) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  #pivot_longer(cols = c(father_highest_education, mother_highest_education, parents_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(mother_highest_education, father_highest_education, income, covid_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(mother_highest_education, father_highest_education, income)
  ) -> mother_highest_father_highest_education_covid_age
  #filter(mother_highest_education == "Junior High or High school", father_highest_education == "Junior High or High school")
 
# plot
mother_highest_father_highest_education_covid_age |>
  
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = covid_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(mother_highest_education), rows = vars(father_highest_education))

# lay out the data
mother_highest_father_highest_education_covid_age |>
  arrange(mother_highest_education, father_highest_education, covid_coverage_age, income)

# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(mother_highest_education) & !is.na(father_highest_education) & !is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
    
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)
         ) |>
  
  # stratify counts by income levels and education
  summarise(
    count = n(),
    .by = c(mother_highest_education, father_highest_education, income, influenza_coverage_age)
  ) |>
  
  mutate(
    proportion = count / sum(count),
    .by = c(mother_highest_education, father_highest_education, income)
  ) -> mother_highest_father_highest_education_influenza_age
  #filter(mother_highest_education == "Junior High or High school", father_highest_education == "Junior High or High school")
 
# plot
mother_highest_father_highest_education_influenza_age |>
  
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(group = influenza_coverage_age), method = "lm") +
  ylim(0, 1) +
  #labs(
  #  title = "covid coverage with diferring annual household \n
  #income levels, stratified by their mother and father's education",
  #  caption = "income rounded to closest 4 million JPY / year"
  #) +
  facet_grid(cols = vars(mother_highest_education), rows = vars(father_highest_education))

# lay out the data
mother_highest_father_highest_education_influenza_age |>
  arrange(mother_highest_education, father_highest_education, influenza_coverage_age, income)
```


Now let's try seperating married fathers & mothers and single parents
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(test_household_income)) |>

# trying all unmarried parents
mutate(
  single_parent_highest_education = case_when(
    test_parents_marital_status == 1 & parent_1_sex == 1 ~ mother_highest_education,
    test_parents_marital_status == 1 & parent_1_sex == 0 ~father_highest_education,
    .default =  NA
  )
) |>

  # pivot to include values for both mother's and father's education
  pivot_longer(
    cols = c(father_highest_education, mother_highest_education, single_parent_highest_education),
    values_to = "education",
    names_to = "parent"
  ) |>
  
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # remove NA values for education
  filter(!is.na(education)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  ylim(0,1) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parent))
```

Now let's try married parents vs single mothers only
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(test_household_income)) |>
  
  # seperate out single mothers from mother's highest education 
  mutate(
    single_mother_highest_education = case_when(
      
    # for any response that indicates unmarried and where the responding parent is female
    test_parents_marital_status == 1 & parent_1_sex == 1 ~ mother_highest_education,
    .default = NA
    )
 ) |>

  # pivot to include values for both mother's and father's education
  pivot_longer(
    cols = c(father_highest_education, mother_highest_education, single_mother_highest_education),
    values_to = "education",
    names_to = "parent"
  ) |>
  
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # remove NA values for education
  filter(!is.na(education)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  ylim(0,1) +
  facet_grid(cols = vars(covid_coverage_age), rows = vars(parent))

  # save the plot
  function_plot_save(plot = last_plot(), "income_marital_father_mother_education_covid_age", "svg", "Output/05_multivariate_uptake_plots")


# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(test_household_income)) |>
  
  # seperate out single mothers from mother's highest education 
  mutate(
    single_mother_highest_education = case_when(
      
    # for any response that indicates unmarried and where the responding parent is female
    test_parents_marital_status == 1 & parent_1_sex == 1 ~ mother_highest_education,
    .default = NA
    )
 ) |>

  # pivot to include values for both mother's and father's education
  pivot_longer(
    cols = c(father_highest_education, mother_highest_education, single_mother_highest_education),
    values_to = "education",
    names_to = "parent"
  ) |>
  
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 4)) |>
  
  # stratify counts by income levels and education
  summarise(count = n(), .by = c(education, income, parent, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(education, income, parent)) |>
  
  # remove NA values for education
  filter(!is.na(education)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = education)) +
  geom_point() +
  geom_smooth(aes(group = education), method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by their mother and father's education",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  ylim(0,1) +
  facet_grid(cols = vars(influenza_coverage_age), rows = vars(parent)) 

  # save the plot
  function_plot_save(plot = last_plot(), "income_marital_father_mother_education_influenza_age", "svg", "Output/05_multivariate_uptake_plots")
```
I'm pretty sure there's some sort of interaction between education and household income in affecting the uptake of influenza because the slopes change

Now, let's examine how uptake differs between families where mothers stay home and don't, holding income level constant
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
    
  # pivot to include values for both mother's and father's education
  # pivot_longer(cols = c(father_highest_education, mother_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, test_household_income, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by families with a stay-home mom"#,
    #caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home))
    
  function_plot_save(plot = last_plot(), "test_household_income_mother_stay_home_covid_age", "svg", "Output/05_multivariate_uptake_plots")

  
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, test_household_income, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_household_income, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = test_household_income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by families with a stay-home mom"#,
   # caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home))
    
  function_plot_save(plot = last_plot(), "test_household_income_mother_stay_home_influenza_age", "svg", "Output/05_multivariate_uptake_plots")

```
Now let's investigate the uptake and how it varies with test_household_income, marital_status and mother's employment
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
    
  # pivot to include values for mom's employment
  # pivot_longer(cols = c(father_highest_education, mother_highest_education), values_to = "education", names_to = "parent") |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, mother_employment_status, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, mother_employment_status, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by mother employment status against stay-home"#,
    #caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(mother_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_employment_covid_age", "svg", "Output/05_multivariate_uptake_plots")

  
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, mother_employment_status, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, mother_stay_home, mother_employment_status)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by mother employment status against stay-home"#,
   # caption = "income rounded to closest 4 million JPY / year"
  ) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(mother_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_employment_influenza_age", "svg", "Output/05_multivariate_uptake_plots")

```

Let's investigate how vaccine uptake varies with test_household_income, mother_employment_status and father's employment ab
```{r}
# covid coverage by age
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, father_employment_status, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, father_employment_status, mother_stay_home)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "covid coverage with diferring annual household \n
  income levels, stratified by mother stay-home against father_stay_home",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(father_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_father_employment_covid_age", "svg", "Output/05_multivariate_uptake_plots")

  
# influenza coverage by age
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age) & !is.na(mother_stay_home) & !is.na(test_household_income)) |>
  
  # stratify income levels to compress them
  mutate(income = ceiling(test_household_income / 5)) |>
  
  # stratify counts by test_household_income and mothers staying home
  summarise(count = n(), .by = c(mother_stay_home, income, father_employment_status, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(income, mother_stay_home, father_employment_status)) |>
  
  # plot
  ggplot(aes(x = income, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  labs(
    title = "influenza coverage with diferring annual household \n
  income levels, stratified by mother stay-home against father_employment",
    caption = "income rounded to closest 4 million JPY / year"
  ) +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(mother_stay_home), rows = vars(father_employment_status))
    
  function_plot_save(plot = last_plot(), "income_mother_stay_home_father_employment_influenza_age", "svg", "Output/05_multivariate_uptake_plots")

```

### (M) age_of_interest

#### birth_order
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    birth_order = ifelse(
      birth_order <= 3,
      as.character(birth_order),
      "4+"
    ),
    
    # round age
    age_of_interest = ceiling(age_of_interest)
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, birth_order, covid_coverage_age) |>
  arrange(birth_order, age_of_interest, covid_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = case_when(
      age_of_interest %in% 1:5 ~ "pre",
      age_of_interest %in% 6:12 ~ "pri",
      age_of_interest > 12 ~ "high"
    )
  ) |>
  #arrange(birth_order, age_of_interest, covid_coverage_age)
  
  #filter(age_cat == "pre", covid_coverage_age == 2) |>
  #mutate(weight = count / sum(count), .by = c(birth_order))
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, birth_order, covid_coverage_age)
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(birth_order)) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \ncoverage by the covid vaccine, stratified by different age groups",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and birth order",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_birth_order_covid_age

age_birth_order_covid_age

# save plots
function_plot_save(plot = last_plot(), "age_birth_order_covid_age", "svg", "Output/05_multivariate_uptake_plots")

  

# influenza coverage
inf_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    birth_order = ifelse(
      birth_order <= 3,
      as.character(birth_order),
      "4+"
    ),
    
    # round age
    age_of_interest = ceiling(age_of_interest)
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, birth_order, influenza_coverage_age) |>
  arrange(birth_order, age_of_interest, influenza_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = case_when(
      age_of_interest %in% 1:5 ~ "pre",
      age_of_interest %in% 6:12 ~ "pri",
      age_of_interest > 12 ~ "high"
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, birth_order, influenza_coverage_age)
  ) -> data_age_birth_order_influenza_age

data_age_birth_order_influenza_age |>
  # plot graphs of influenza coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(birth_order)) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \ncoverage by the influenza vaccine, stratified by different age groups",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and birth order",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_birth_order_influenza_age

age_birth_order_influenza_age

# save plots
function_plot_save(age_birth_order_influenza_age, "age_birth_order_influenza_age", "svg", "Output/05_multivariate_uptake_plots")


```

#### child_siblings
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    child_siblings = ifelse(
      child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, child_siblings, covid_coverage_age) |>
  arrange(child_siblings, age_of_interest, covid_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) -> cov_prepped_ivd_transformed_age_siblings_age_cat
  
cov_prepped_ivd_transformed_age_siblings_age_cat |>

  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, child_siblings, covid_coverage_age)
  ) -> data_age_child_siblings_covid_age_cat2

data_age_child_siblings_covid_age_cat2 |>
  
  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the covid vaccine changes with age, stratified by the number of siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_child_siblings_covid_age_cat2

age_child_siblings_covid_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_child_siblings_covid_age_cat2", "svg", "Output/05_multivariate_uptake_plots")

# running an ancova to determine if they're any differences between uptakes for different ages across age groups and the number of siblings
cov_prepped_ivd_transformed_age_siblings_age_cat |>

  # filter the data to only include cases of full vaccination
  filter(covid_coverage_age == 2) -> cov_prepped_ivd_transformed_age_siblings_age_cat_full_uptake

  # testing for independence of covariates
  aov(age_of_interest ~ age_cat + child_siblings, data = cov_prepped_ivd_transformed_age_siblings_age_cat_full_uptake) |>
  summary()

  # testing for homogeneity in variance
  leveneTest(age_of_interest ~ age_cat * child_siblings, data = cov_prepped_ivd_transformed_age_siblings_age_cat_full_uptake)
  # age_cat and age of interest aren't independent which makes sense but child_sibligns is independent of age_of_interest
  
# fitting the ancova
data_age_child_siblings_covid_age_cat2 |>
  
  # filter the data to only contain cases with full uptake
  filter(covid_coverage_age == 2) |>
  

  (\(.x) {
    
  # to store ancovas
  ancovas_age_cat <- list()
      
  # plot the ancova for each age 
  for(i in c("pre", "primary", "highsch")) {
    filter(.x, age_cat == i) |>
        
      aov(
        proportion ~ age_of_interest + child_siblings + child_siblings * age_of_interest,
        data = _
      ) |>
      
      Anova(type = "III") -> ancova_result
      
      ancovas_age_cat[[i]] <- ancova_result
  }
    
  return(ancovas_age_cat)
  }) ()

  
  
# influenza coverage
inf_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    child_siblings = ifelse(
      child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, child_siblings, influenza_coverage_age) |>
  arrange(child_siblings, age_of_interest, influenza_coverage_age) |>
  
   mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, child_siblings, influenza_coverage_age)
  ) |>

  # plot graphs of influenza coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the influenza vaccine, changes with age, stratified by the number of siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_child_siblings_influenza_age_cat2

age_child_siblings_influenza_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_child_siblings_influenza_age_cat2", "svg", "Output/05_multivariate_uptake_plots")
```

#### test_child_siblings
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    test_child_siblings = ifelse(
      test_child_siblings <= 2,
      as.character(test_child_siblings),
      "3+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, test_child_siblings, covid_coverage_age) |>
  arrange(test_child_siblings, age_of_interest, covid_coverage_age) |>
  
  mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, test_child_siblings, covid_coverage_age)
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(test_child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the covid vaccine changes with age, stratified by the number of test_siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and test_siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_test_child_siblings_covid_age_cat2

age_test_child_siblings_covid_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_test_child_siblings_covid_age_cat2", "svg", "Output/05_multivariate_uptake_plots")

  

# influenza coverage
inf_prepped_ivd |>
  
  mutate(
    
    # compress higher birth order
    test_child_siblings = ifelse(
      test_child_siblings <= 2,
      as.character(test_child_siblings),
      "3+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>

  function_data_triple_stratify(age_of_interest, as.numeric, test_child_siblings, influenza_coverage_age) |>
  arrange(test_child_siblings, age_of_interest, influenza_coverage_age) |>
  
   mutate(
    
    # make age categories so that you can stratify by different ages: preprimary, primary, secondary
    age_cat = factor(
      case_when(
      age_of_interest %in% seq(0, 5, by = 0.5) ~ "pre",
      age_of_interest %in% seq(5.5, 12, by = 0.5) ~ "primary",
      age_of_interest %in% seq(12.5, 18, by = 0.5) ~ "highsch"
      )
    )
  ) |>
  
  mutate(
    
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, test_child_siblings, influenza_coverage_age)
  ) |>

  # plot graphs of influenza coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(test_child_siblings)) +
  labs(
    title = "how the proportion of children in different age categores with each degree of 
    \ncoverage by the influenza vaccine, changes with age, stratified by the number of test_siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and test_siblings",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> age_test_child_siblings_influenza_age_cat2

age_test_child_siblings_influenza_age_cat2

# save plots
function_plot_save(plot = last_plot(), "age_test_child_siblings_influenza_age_cat2", "svg", "Output/05_multivariate_uptake_plots")
```
Let's stratify by child sibling and test_child_siblings
```{r}
# covid_uptake
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      test_child_siblings <= 2,
     as.character(test_child_siblings),
      "3+"
    ),
    
    child_siblings = ifelse(
     child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, test_child_siblings, child_siblings, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, test_child_siblings, child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(aes(fill = covid_coverage_age), method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(child_siblings), rows = vars(test_child_siblings)) +
  labs(
    title = "Plot of how the uptake of different coverages of the covid vaccine changes with age",
    subtitle = "stratified by child_siblings with columns and test_child_siblings by rows" 
  ) 

# influenza uptake
inf_prepped_ivd |>
  filter(!is.na(influenza_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      test_child_siblings <= 2,
     as.character(test_child_siblings),
      "3+"
    ),
    
    child_siblings = ifelse(
     child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, test_child_siblings, child_siblings, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, test_child_siblings, child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point() +
  geom_smooth(aes(fill = influenza_coverage_age), method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(child_siblings), rows = vars(test_child_siblings)) +
  labs(
    title = "Plot of how the uptake of different coverages of the influenza vaccine changes with age",
    subtitle = "stratified by child_siblings with columns and test_child_siblings by rows" 
  ) 
```



#### age_cat

Testng age categories and how they interact with ages
```{r}
# covid_uptake
cov_prepped_ivd |>
  
  filter(!is.na(covid_coverage_age)) |>
  
  mutate(
    
    # compress higher birth order
    child_siblings = ifelse(
      child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>
  
  summarise(count = n(), .by = c(age_of_interest, covid_coverage_age, child_siblings, age_cat)) |>
  mutate(proportion = count / sum (count), .by = c(age_of_interest, child_siblings, age_cat)) |>
  arrange(child_siblings, age_of_interest, covid_coverage_age) |>
  
  mutate(
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, child_siblings, covid_coverage_age)
    
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \n coverage by the covid vaccine, stratified by different age groups and the number of siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and birth order",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))

# influenza
inf_prepped_ivd |>
  
  filter(!is.na(influenza_coverage_age)) |>
  
  mutate(
    
    # compress higher birth order
    child_siblings = ifelse(
      child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    ),
    
    # segment age into increments of 0.5 years
    age_of_interest = round(age_of_interest * 2) / 2
  ) |>
  
  summarise(count = n(), .by = c(age_of_interest, influenza_coverage_age, child_siblings, age_cat)) |>
  mutate(proportion = count / sum (count), .by = c(age_of_interest, child_siblings, age_cat)) |>
  arrange(child_siblings, age_of_interest, influenza_coverage_age) |>
  
  mutate(
    # weight observations within each age_category, such that the trend for the proportion that have received each coverage is reflective of the sample size
    weights = count / sum(count), .by = c(age_cat, child_siblings, influenza_coverage_age)
    
  ) |>

  # plot graphs of covid coverage by age across different birth orders
  ggplot(aes(x = age_of_interest, y = proportion, colour = influenza_coverage_age)) +
  geom_point(aes(shape = age_cat)) +
  geom_smooth(aes(linetype = age_cat, weight = weights), method = "lm", se = FALSE) +
  facet_wrap(vars(child_siblings)) +
  labs(
    title = "proportions of children in different age categores with each degree of 
    \n coverage by the influenza vaccine, stratified by different age groups and the number of siblings they have",
    subtitle = "trend lines weighted by the sample size within each age category, coverage status and birth order",
    x = "age",
    y = "proportion"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))
```



Looking at uptake by age of interest stratified by birth order and child_siblings
where child siblings refers only to children < 18
```{r}
# covid_uptake
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      birth_order <= 2,
     as.character(birth_order),
      "3+"
    ),
    
    child_siblings = ifelse(
     child_siblings <= 2,
      as.character(child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, birth_order, child_siblings, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, birth_order, child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(child_siblings), rows = vars(birth_order)) +
  labs(
    title = "Plot of how the uptake of different coverages of the covid vaccine changes with age",
    subtitle = "stratified by child_siblings with columns and birth_order by rows" 
  ) 
```

Looking at uptkae by age of interest stratified by birth order and test_child_siblings
```{r}
# covid_uptake
cov_prepped_ivd |>
  filter(!is.na(covid_coverage_age)) |>
  mutate(age_of_interest = ceiling(age_of_interest)) |>
  
  # compress the categories of birth order and siblings
    mutate(
    birth_order = ifelse(
      birth_order <= 2,
     as.character(birth_order),
      "3+"
    ),
    
    test_child_siblings = ifelse(
     test_child_siblings <= 2,
      as.character(test_child_siblings),
      "3+"
    )
  ) |>
  
  # summarise by age and number of siblings
  summarise(count = n(), .by = c(age_of_interest, birth_order, test_child_siblings, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(age_of_interest, birth_order, test_child_siblings)) |>
  
  # plot and facet by birth order
  ggplot(aes(x = age_of_interest, y = proportion, colour = covid_coverage_age)) +
  geom_point() +
  geom_smooth(method = "lm") +
  lims(y = c(0, 1)) +
  facet_grid(cols = vars(test_child_siblings), rows = vars(birth_order)) +
  labs(
    title = "Plot of how the uptake of different coverages of the covid vaccine changes with age",
    subtitle = "stratified by test_child_siblings with columns and birth_order by rows" 
  ) 
```


### (M) test_parents_marital_status
#### child_parents
Testing how test_parents_marital_status interacts with a child's parents

general breakdown:
```{r}
cov_prepped_ivd |>
  summarise(n(), .by = c(test_parents_marital_status, child_parents))
```

stratified plots
```{r}
# covid plot
cov_prepped_ivd |>
  
  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(covid_coverage_age)) |>
  summarise(count = n(), .by = c(test_parents_marital_status, child_parents, covid_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_parents_marital_status, child_parents)) |>
  
  # plot
  ggplot(aes(x = child_parents, y = proportion)) +
  geom_point(aes(colour = test_parents_marital_status)) +
  geom_smooth(method = "lm", aes(colour = test_parents_marital_status)) +
  function_plot_label_count(child_parents, test_parents_marital_status) +
  facet_wrap(vars(covid_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the covid vaccine \n 
    according to their parents marital status and the number of parents they have"
  ) +
  theme(plot.title = element_text(lineheight = 0.5))  -> child_parents_marital_status_covid_age

  # save the plot for reference
  function_plot_save(last_plot(), "child_parents_marital_status_covid_age", ".png", "Output/05_multivariate_uptake_plots")

# influenza plot
inf_prepped_ivd |>
  
  # ensure no missing covid vax data and stratify by marital status and parents
  filter(!is.na(influenza_coverage_age)) |>
  summarise(count = n(), .by = c(test_parents_marital_status, child_parents, influenza_coverage_age)) |>
  mutate(proportion = count / sum(count), .by = c(test_parents_marital_status, child_parents)) |>
  
  # plot
  ggplot(aes(x = child_parents, y = proportion)) +
  geom_point(aes(colour = test_parents_marital_status)) +
  geom_smooth(method = "lm", aes(colour = test_parents_marital_status)) +
  function_plot_label_count(child_parents, test_parents_marital_status) +
  facet_wrap(vars(influenza_coverage_age)) +
  labs(
    title = "proportion of children with each uptake of the influenza vaccine \n 
    according to their parents marital status and the number of parents they have"
  ) +
  theme(plot.title = element_text(lineheight = 0.5)) -> child_parents_marital_status_influenza_age

  # save the plot for reference
  function_plot_save(last_plot(), "child_parents_marital_status_influenza_age", ".png", "Output/05_multivariate_uptake_plots")
```