---
title: "05_investigating interdependence"
format: html
execute: 
  eval: true
  echo: false
---

Libraries
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)
library(patchwork)

# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

Data
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )

# transformed age data
age <- 
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_age_data.RDS"
    )
  )

# Creating data frames for bivariate and multivariate analysis
# influenza and independent variable data
inf_ivd <- bind_cols(inf, ivd)

# covid and independent variable data
cov_ivd <- bind_cols(cov, ivd)
```
This document will be used to analyse the interdependencies between variables we have processed thusfar,
to help us determine the sort of relationships that exist between them, and aid us in choosing a model to use.

## Section 1 - collinearity between independent (explanatory) variables
### Numerical variables
Check if any of the continuous numerical variables are collinear

```{r}
# extract all numerical variables (including test_household income)
ivd |>
  filter(child_of_interest == 1) |>
  
  # make test_household_income numeric
  mutate(test_household_income = as.numeric(test_household_income)) |>
  
  # transform test_household_income such that each value represents the number of JPY in millions
  mutate(
    test_household_income = case_when(
      test_household_income == 1 ~ 0,
      test_household_income %in% 2:3 ~ 1,
      test_household_income >= 4 ~ test_household_income - 2
    )
  ) |>
  
  select(!where(is.factor) & !starts_with("respondent_") & !starts_with("perception")) |>
  filter(!is.na(test_household_income)) |>

  # calculate correlation matrix for cases with a COI
  cor() |>
  
  # plot the correlation plot
  ggcorrplot(method = "square", lab = TRUE, lab_size = 3)
```
The variables that display the most collinearity are:
household total
1. child siblings
2. child_borthers
3. child_sisters
4. child_grand

Furthermore, child_siblngs is associated withthe number of brothers and the number of sisters

### Categorical variables
Check if there's **covariance** between categorical variables

**you cAN look at this type of graph for variables you suspect may be highly correlated**
```{r}
# prepare data frame to be passed into recursive function
ivd$age_of_interest <- age$age_of_interest
prepped_ivd <- ivd |>
  filter(child_of_interest != 0)

# read dependencies
causal_relationship_combinations <-
  readRDS(here("Output", "causal_relationship_combinations.RDS")) |>
  rename(variable1 = name, variable2 = to) |>

  # dropping rows with COI's_familial_factors and "vaccine_uptake" for now
  filter(!if_any(everything(), ~ .x %in% c("vaccine uptake", "COI's familial factors")))
  
# plot every pair 
# input the list of factor_pairs, the function, and pass the dataframe ivd to the df argument of our custom fn
list_of_plots <- pmap(causal_relationship_combinations, function_plot_corr_pairs, df = prepped_ivd)
```

save the categorical plots

```{r}
saveRDS(list_of_plots, here("Output", "causal_relationship_plots.RDS"))
```