---
title: "05_investigating interdependence"
format: html
execute: 
  eval: true
  echo: false
---

Libraries
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)

# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

Data
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )


# Creating data frames for bivariate and multivariate analysis
# influenza and independent variable data
inf_ivd <- bind_cols(inf, ivd)

# covid and independent variable data
cov_ivd <- bind_cols(cov, ivd)
```
This document will be used to analyse the interdependencies between variables we have processed thusfar,
to help us determine the sort of relationships that exist between them, and aid us in choosing a model to use.

## Section 1 - collinearity between independent (explanatory) variables
Check if any of the continuous numerical variables are collinear

```{r}
# extract all numerical variables
ivd |>
  filter(child_of_interest == 1) |>
  select(!where(is.factor) & !starts_with("respondent_") & !starts_with("perception")) |>
  
  # calculate correlation matrix for cases with a COI
  cor() |>
  
  # plot the correlation plot
  ggcorrplot(method = "square", lab = TRUE, lab_size = 3)
```
The variables that display the most collinearity are:
household total
1. child siblings
2. child_borthers
3. child_sisters
4. child_grand

Furthermore, child_siblngs is associated withthe number of brothers and the number of sisters
