05_investigating_interdependence_regresssions for test_mother_highest_test_father_highest_education_

This document serves to run a script which will run a mini regression,
to compare how different highest educational attainments of the COI's mothers and 
fathers affects their uptake of the covid and influenza vaccine differently, when 
factors such as household_income are varied

## Libraraies
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)
library(patchwork)
library(car)

# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

## Data
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )

# transformed age data
age <- 
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_age_data.RDS"
    )
  )

# Creating data frames for bivariate and multivariate analysis
# limit indep data to only those households with a COI
prepped_ivd <- ivd |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1)

# influenza and independent variable data
inf_prepped_ivd <- bind_cols(inf, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1 & !is.na(influenza_coverage_age)) 

# covid and independent variable data
cov_prepped_ivd <- bind_cols(cov, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1 & !is.na(covid_coverage_age))

# create dummy variables for both influenza and covid uptake response variables
inf_prepped_ivd |>
  model.matrix(~ influenza_coverage_age + 0, data = _) |>
  as.data.frame() -> inf_ivd_dummy_vars

cov_prepped_ivd |>
  model.matrix(~ covid_coverage_age + 0, data = _) |>
  as.data.frame() -> cov_ivd_dummy_vars


# create sets of data with dummy response variables for multinomial regresion fitting
# influenza
dummy_inf_prepped_ivd <-
  cbind(inf_ivd_dummy_vars, inf_prepped_ivd) |>
  select(-influenza_coverage_age)

# covid
dummy_cov_prepped_ivd <-
  cbind(cov_ivd_dummy_vars, cov_prepped_ivd) |>
  select(-covid_coverage_age)

```

## parents_highest_education with income
Let's test how uptake varies with parent's highest education
```{r}
# influenza 
dummy_inf_prepped_ivd |>
  
  # ensure only children with households of non NA income statuses are investigated
  filter(!is.na(test_household_income)) |>
  
  # ensure only children where both parents' education statuses are available are investigated
  filter(!is.na(parents_highest_education)) -> dummy_inf_parents_highest_education_test_household_income

# create dummy variables for each level of the parents' educations so we can examine ONLY the interaction of postgrad education with income
dummy_inf_parents_highest_education_test_household_income |>
  
  model.matrix(~ parents_highest_education + 0, data = _) -> 
  inf_dummy_parents_highest_education_test_household_income


# append the dummy variables for parents' educations on to our current dataframe
dummy_inf_dummy_parents_highest_education_test_household_income <- 
  cbind(inf_dummy_parents_highest_education_test_household_income, dummy_inf_parents_highest_education_test_household_income)

# create a vector that contains each level of the dummy variable
  inf_dummy <- dummy_inf_parents_highest_education_test_household_income |>
    select(starts_with("influenza_coverage_age"))
  
# run different linear models for each level of influenza 
  # no interaction
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + parents_highest_education, 
      data = dummy_inf_dummy_parents_highest_education_test_household_income
    )
  )
  
  # interaction between mother's education and income and father's education and income
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + parents_highest_education +
        parents_highest_education * test_household_income + parents_highest_education * test_household_income, 
      data = dummy_inf_dummy_parents_highest_education_test_household_income
    )
  )
  
  # interaction between mother's and father's highest education and income
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + `parents_highest_educationJunior High or High school` + `parents_highest_educationJunior/Technical College` + parents_highest_educationPostgrad + parents_highest_educationTertiary +
        parents_highest_educationPostgrad * test_household_income + `parents_highest_educationJunior/Technical College` * test_household_income + parents_highest_educationTertiary * test_household_income + `parents_highest_educationJunior High or High school` * test_household_income , 
      data = dummy_inf_dummy_parents_highest_education_test_household_income
    )
  )
  
  # interaction between mother and father's education
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + test_mother_highest_education + test_father_highest_education +
        test_father_highest_education * test_mother_highest_education, 
      data = dummy_inf_dummy_mother_father_highest_education_test_household_income
    )
  )
```


## test_mother_highest_test_father_highest_education_ with income
### LPM
First let's test probability of each vaccination status with respect the the COI's
mother's and father's highest educational attainment
```{r}
# influenza 
dummy_inf_prepped_ivd |>
  
  # ensure only children with households of non NA income statuses are investigated
  filter(!is.na(test_household_income)) |>
  
  # ensure only children where both parents' education statuses are available are investigated
  filter(!is.na(test_mother_highest_education) & !is.na(test_father_highest_education)) -> dummy_inf_mother_father_highest_education_test_household_income

# create dummy variables for each level of the parents' educations so we can examine ONLY the interaction of postgrad education with income
dummy_inf_mother_father_highest_education_test_household_income |>
  
  model.matrix(~ test_father_highest_education + test_mother_highest_education + 0, data = _) -> 
  inf_dummy_mother_father_highest_education_test_household_income


# append the dummy variables for parents' educations on to our current dataframe
dummy_inf_dummy_mother_father_highest_education_test_household_income <- 
  cbind(inf_dummy_mother_father_highest_education_test_household_income, dummy_inf_mother_father_highest_education_test_household_income)

# create a vector that contains each level of the dummy variable
  inf_dummy <- dummy_inf_mother_father_highest_education_test_household_income |>
    select(starts_with("influenza_coverage_age"))
  
# run different linear models for each level of influenza 
  # no interaction
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + test_mother_highest_education + test_father_highest_education, 
      data = dummy_inf_dummy_mother_father_highest_education_test_household_income
    )
  )
  
  # interaction between mother's education and income and father's education and income
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + test_mother_highest_education + test_father_highest_education +
        test_father_highest_education * test_household_income + test_mother_highest_education * test_household_income, 
      data = dummy_inf_dummy_mother_father_highest_education_test_household_income
    )
  )
  
  # interaction between mother's and father's highest education (postgrad) and income
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + `test_mother_highest_educationVocational Sch` + `test_mother_highest_educationJunior College` + test_mother_highest_educationTertiary + test_mother_highest_educationPostgrad + `test_father_highest_educationVocational Sch` + `test_father_highest_educationTechnical College` + test_father_highest_educationTertiary + test_father_highest_educationPostgrad +
        test_father_highest_educationPostgrad * test_household_income + test_mother_highest_educationPostgrad * test_household_income, 
      data = dummy_inf_dummy_mother_father_highest_education_income
    )
  )
  
  # interaction between mother and father's education
  map(
    inf_dummy,
    function(x) lm(
      x ~ test_household_income + test_mother_highest_education + test_father_highest_education +
        test_father_highest_education * test_mother_highest_education, 
      data = dummy_inf_dummy_mother_father_highest_education_test_household_income
    )
  )
```


### Logit model
Next, we'll run a logistc regression by treating the different income categories (subdividing them into bins of 4 million JPY each) as categorical variables

Interactions between both parent's educations and income was excluded because it was just a bad fit
```{r}
# influenza 
dummy_inf_prepped_ivd |>
  
  # ensure only children with households of non NA income statuses are investigated
  filter(!is.na(test_household_income)) |>
  
  # ensure only children where both parents' education statuses are available are investigated
  filter(!is.na(test_mother_highest_education) & !is.na(test_father_highest_education)) |>
  
  # categorise income
  mutate(income = ceiling(test_household_income / 4) |> as.factor()) -> dummy_inf_mother_father_highest_education_income

  
# create dummy variables for each level of the parents' educations so we can examine ONLY the interaction of postgrad education with income
dummy_inf_mother_father_highest_education_income |>
  
  model.matrix(~ test_father_highest_education + test_mother_highest_education + 0, data = _) -> 
  inf_dummy_mother_father_highest_education_income


# append the dummy variables for parents' educations on to our current dataframe
dummy_inf_dummy_mother_father_highest_education_income <- 
  cbind(inf_dummy_mother_father_highest_education_income, dummy_inf_mother_father_highest_education_income)


# create a vector that contains each level of the dummy variable for influenza which we can loop through as our dependent variable
  inf_dummy <- dummy_inf_mother_father_highest_education_income |>
    select(starts_with("influenza_coverage_age"))
    

# run different logistic regression models for each level of influenza coverage
  
  # no interaction
  map(
    inf_dummy,
    function(x) glm(
      x ~ income + test_mother_highest_education + test_father_highest_education, 
      family = "binomial",
      data = dummy_inf_dummy_mother_father_highest_education_income
    )
  )
  
  # interaction between mother's education and income and father's education (postgrad) and income
  map(
    inf_dummy,
    function(x) glm(
      x ~ income + test_mother_highest_education + test_father_highest_education +
        test_father_highest_educationPostgrad * income + test_mother_highest_educationPostgrad * income, 
      family = "binomial",
      data = dummy_inf_dummy_mother_father_highest_education_income
    )
  )
  
  # interaction between mother's education and income and father's education (postgrad) and income (DIFF FORMATTING)
  map(
    inf_dummy,
    function(x) glm(
      x ~ test_household_income + `test_mother_highest_educationVocational Sch` + `test_mother_highest_educationJunior College` + test_mother_highest_educationTertiary + test_mother_highest_educationPostgrad + `test_father_highest_educationVocational Sch` + `test_father_highest_educationTechnical College` + test_father_highest_educationTertiary + test_father_highest_educationPostgrad +
        test_father_highest_educationPostgrad * test_household_income + test_mother_highest_educationPostgrad * test_household_income, 
      family = "binomial",
      data = dummy_inf_dummy_mother_father_highest_education_income
    )
  )
  
  # interaction between mother and father's education
  map(
    inf_dummy,
    function(x) glm(
      x ~ income + test_mother_highest_education + test_father_highest_education, 
      family = "binomial",
      data = dummy_inf_dummy_mother_father_highest_education_income
    )
  )
```
