---
format: 
  html:
    fig-asp: 0.8
execute: 
  eval: true
  echo: false
  warning: false
---

Libraries
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)
library(patchwork)
library(car)

# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

Data
```{r}
# transformed independent variable data
ivd <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_independent_variable_data.RDS"
      )
    )

# transformed covid data
cov <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_covid_data.RDS"
    )
  )

# transformed influenza data
inf <-
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_influenza_data.RDS"
    )
  )

# transformed age data
age <- 
  readRDS(
    here(
      "Data",
      "JACSIS2023", 
      "processed", 
      "transformed_age_data.RDS"
    )
  )

# Creating data frames for bivariate and multivariate analysis
# limit indep data to only those households with a COI
prepped_ivd <- ivd |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1)

# influenza and independent variable data
inf_prepped_ivd <- bind_cols(inf, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1 & !is.na(influenza_coverage_age)) 

# covid and independent variable data
cov_prepped_ivd <- bind_cols(cov, ivd) |>
  mutate(age_of_interest = age$age_of_interest) |>
  filter(child_of_interest == 1 & !is.na(covid_coverage_age))

# create dummy variables for both influenza and covid uptake response variables
inf_prepped_ivd |>
  model.matrix(~ influenza_coverage_age + 0, data = _) |>
  as.data.frame() -> inf_ivd_dummy_vars

cov_prepped_ivd |>
  model.matrix(~ covid_coverage_age + 0, data = _) |>
  as.data.frame() -> cov_ivd_dummy_vars


# create sets of data with dummy response variables for multinomial regresion fitting
# influenza
dummy_inf_prepped_ivd <-
  cbind(inf_ivd_dummy_vars, inf_prepped_ivd) |>
  select(-influenza_coverage_age)

# covid
dummy_cov_prepped_ivd <-
  cbind(cov_ivd_dummy_vars, cov_prepped_ivd) |>
  select(-covid_coverage_age)
```

This document will serve as a space where we explore different techniques/strategies to fit (parts of) our regression model.

## Subsections of regression fitting
### Fiting a segmented model for age against age category
Age category here acts as the interaction term. However, I can't figure out if we need to make the intercept vary with age cat too.

We will be investigating 2 approaches:
