---
format: 
  html:
    fig-asp: 0.8
execute: 
  eval: true
  echo: false
  warning: false
---

Libraries
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)
library(patchwork)
library(car)
library(pscl)


# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

Data
```{r}
# read combined data
regression_data <- readRDS(
  here("Data", "JACSIS2023", "processed", "reshaped_combined_data.RDS")
  )
```

This document will serve as a space where we explore different techniques/strategies to fit (parts of) our regression model.

## Subsections of regression fitting
### Fiting a segmented model for age against age category
Age category here acts as the interaction term. However, I can't figure out if we need to make the intercept vary with age cat too.

To determine which approach we'll use, we will be fitting a model of the proportion of vaccine uptake statuses with age, age-category and number of siblings. To see which matches the models produced during our EDA phase better. Logistic regressions will be run, and their outcomes plotted for comparison

We will be investigating 2 approaches:
1. just adding an interaction term to current regression model packages such as glm 
2. using `segmented` to specify a regresion model?

### Approach 1 - exising regression model packages
```{r}
# Model for covid vaccination
  # Full coverage

    # full coverage without siblings
    model_1_covid_coverage_age_2 <- glm(
      covid_coverage_age_2 ~ age_of_interest + age_cat + age_cat*age_of_interest,
      family = "binomial",
      data = regression_data
    )
    
    # Assessing the fit
    pscl::pR2(model_1_covid_coverage_age_2)["McFadden"]
    
    # full coverage with siblings
    model_2_covid_coverage_age_2 <- glm(
      covid_coverage_age_2 ~ age_of_interest * age_cat * child_siblings,
      family = "binomial",
      data = regression_data
    ) 
    
    # Assessing the fit
    pscl::pR2(model_2_covid_coverage_age_2)["McFadden"]
    
    # full coverage with birth order
    model_3_covid_coverage_age_2 <- glm(
      covid_coverage_age_2 ~ age_of_interest * age_cat * birth_order,
      family = "binomial",
      data = regression_data
    )
    
    # Assessing the fit
    pscl::pR2(model_3_covid_coverage_age_2)["McFadden"]

  
  # No coverage
    # no coverage without siblings
    model_1_covid_coverage_age_0 <- glm(
      covid_coverage_age_0 ~ age_of_interest + age_cat + age_cat*age_of_interest,
      family = "binomial",
      data = regression_data
    ) 
  
    # Assessing the fit
    pscl::pR2(model_1_covid_coverage_age_0)["McFadden"]
  
    # no coverage with siblings
    model_2_covid_coverage_age_0 <- glm(
      covid_coverage_age_0 ~ age_of_interest * age_cat * child_siblings,
      family = "binomial",
      data = regression_data
    )
  
    # Assessing the fit
    pscl::pR2(model_2_covid_coverage_age_0)["McFadden"]
  
    # no coverage with birth order
    model_3_covid_coverage_age_0 <- glm(
      covid_coverage_age_0 ~ age_of_interest * age_cat * birth_order,
      family = "binomial",
      data = regression_data
    ) 
  
    # Assessing the fit
    pscl::pR2(model_3_covid_coverage_age_0)["McFadden"]


  
# Model for influenza vaccination
  # complete coverage
  model_influenza_coverage_age_2 <- glm(
      influenza_coverage_age_2 ~ age_of_interest + age_cat + age_cat*age_of_interest,
      family = "binomial",
      data = regression_data
    )

  # no coverage
  model_influenza_coverage_age_0 <- glm(
      influenza_coverage_age_0 ~ age_of_interest + age_cat + age_cat*age_of_interest,
      family = "binomial",
      data = regression_data
    )
```

### Approach 2 - using the `segmented` package
```{r}

```


