---
format: 
  html:
    fig-asp: 0.8
execute: 
  eval: true
  echo: false
  warning: false
---

Libraries
```{r}
#| echo: false
#| warning: false
library(here)
library(tidyverse)
library(lubridate)
library(knitr)
library(reshape2)
library(binom)
library(ggcorrplot)
library(patchwork)
library(car)


# custom functions
source(here("Scripts", "functions", "exploratory functions.R"))
```

Data
```{r}
# read combined data
regression_data <- readRDS(
  here("Data", "JACSIS2023", "processed", "reshaped_combined_data.RDS")
  )
```

This document will serve as a space where we explore different techniques/strategies to fit (parts of) our regression model.

## Subsections of regression fitting
### Fiting a segmented model for age against age category
Age category here acts as the interaction term. However, I can't figure out if we need to make the intercept vary with age cat too.

To determine which approach we'll use, we will be fitting a model of the proportion of vaccine uptake statuses with age, age-category and number of siblings. To see which matches the models produced during our EDA phase better. Logistic regressions will be run, and their outcomes plotted for comparison

We will be investigating 2 approaches:
1. just adding an interaction term to current regression model packages such as glm 
2. using `segmented` to specify a regresion model?

### Approach 1 - exising regression model packages
```{r}
# Model for covid vaccination
model_covid_coverage_age_2 <- glm(
    covid_coverage_age_2 ~ age_of_interest + age_cat + age_cat*age_of_interest,
    family = "binomial",
    data = regression_data
  )

  # no coverage
model_covid_coverage_age_0 <-  glm(
    covid_coverage_age_0 ~ age_of_interest + age_cat + age_cat*age_of_interest,
    family = "binomial",
    data = regression_data
  )


# Model for influenza vaccination
  # complete coverage
model_influenza_coverage_age_2 <- glm(
    influenza_coverage_age_2 ~ age_of_interest + age_cat + age_cat*age_of_interest,
    family = "binomial",
    data = regression_data
  )

  # no coverage
model_influenza_coverage_age_0 <- glm(
    influenza_coverage_age_0 ~ age_of_interest + age_cat + age_cat*age_of_interest,
    family = "binomial",
    data = regression_data
  )
```



